### 2017-06-23 manuscript_gravitationalconstant.tex
Initial commit

\documentclass[prb,preprint]{revtex4-1} 
% The line above defines the type of LaTeX document.
% Note that AJP uses the same style as Phys. Rev. B (prb).

% The % character begins a comment, which continues to the end of the line.

\usepackage{amsmath}  % needed for \tfrac, \bmatrix, etc.
\usepackage{amsfonts} % needed for bold Greek, Fraktur, and blackboard bold
\usepackage{graphicx} % needed for figures
\usepackage{epstopdf}

\begin{document}

% Be sure to use the \title, \author, \affiliation, and \abstract macros
% to format your title page.  Don't use lower-level macros to  manually
% adjust the fonts and centering.

\title{Could a more precise measurement of the gravitational constant lead to Planckian SI units?}
% In a long title you can use \\ to force a line break at a certain location.

\author{Prasenjit Saha}
\email{psaha@physik.uzh.ch}
% If there were a second author at the same address, we would put another 
% \author{} statement here.  Don't combine multiple authors in a single
% \author statement.
\author{Michael Ebersold}
\email{michael.ebersold@uzh.ch} 
% Please provide a full mailing address here.
\affiliation{Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland}

% See the REVTeX documentation for more examples of author and affiliation lists.

\date{\today}

\begin{abstract}
We present a new idea how the gravitational constant could be measured more precisely and if it could lead to a true Planckian basis for the SI unit system of measurement.
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

\maketitle % title page is now complete

\section{Introduction} % Section titles are automatically converted to all-caps.
% Section numbering is automatic.

In the late 19th century, Max Planck was working on reports about the irreversible process of radiation. He worked out a new entropy law to explain the empirical Wien law of radiation. This required him to introduce two new physical constants, which nowadays are known as the Planck constant and the Boltzmann constant \cite{Tomilin1999}. As a consequence, he described in 1899 a unit system which is based on fundamental natural constants only and thus free of anthropocentric arbitrariness. He pointed out the advantage of such a system in the following words:\cite{Planck99}\\

\begin{quote} ...ihre Bedeutung f\"{u}r alle Zeiten und f\"{u}r alle, auch au{\ss}erirdische und au{\ss}ermenschliche Kulturen notwendig behalten und welche daher als  ``nat\"{u}rliche Ma{\ss}einheiten" bezeichnet werden k\"{o}nnen... \end{quote}

\begin{quote} ...These necessarily retain their meaning for all times and for all civilizations, even extraterrestrial and non-human ones, and can therefore be designated as ``natural units"... \end{quote}

Planck units are defined in such a way that five universal physical constants are given by a numerical value of 1 when expressed in these units. Today the five constants are the speed of light in vacuum $c$, the gravitational constant $G$, the reduced Planck constant $\hbar$, the Boltzmann constant $k_B$ and the Coulomb constant $\left(4 \pi \epsilon_0\right)^{-1}$. Planck had defined them in a somewhat different form and did not adopt any electromagnetic unit. But the natural extension is to include the Coulomb constant, another possibility is to use the elementary charge $e$ to define a basic unit of charge \cite{Tomilin99}.\\
These constants can each be linked with a fundamental theory in physics that is widely accepted and universal: $\hbar$ with quantum mechanics, $c$ with special relativity, $G$ with general relativity, $k_B$ with thermodynamics and statistical mechanics, and $e$ or $\left(4 \pi \epsilon_0\right)^{-1}$ with electrodynamics.\\

The International System of Units (SI) is the commonly used system of measurement. Its beginnings go back to the French Revolution in 1799 as a precursor of the metric system was implemented. With the signing of the Convention of the Metre in 1875, new international prototypes of the metre and the kilogram were established. In the early twentieth century electromagnetic units joined the system and it underwent constant improvement, until in 1960 the modern form, called the Système International d'Unités (SI), was launched. Since the Mole joined the system of measurement in 1971, the SI unit system is in its present form.\\

To come away from the definitions based on artefacts, specific physical states and idealized experiments and because it is technologically possible to measure physical constants to high accuracy, the International Committee for Weights and Measures (CIPM) has proposed new definitions of the SI base units, which likely will be adopted in fall 2018 at the next General Conference on Weights and Measures. The revision of the SI unit system in 2018 goes towards a Planckian based system, since the values of seven physical constants get fixed and thereby define the seven base units. 
To get a truly Planckian, hence ``most natural", basis for the SI, one would have to exchange the ground state hyperfine splitting frequency of the caesium-133 atom $\Delta \nu_{\mathrm{Cs}}$ with the gravitational constant $G$ and then define the second by  
\begin{equation}
\mathrm{s} = \sqrt{\frac{h \, G}{c^5}}.
\end{equation}
Because these three natural constants would have fixed numerical values, this definition is exact. Such a definition would lead to an SI system that is based on fundamental natural constants and therefore stable over time and realizable everywhere. Also completely new and more precise measurements could be designed without having to revise the definitions of the units \cite{Fischer16}. The big problem is, that the uncertainty in the measurements of $G$ is very large large. In Fig.~\ref{fig:Gmeasurements} the latest and most precise measurements of the gravitational constant are plotted together with the recommended CODATA value and its uncertainty. At first glance one notices, that the measured values are not even in good agreement with each other.\\

The big problem that this approach faces, is that the current definition of the second which is based on the hyperfine splitting frequency in the Caesium 33 atom, is much more accurate. \\

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{img/plotGmeas.eps}
	\caption{The data points represent six of the most recent measurement of the gravitational constant. The green line represents the recommended CODATA value and its uncertainty.}
	\label{fig:Gmeasurements}
\end{figure}

\section{A new approach to measure $G$}

The measurements of the gravitational constant sketched in Fig.~\ref{fig:Gmeasurements} have all been done by measuring the very small force with a mechanical apparatus, expect the one with cold atom interferometry. However, it is difficult to exactly measure the weak gravitational force and it is doubtful if there will be significant improvements in measurement uncertainty with this techniques. Also the disagreement of current measurements suggests a demand for new, potentially different measurements. \\

\subsection{Description of new measurement}
Newton's law of gravitation does not only explain why an apple falls down from a tree, it also explains orbits. So if one has two bodies of masses $m_1$ and $m_2$, on which the only force acting is their respective gravitational attraction, they will orbit around their common barycenter. This orbit is described by Kepler's laws. The third law, given in Eq.~(\ref{eq:kepler3}), states that the square of the orbital period $P$ is directly proportional to the cube of the semimajor axis $a$ of the orbit. In this proportionality factor, the gravitational constant $G$ appears. To get a feeling what the dimensions of such an experiment could be, choose for example lead balls with a diameter of about 10 cm, their mass then is about 6 kg. If one then chooses a semimajor axis of 15 cm, the orbital period would be roughly 3.5 hours and the gravitational force acting between the two bodies is of order $10^{-8}$ N. In Fig.~\ref{fig:sketch} we show a sketch on how this would look like.
\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{img/sketchnonumb.pdf}
	\caption{Sketch on how the two masses inside the cavity of a spacecraft orbit around each other.}
	\label{fig:sketch}
\end{figure}
\begin{equation}\label{eq:kepler3}
P^2 = \frac{4 \, \pi^2}{G(m_1+m_2)}a^3
\end{equation}
If one measures the position of the two masses very accurately, it is possible to deduce the gravitational constant. The main difference to other techniques is that position measurements can be very accurate compared to directly measuring the gravitational force.\\

So the goal is to have a two-body system which is freely falling. The only way to achieve this over some time, is to go to space. Thus, one has to design a spacecraft with a cavity that contains the two masses and a position measurement apparatus. The spacecraft is then put in space, preferably to a Lagrange point of the earth-sun system, in order to prevent large inertial forces. To get an improvement in the precision of the gravitational constant, the positions of the two balls have to be known very accurately. Best suitable would probably be a laser interferometry system, which can yield precisions down to some nanometers.\cite{Loughridge13} \\

This approach appears simple, but it brings various difficulties with it. It is practically impossible to have a clean system, where only the respective gravitational force is acting between the two bodies, so one has find out what effects could possibly disturb the system and then either make them as small as possible or correct for them. \\

\subsection{Disturbing effects}

\textbf{Radiation pressure:} In space, there is a constant bombardment of radiation and charged particles from the sun, the so called solar wind. Thus the envelope of the cavity has to protect the two balls. Since the activity of the sun and the direction of the solar wind varies much, the spacecraft must be able to correct its position around the freely falling masses inside the cavity.\\
Furthermore, there is thermal radiation inside the cavity, that could disturb the orbit. To estimate the force on a ball exerted by radiation, we use the Stefan-Boltzmann law. The radiation pressure $p_r$ can be written as a third of the energy density of the electromagnetic radiation. With fundamental thermodynamics one can relate the radiation pressure to the temperature $T$
\begin{equation}
\label{Stefan-Boltzmann}
p_r = \frac{1}{3} u = \frac{1}{3} a T^4
\end{equation}
where the constant $a$ follows from Planck's radiation law and is
\begin{equation}
\label{eq:a}
a = \frac{8 \pi^5 {k_\mathrm{B}}^4}{15 c^3 h^3}.
\end{equation}
We have now a direct relation between radiation pressure and the temperature in the cavity. Then we can estimate the force exerted on a ball of radius $r$ by just multiplying the pressure with the area
\begin{equation}
F = \frac{1}{3} \pi r^2 a T^4.
\end{equation}
As we can see, this force is highly temperature dependent. In order to minimize this influence, one should deploy a temperature as small as possible in the cavity. In fact, if a cooling system based on liquid helium is installed, temperature can be brought down to about 4 K. Such a low temperature results in a radiation pressure of about $10^{-14} \, \mathrm{N} \, \mathrm{m}^{-2}$, which leads to a force on the balls in the order of $10^{-16}$ N. Compared to the gravitational force, this is orders of magnitude less and thus we don't have to worry about effects of radiation pressure.\\

\textbf{Influence of the position measurement:} In general, one has to pay attention as soon as one undertakes a measurement on a physical system, because every measurement can disturb the system. In this case we have a laser that measures the position of two masses which are in an orbit but the photons from the laser exerts an additional force on the masses. To give a rough estimation of this influence, we can compare the radiation pressure of the laser with the one of thermal radiation in the cavity, which we estimated before. In terms of the power $P$ of the laser and the area of the balls $A$, the radiation pressure is
\begin{equation}
\label{eq:radpress}
p_r = \frac{P}{c\,A}.
\end{equation}
On behalf of minimizing the impact of the position measurement, a laser with small power should be used. If we assume a laser with a power of 1 mW, the radiation pressure is in the order of $10^{-10} \, \mathrm{N} \, \mathrm{m}^{-2}$. This is a factor of $10^4$ more than radiation pressure of thermal radiation in the cavity, but the laser doesn't have to shoot photons on the balls constantly. Only for the actual measurement a short pulse has to be sent. If this pulse has a duration of less than roughly $0.1$ ms, its disturbing effect on the orbit is in the same range as the effect of thermal radiation and is thus negligible too.\\

\textbf{Coulomb force:}
Since the electromagnetic force is orders of magnitude stronger than the gravitational force, the balls must be absolutely neutral. A possible source of charges are cosmic rays or the solar wind, so they have to be protected as good as possible. If we want that the Coulomb force between the balls is in the order of $10^{-16} \,\mathrm{N}$ or smaller, and thus negligible, the maximal allowed charge on the balls is about $6 \cdot 10^{-14}\,\mathrm{C}$, which corresponds to roughly $4 \cdot 10^5$ elementary charges.\\

\textbf{Coriolis effect}
\label{sec:coriolis}
The Coriolis force is a fictitious force which only acts on moving bodies in a rotating reference frame. If we imagine the spacecraft located stationary at a Lagrange point of the earth-sun system, it is situated in a rotating frame around the earth-sun barycenter. With respect to this frame, the balls are on their orbit in movement. Thus, there will be a Coriolis acceleration
\begin{equation}
\label{eq:coriolis}
\ddot{\vec{r}}_\mathrm{c} = - 2 \; \vec{\omega} \times \dot{\vec{r}}.
\end{equation}
Here $\vec{\omega}$ is the angular velocity vector of the rotating frame and $\dot{\vec{r}}$ is the velocity vector in the two-body system. Since we don't know the exact orientation of our system with respect to the earth-sun orbital plane, we will have to fit for it.\\

\textbf{Centrifugal and tidal forces}
\label{sec:tidal}
The two masses in the spacecraft should be in a free fall and only feel their respective gravitational attraction. But this is not possible to achieve for both masses simultaneously.\\
Since we are in a non-inertial, rotating frame, there is a centrifugal force. The centrifugal acceleration $\ddot{\vec{r}}_{\mathrm{Z}}$ is proportional to the distance vector $\vec{r}$ and scales with $\omega^2$, where $\omega$ is the angular velocity of the sun-earth reference frame:
\begin{equation}
\label{eq:centrifugalacc}
\ddot{\vec{r}}_{\mathrm{Z}} = \vec{\omega} \times \left( \vec{\omega} \times \vec{r} \right) 
\end{equation}
On the other hand, there are tidal forces. Imagine if one mass is closer to the sun-earth barycenter, the gravitational force on it is slightly bigger than on the other mass. This results in a correction proportional to the distance too. One can approximate the tidal acceleration as
\begin{equation}
\label{eq:tidalacc}
\ddot{\vec{r}}_{\mathrm{\tau}} \approx \frac{2 \, G \, M_\odot}{R^3} \, \vec{r}.
\end{equation}
In this equation $M_\odot$ is the solar mass and $R$ is the radius of the orbit around the sun. With Kepler's third law one can rewrite the tidal acceleration as a function of the orbital period squared of the sun-earth reference frame. Thus it scales the same way as the centrifugal force. The effect is off course tiny, since the system under consideration is much smaller compared to the earth-sun system. To estimate the magnitude of the centrifugal and tidal acceleration relative to the gravitational acceleration between the two balls, we find that their ratio is proportional to the orbital periods squared
\begin{equation}\label{a_ratio}
\frac{\ddot{r}_{\mathrm{\tau}}}{\ddot{r}_\mathrm{G}} \propto \frac{P^2}{{P_\odot}^2} \approx 10^{-7},
\end{equation}
here $P_\odot$ corresponds to one year, whereas $P$ is the orbital period of the two balls. So tidal and centrifugal effects are about $10^{-7}$ times smaller than the respective gravity of the two balls.
In choosing the reference frame such that the net force in the system barycenter is zero, we can correct with a term in the equations of motion for the two-body system, which is proportional to the distance. Because we are in a 3-dimensional space, and possibly the influences of the different axis could mix, we have to multiply the distance vector $\vec{r}$ with a symmetric $3 \times 3$ matrix $C$, such that  
\begin{equation}
\label{eq:tidal}
\ddot{\vec{r}}_{\mathrm{C}} = C \cdot \vec{r}.
\end{equation}
or in terms of the individual components 
\begin{equation}
\label{eq:tidacom}
\left(\ddot{r}_\mathrm{C}\right)_i = \sum_{k=1}^{3} C_{ik} \: r_k.
\end{equation}
The matrix $C$ has six individual components which are not exactly known presumably, we will set constraints to their values and then fit for them. \\

\textbf{Gravitational field:}
A source of an additional gravitational field is earth's moon and the other planets in the solar system. Fortunately, for this we don't need to correct if the whole system, consisting of the spacecraft and the two-body system, is moving on a geodesic through space. Although, the spacecraft should be able to correct its position around the two balls to avoid a collision.
However, much attention has to be paid to the effect of the gravitational field of the spacecraft itself and the measurement apparatus. This certainly can't be neglected, but with a clever design, its effects can be minimized. For example an almost spherically symmetric spacecraft would probably be a good choice. Its gravitational field doesn't have to vanish perfectly, because first order corrections are absorbed in the matrix $C$, for which will be fitted anyway. \\
If this is not practicable or the effects are still too large, it should be possible to calculate the gravitational field caused by the components of the spacecraft at the positions of the balls. Then one can correct the equation of motion by adding an extra term that is accounting for this gravitational field. \\

\section{Extracting $G$ from simulated data}

Now we are going to simulate position data of the two balls that the laser interferometry measurement would provide. From this data we then try to recover the parameters in the orbital equation of motion and thus also the gravitational constant. But first we have to find the orbital equation of motion for the two balls.\\

\subsection{Orbital equation of motion}
From Newtonian dynamics the equation of motion for a two-body system is given by 
\begin{equation}
\label{eq:eomeasy}
\ddot{\vec{r}} = - \frac{G M\, \vec{r}}{r^3}.
\end{equation}
Here $M$ denotes the sum of the masses $m_1$ and $m_2$, $G$ is the gravitational constant and $r$ is the relative distance between the two bodies. This equation just describes the motion of the two-body system. There are no forces acting on the center of mass, so the whole system is moving on a geodesic together with the spacecraft. For simplicity we will abbreviate the product of $GM$ with $k$.\\
Since our two-body system is in a rotating frame and there are perhaps other perturbations, we have to add the terms developed before for the Coriolis effect and the other corrections. Thus, the equation of motion for the two balls looks as follows:
\begin{equation}
\label{eq:eom}
\ddot{\vec{r}} = - \frac{k\,\vec{r}}{r^3} - 2 \; \vec{\omega} \times \dot{\vec{r}} + C \cdot \vec{r}
\end{equation}
These are actually three coupled equations of motion, one for each coordinate axis. Since all are second order differential equations, this leaves us with six initial conditions. In other words to determine the orbit, we need to give six starting values.\\
We choose our coordinate system such that the orbital plane of the two-body system is in the $x-y$ plane. $\vec{\omega}$ is a constant vector that points in the direction of the rotation axis of the earth-sun reference frame. We don't know the exact respective orientation of these two planes, but this is no problem, since we will fit for them. We just need to know the orientation to some degree, to provide good starting points for the fit.
The symmetric matrix $C$ has six independent components which account for tidal forces, centrifugal forces and other perturbations. Also here we don't have exact knowledge on how big these components will be and so we have to make an estimation and then fit for them. \\

Counting all unknown parameters in the equation of motion, we get 16. They correspond to 6 initial conditions, 6 components of the matrix $C$, 3 components of the vector $\vec{\omega}$ and the object of main interest, $k$,  which contains the gravitational constant ($k = GM$). Fitting for so many parameters is not an easy task, but it should be possible because the parameters are not completely unknown and thus we have good starting points for the fit.\\

\subsection{Markov Chain Monte-Carlo fit}

Our problem has 16 unknown parameters, but the only one we are really interested in is $k$, which contains the gravitational constant. For the fit, we suggest to use a Markov Chain Monte-Carlo (MCMC) method because it does good work even if the parameter space is large. We will not describe in detail how the MCMC is working, rather refer to an online tutorial from ESO PyCoffee\cite{esopycoffee} or an introduction paper from van Ravenzwaaij et al.\cite{vanRavenzwaaij16} \\

A Markov chain Monte-Carlo method is a Bayesian approach to data analysis. It uses the information provided by observed data about a set of parameters, to update a prior state of beliefs about the set of parameters to become a posterior state of beliefs about a set of parameters. First we have to specify the prior probability distribution, so to say what values for the 16 parameters in the equation of motion actually make sense. In table~\ref{tab:parameters}, estimated ranges for each parameters are shown. Then, for all 16 parameters a uniform distribution within these ranges and zero probability everywhere else is assumed as the prior probability distribution. \\

We start with the parameter $k$, which is the product of the gravitational constant $G$ and the total mass $M$. If we look at the measured values for the gravitational constant in Fig.~\ref{fig:Gmeasurements}, it is reasonable to constrain its numerical value in SI units to values between $6.671 \cdot 10^{-11}$ and $6.676 \cdot 10^{-11}$. The masses of the two balls can be determined to more than $10^{-5}$ in relative uncertainty, so they will not contribute to a larger uncertainty in $k$. If we take the consideration of balls with a mass of 6 kg, we can give a lower and an upper bound for $k$ which are displayed in table~\ref{tab:parameters}.\\

The vector $\vec{\omega}$ accounts for the rotation of the reference frame. If we say that the orbit of the balls lies in the same plane as the orbital plane of the earth, $\vec{\omega}$ will point in $z$ - direction with $x$ and $y$ components small. Thus $\omega_z$ is associated with the period $P_\odot$ of one year through $2\pi/P_\odot$. Because the rotation axis are conceivably not exactly aligned, we add some uncertainty. As mentioned before, the $x$ and $y$ components are small, so to say roughly in the range of the uncertainty in $w_z$.\\

To estimate the six components of the matrix $C$, we first state again that the barycentre of the two balls is in free fall. So at this point all forces cancel out. If we imagine the ball on its orbit, the tidal force is stronger when its nearer to the earth-sun barycentre and the centrifugal force is stronger when it is in the opposite position. So over an orbit, the effect on the balls stays constant. Also other perturbations are assumed to be constant, at least during some orbits.
The main component of this term should be perpendicular to the rotation axis, for which we have chosen the $z$ - axis. Since we are free to set the $x$ and $y$ axis in the orbital plane, we can choose it such that the main contribution lies in the $x$ - axis. Its magnitude goes as $\omega^2$, so the $C_{xx}$ component should be around $4 \cdot 10^{-14}$. Because we assumed that the main effect is in the $x$ - direction, all the other components are smaller, we constrain them to somewhere between $\pm 10^{-14}$. Since the $C$ matrix also absorbs other perturbations, we give some more uncertainty here. \\

The initial values for the positions can be guessed very accurately, since the position is directly measured precisely. We choose the coordinate system such that the orbit is in the $x-y$ plane and the origin is at the barycenter of the two balls. We set the $x$ - axis such that at the beginning it corresponds to the radius and the $y$ - component is zero.
If we choose the initial positions like this, the initial velocities in $x-$ and $z$ - direction are very small, they just arise from perturbations. The velocity in $y$ - direction can be calculated from Kepler's third law and is therefore also linked with the parameter $k$.\\

In the next step, we set the parameters to a fixed ``true" value within the range estimated. We have to keep in mind that $k$, $x_0$ and $v_{y_0}$ are linked together and there must not be contradictions in the true values. The chosen values are displayed in the right column in table~\ref{tab:parameters}.\\

\begin{table}[h]
	\centering
	\caption{This table shows the ranges in which the parameters numerical values in SI units are estimated to make sense and and also the value which was chosen to generate data.}
	\begin{ruledtabular}
		\begin{tabular}{l c c c}
			% The codes above determine the horizontal alignment in each column.
			% Options are l (left), r (right), c (centered), and p (paragraph).
			% The p option allows an entry to be broken into multiple lines, and
			% therefore requires a width specification, in this case 5 centimeters.
			Parameter & min. value & max. value & chosen value \\
			\hline	% horizontal line to separate headings from data
			$k$ & $8.0052 \cdot 10^{-10}$ & $8.0112 \cdot 10^{-10}$ & $8.0088 \cdot 10^{-10}$ \\
			$\omega_x$ & $-1.0 \cdot 10^{-8}$ & $-1.0 \cdot 10^{-8}$ & $0.02 \cdot 10^{-8}$ \\
			$\omega_y$ & $-1.0 \cdot 10^{-8}$ & $-1.0 \cdot 10^{-8}$ & $-0.03 \cdot 10^{-8}$ \\
			$\omega_z$ & $1.95 \cdot 10^{-7}$ & $2.05 \cdot 10^{-7}$ & $1.996 \cdot 10^{-7}$ \\
			$C_{xx}$ & 0 & $5.0 \cdot 10^{-14}$ & $3.8 \cdot 10^{-14}$ \\
			$C_{yy}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $0.3 \cdot 10^{-14}$ \\
			$C_{zz}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $-0.2 \cdot 10^{-14}$ \\
			$C_{xy} = C_{yx}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $0.3 \cdot 10^{-14}$ \\
			$C_{yz} = C_{zy}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $0.1 \cdot 10^{-14}$ \\
			$C_{xz} = C_{zx}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $-0.4 \cdot 10^{-14}$ \\
			$x_0$ & $0.15$ & $0.1499999$ & $0.1500001$ \\
			$y_0$ & $-1.0 \cdot 10^{-7}$ & $1.0 \cdot 10^{-7}$ & $0.0$ \\ 
			$z_0$ & $-1.0 \cdot 10^{-7}$ & $1.0 \cdot 10^{-7}$ & $0.0$ \\ 
			$v_{x_0}$ & $-1.0 \cdot 10^{-7}$ & $1.0 \cdot 10^{-7}$ & $0.0$ \\ 
			$v_{y_0}$ & $7.30 \cdot 10^{-7}$ & $7.31 \cdot 10^{-7}$ & $7.30698296 \cdot 10^{-5}$ \\
			$v_{z_0}$ & $-1.0 \cdot 10^{-7}$ & $1.0 \cdot 10^{-7}$ & $0.0$ \\
		\end{tabular}
	\end{ruledtabular}
	\label{tab:parameters}
\end{table}

To simulate data we would obtain from the position measurements, we integrate the equations of motion. The time for one orbit without perturbations can be estimated using Kepler's third law (\ref{eq:kepler3}). For the value of $k$ assumed above and a semi-major axis of $0.15 \, \mathrm{m}$, this results in an orbital period of roughly $12900 \, \mathrm{seconds}$ or $3.5 \, \mathrm{hours}$. Here we integrate two orbits in $100000$ steps, that would correspond to about $4$ measurements per second, which should be feasible. To the generated data, we add normal distributed noise with a standard deviation of $10 \, \mathrm{nm}$. This uncertainty stays for a systematic error in the laser interferometry measurement and also random statistic noise. Its value is just an estimation, it would depend highly on the measurement system that has been used. There are laser interferometers, which are able to measure positions with an accuracy of $10\,\mathrm{nm}$.\cite{Loughridge13} \\

A useful way to look at the samples of the posterior returned by the MCMC is doing a corner plot using a Python module named \textit{corner}\cite{corner}. The corner plot shows all the one and two dimensional projections of the posterior probability distributions and demonstrates quickly the covariances between parameters. Along the diagonal, the marginalized distribution for each parameter independently is shown. From this distribution we can then estimate its best value and uncertainty.
In Fig.~\ref{fig:plotCorner4} an excerpt of the full corner plot is shown. Here we only depict the parameters $x_0$, $v_{y_0}$, $\omega_z$, $C_{xx}$ and $k$. These are the more important ones, because for example the main contribution to $\vec{\omega}$ comes from its $z$-component.\\

\begin{figure}[h]
	\centering
	\includegraphics[width=1.0\textwidth]{img/4cornerfit.png}
	\caption{Corner plot of the posterior for 4 parameters: $x_0$, $v_{y_0}$, $\omega_z$ and $k$. Indicated with blue lines are the values we calculated the data from. The dashed lines in the histograms along the diagonal represent the median and the 0.16 and 0.84 percentiles respectively.}
	\label{fig:plotCorner4}
\end{figure}

To arrive at a best value for $k$ and an uncertainty, we take the median and the percentiles corresponding to one sigma from this distribution of $k$. For this example we get:
\begin{equation}\label{eq:kfit}
k = \left( 8.0088006 \, \substack{+0.0000005 \\ -0.0000008}\, \right) \cdot 10^{-10}
\end{equation}
Now we divide $k$ by the total mass of the two balls. Note, that we assume, that the uncertainty on the mass of the balls does not contribute to a larger uncertainty on $G$, because their mass should be determinable to a relative uncertainty of about $10^{-8}$, whereas the one of $k$ is roughly $10^{-7}$. We change the way to write the uncertainty from the 0.16 and 0.84 percentiles to the usual standard deviation, while adding some margin. With units put back in, we arrive at the following value for the gravitational constant $G$:
\begin{equation}\label{Gfit}
G = \left(6.674005 \pm 0.000001 \right) \cdot 10^{-11}  \frac{\mathrm{m}^3}{\mathrm{kg \, s}^2}
\end{equation}
This corresponds to a relative uncertainty of $1.5 \cdot 10^{-7}$ or 15 parts in a hundred million.\\

\section{Conclusion}

\appendix*   % Omit the * if there's more than one appendix.

\section{Uninteresting stuff}

Appendices are for material that is needed for completeness but
not sufficiently interesting to include in the main body of the paper.  Most
articles don't need any appendices, but feel free to use them when
appropriate.  This sample article needs an appendix only to illustrate how 
to create an appendix.

\begin{acknowledgments}

Need acknowledgments?
\end{acknowledgments}

\begin{thebibliography}{99}

\bibitem{vanRavenzwaaij16} D. van Ravenzwaji, and P. Cassey, and S. D. Brown, ``A simple introduction to Markov Chain Monte-Carlo sampling,'' 
Psychonomic Bulletin {\&} Review, 1--12 (2016).  
% Note that the issue number (10) in this citation is required, because
% each issue of Physics Today starts over with page 1.  Also note the use of
% an en-dash (--), not a hyphen (-), for the page range.

\bibitem{Tomilin1999} D. K. Tomilin, ``Natural Systems of Units. To the Centenary Anniversary of the Planck System,'' 
Proceedings of the XXII Workshop on high Energy Physics and field theory, 290 (1999).

\bibitem{Planck99} M. Planck, ``\"{U}ber irreversible {S}trahlungsvorg\"{a}nge,'' 
Sitzungsberichte der K\"{o}niglich Preussischen Akademie der Wissenschaften zu Berlin, 479--480 (1899).

\bibitem{Tomilin99} D. K. Tomilin, ``Fine-structure constant and dimension analysis,'' 
European Journal of Physics (20.5), L39 (1999).

\bibitem{Fischer16} J. Ullrich, and J. Fischer, ``The new system of units,'' 
Nature Physics (12.1), 4--7 (2016).

\bibitem{esopycoffee} Fast and easy-to-implement Markov Chain Monte Carlo with the emcee package, ESO PyCoffee (2014),
\url{<http://eso-python.github.io/ESOPythonTutorials/ESOPythonDemoDay8_MCMC_with_emcee.html>}.

\bibitem{Loughridge13} R. Loughridge, and D. Y. Abramovitch, ``A tutorial on laser interferometry for precision measurements,'' 
American Control Conference, 3686--3703 (2013).

\bibitem{corner} Daniel Foreman-Mackey, ``corner.py: Scatterplot matrices in Python,'' 
The Journal of Open Source Software (10), (2016).

\end{thebibliography}

\end{document}

### 2017-06-23 sample/Sample.tex
readme added as well as sample manuscript

\documentclass[prb,preprint]{revtex4-1} 
% The line above defines the type of LaTeX document.
% Note that AJP uses the same style as Phys. Rev. B (prb).

% The % character begins a comment, which continues to the end of the line.

\usepackage{amsmath}  % needed for \tfrac, \bmatrix, etc.
\usepackage{amsfonts} % needed for bold Greek, Fraktur, and blackboard bold
\usepackage{graphicx} % needed for figures
\usepackage{epstopdf}

\begin{document}

% Be sure to use the \title, \author, \affiliation, and \abstract macros
% to format your title page.  Don't use lower-level macros to  manually
% adjust the fonts and centering.

\title{Preparation of manuscripts for the American Journal of Physics
using \LaTeX}
% In a long title you can use \\ to force a line break at a certain location.

\author{Daniel V. Schroeder}
\email{dschroeder@weber.edu} % optional
\altaffiliation[permanent address: ]{101 Main Street, 
  Anytown, USA} % optional second address
% If there were a second author at the same address, we would put another 
% \author{} statement here.  Don't combine multiple authors in a single
% \author statement.
\affiliation{Department of Physics, Weber State University, Ogden, UT 84408-2508}
% Please provide a full mailing address here.

\author{David P. Jackson}
\email{ajp@dickinson.edu}
\affiliation{Department of Physics, Dickinson College, Carlisle, PA 17013}

% See the REVTeX documentation for more examples of author and affiliation lists.

\date{\today}

\begin{abstract}
This article explains and illustrates the use of \LaTeX\ in preparing manuscripts
for submission to the American Journal of Physics (AJP). While it is not a
comprehensive reference, we hope it will suffice for the needs of most
AJP authors.
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

\maketitle % title page is now complete

\section{Introduction} % Section titles are automatically converted to all-caps.
% Section numbering is automatic.

\LaTeX\ is typesetting software that is widely used by mathematicians
and physicists because it is so good at typesetting equations. It is 
also completely programmable, so it can be configured to produce 
documents with almost any desired formatting, and to automatically
number equations, figures, endnotes, and so on.

To prepare manuscripts for the American Journal of Physics (AJP), 
you should use the REV\TeX\ 4.1 format for Physical Review B
preprints, as indicated in the \texttt{documentclass} line at the top 
of this article's source file.  (If you're already familiar with 
\LaTeX\ and have used other \LaTeX\ formats, please resist the 
temptation to use them, or to otherwise override REV\TeX's formatting 
conventions, in manuscripts that you prepare for AJP.)

This sample article is intended as a tutorial, template, and reference for 
AJP authors, illustrating most of the \LaTeX\ and REV\TeX\ features that 
authors will need.  For a more comprehensive introduction to \LaTeX, 
numerous books and online references are available.\cite{latexsite, 
wikibook, latexbook}  Documentation for the REV\TeX\ package 
can be found on the APS web site.\cite{revtex}

\LaTeX\ is free software, available for Unix/Linux, Mac OS X, and Windows
operating systems. For downloading and installation instructions, follow
the links from the \LaTeX\ web site.\cite{latexsite} It is most
convenient\cite{cloudLaTeX} to install a ``complete \TeX\ distribution,'' 
which will include \LaTeX, the underlying \TeX\ engine, macro packages 
such as REV\TeX, a large collection of fonts, and GUI tools for editing 
and viewing your documents.  To test your installation, try to process
this sample article.

\section{Ordinary text and paragraphs}

To typeset a paragraph of ordinary text, just type the text in your source
file like this. Put line breaks
wherever
you
want, and don't      worry      about      extra      spaces      between      words, which \LaTeX\ will ignore.  You can almost always trust \LaTeX\ to make your paragraphs look good, with neatly justified margins.  % Long lines of text are fine, since most editing programs will wrap them automatically.

To start a new paragraph, just leave a blank line in your source file.

A few punctuation characters require special treatment in \LaTeX. There 
are no ``smart quotes,'' so you need to use the left-quote key (at the 
top-left corner of the keyboard) for a left quote, and the ordinary apostrophe
key (next to the semi-colon) for a right quote. Hit either key twice for double
quotes, which are standard in American English.  Don't use shift-apostrophe
to make double quotes.  Use single quotes when they're nested inside a 
double-quoted quotation.  When a period or comma belongs at the end of
a quotation, put it inside the quotes---even if it's not part of what you're
quoting.\cite{nevermindlogic}

Your fingers also need to distinguish between a hyphen (used for
multi-word adjectives and for hyphenated names like Lennard-Jones), an 
en-dash (formed by typing two consecutive hyphens, and used for ranges 
of numbers like 1--100), and an em-dash (formed out of three consecutive
hyphens and used as an attention-getting punctuation symbol---preferably 
not too often).

Some non-alphanumeric symbols like \$, \&, and \% have special meanings 
in a \LaTeX\ source file, so if you want these symbols to appear in the output, 
you need to precede them with a backslash.

There are also special codes for generating the various accents
that can appear in foreign-language words and names, such as Amp\`ere
and Schr\"odinger.\cite{FontEncodingComment}

You can switch to \textit{italic}, \textbf{bold}, and \texttt{typewriter} fonts
when necessary. Use curly braces to enclose the text that is to appear in 
the special font. In general, \LaTeX\ uses curly braces to group characters 
together for some common transformation.

Notice that any word or symbol preceded by the backslash character is
a special instruction to \LaTeX, typically used to produce a special 
symbol or to modify the typeset output in some way. These instructions 
are also called \textit{control sequences} or \textit{macros}.  
After you've used \LaTeX\ for a while, the little finger of your right 
hand will be really good at finding the backslash and curly-brace keys.

\section{Math symbols}

To type mathematical symbols and expressions within a paragraph, put
them between \$ signs, which indicate \textit{math mode}: $ab + 2c/d = e-3f$.
\LaTeX\ ignores spaces in math mode, using its own algorithms to determine
the right amount of space between symbols.  Notice that an ordinary letter 
like~$x$, when used in math mode, is automatically typeset in italics. 
This is why you need to use math mode for all mathematical
expressions (except plain numerals), even when they don't contain any 
special symbols.  But don't use math mode to italicize ordinary \textit{words}.

Besides ordinary letters and numerals and common arithmetic symbols, math 
mode provides a host of other characters that you can access via control 
sequences.\cite{wikimathpage} These include Greek letters like $\pi$ and 
$\Delta$ (note capitalization), symbols for operations and relations such 
as $\cdot$, $\times$, $\pm$, $\gg$, $\leq$, $\sim$, $\approx$, $\propto$, 
and $\rightarrow$, and special symbols like $\nabla$, $\partial$, $\infty$, 
and~$\hbar$. You can decorate symbols with dots ($\dot x$ or $\ddot x$), 
arrows ($\vec\mu$), bars ($\bar x$ or $\overline m$), hats ($\hat x$), 
tildes ($\tilde f$ or $\widetilde w$), and radicals ($\sqrt\pi$, $\sqrt{2/3}$).
Parentheses and square brackets require no special keystrokes, but you
can also make curly braces and angle brackets: $\{\langle\ \cdots\ \rangle\}$.

To make subscripts and superscripts, use the underscore and caret 
(circumflex) symbols on your keyboard: $x^\mu$, $g_{\mu\nu}$, $\delta^i_j$, 
$\epsilon^{ijk}$.  Notice that you need to put the subscript or superscript 
in curly braces if it's longer than one character (or one control sequence). 
You can even make nested subscripts and superscripts, as in $e^{-x^2}$.  
If a subscript consists of an entire word or word-like abbreviation, 
we usually put it in plain Roman type: $x_\textrm{max}$.  If you need to 
put a subscript or superscript \textit{before} a symbol, use an empty
set of curly braces: ${}^{235}_{\ 92}\textrm{U}$. (Notice the trick of using 
backslash-space put a space before the 92.)

\newcommand{\bE}{\mathbf{E}}   % defines the abbreviation \bE, used below

To make boldface letters you use the \verb/\mathbf/ control sequence, as in
$\nabla\times\mathbf{E} = -\partial\mathbf{B}/\partial t$.  For bold Greek
letters like $\boldsymbol{\omega}$, you need to use \verb/\boldsymbol/
instead.  You can also use calligraphic ($\mathcal{E}$), Fraktur 
($\mathfrak{D}$), and blackboard bold ($\mathbb{R}$) fonts, if you need them. 
If you'll be using a symbol in a special font repeatedly, you can save 
some keystrokes by defining an abbreviation for it; for example, the 
definition \verb/\newcommand{\bE}{\mathbf{E}}/ allows you to type simply 
\verb/\bE/ to get $\bE$.

Unit abbreviations, as in $1~\mathrm{eV} = 1.6\times10^{-19}~\mathrm{J}$,
should be in the plain Roman font, not italics.  You can access this font
from math mode using \verb/\mathrm/. For function names like $\sin\theta$, 
$\exp x$, and $\ln N!$, \LaTeX\ provides special control sequences, 
which you should use instead of \verb/\mathrm/ whenever possible because
they work better with \LaTeX's automatic spacing algorithms.

But \LaTeX\ doesn't always get the spacing right in mathematical formulas.
In the previous paragraph we had to use the \verb/~/ symbol to 
manually insert a space between each number and its units.  The \verb/~/
symbol actually represents an unbreakable space, where \LaTeX\ will never
insert a line break. For occasional minor adjustments to the spacing
in a \LaTeX\ expression, you can insert or remove a little 
space with \verb/\,/ and \verb/\!/.  Use these macros sparingly,
because \LaTeX's default spacing rules will provide more consistency
within and among AJP articles.  The most common use of \verb/\,/ 
is in expressions like $T\,dS - P\,dV$.

\section{Displayed equations}
\label{DispEqSection}	% You can label sections for reference

When an equation is important and/or tall and/or complicated, you should 
display it on a line by itself, with a number. To do this, you put 
\verb/\begin{equation}/ before the equation and \verb/\end{equation}/ 
after it, as in     % Note: never put a blank line before an equation.
\begin{equation}
\int_0^\infty \! \frac{x^3}{e^x - 1} \, dx = 6\sum_{k=1}^\infty \frac1{k^4} = 
    6\left(\frac{\pi^4}{90}\right) = \frac{\pi^4}{15}.
\end{equation}
% Don't put a blank line after the equation unless you're starting a new paragraph.
This example also shows how to make the sum and integral symbols, big parentheses, 
% Don't use \left and \right for small parentheses; you'll get too much space around them.
and built-up fractions.  (Don't put built-up fractions in a 
non-displayed equation, because there won't be enough vertical space in 
AJP's final, single-spaced paragraphs.  Use the slashed form, $x^3/(e^x-1)$, 
instead.)

If you want to refer to an equation elsewhere in your manuscript, you can 
give it a label.  For example, in the equation
\begin{equation}
\label{deriv}
\frac{\Delta x}{\Delta t} \mathop{\longrightarrow}_{\Delta t\rightarrow0} \frac{dx}{dt} 
 = \lim_{\Delta t\rightarrow0} \frac{\Delta x}{\Delta t}
\end{equation}
we've inserted \verb/\label{deriv}/ to label this equation 
\texttt{deriv}.\cite{labelnames}  To refer to 
Eq.~(\ref{deriv}), we then type \verb/\ref{deriv}/.\cite{footnotes}  Notice 
that AJP's style conventions also require you to put the equation number in 
parentheses when you refer to it, and to abbreviate ``Eq.''\ unless it's at 
the beginning of a sentence.

Some equations require more complicated layouts. In the equation
\begin{equation}
E_n = (n + \tfrac12)\hbar, \quad \textrm{where}\  n = 0, 1, 2, \ldots,
\end{equation}
we've used \verb/\quad/ to leave a wide space and \verb/\textrm/ to put ``where'' 
in plain Roman type.  To create a matrix or column vector, as in
\begin{equation}
\begin{bmatrix}
	t' \\
	x' \\
\end{bmatrix}
=
\begin{pmatrix}
	 \gamma & -\beta\gamma \\
	-\beta\gamma & \gamma \\
\end{pmatrix}
\begin{bmatrix}
	t \\
	x \\
\end{bmatrix},
\end{equation}
you can use the \texttt{pmatrix} and/or \texttt{bmatrix} environment, 
for matrices delimited by parentheses and/or brackets.  There's also
a plain \texttt{matrix} environment that omits the delimiters.
In this and other examples of \LaTeX\ tables and arrays, the \verb/&/ 
character serves as a ``tab'' to separate columns, while the \verb/\\/ 
control sequence marks the end of a row.

For a list of related equations, with nicely lined-up equals signs, 
use the \texttt{eqnarray} environment:
\begin{eqnarray}
\oint \vec B \cdot d\vec\ell & = & -\frac{d\Phi_E}{dt} ; \\
\oint \vec E \cdot d\vec\ell & = & \mu_0\epsilon_0\frac{d\Phi_B}{dt} + \mu_0 I.
\end{eqnarray}
You can also use \texttt{eqnarray} to make a multi-line equation, for example,
\begin{eqnarray}
\mathcal{Z} 
& = & 1 + e^{-(\epsilon-\mu)/kT} + e^{-2(\epsilon-\mu)/kT} + \cdots \nonumber \\
& = & 1 + e^{-(\epsilon-\mu)/kT} + (e^{-(\epsilon-\mu)/kT})^2 + \cdots \nonumber \\
& = & \frac{1}{1 - e^{-(\epsilon-\mu)/kT}}.
\end{eqnarray}
Here the first column of the second and third lines is empty.  Note that you 
can use \verb/\nonumber/ within any line to suppress the generation of
an equation number; just be sure that each multi-line equation has at least 
one number.

Another commonly used structure is the \texttt{cases} environment, as in
\begin{equation}
m(T) =
\begin{cases}
	0 & T > T_c \, , \\
	\bigl(1 - [\sinh 2 \beta J]^{-4} \bigr)^{1/8} & T < T_c \, .
\end{cases}
\end{equation}

At AJP we require that you put correct punctuation before and after every
displayed equation, treating each equation as part of a correctly punctuated
English sentence.\cite{mermin} The preceding examples illustrate good
equation punctuation.

\section{Figures}

\LaTeX\ can import figures via the \verb/\includegraphics/ macro.
For AJP, you should embed this in the \texttt{figure} environment, which 
can place the figure in various locations.  This environment also lets 
you add a caption (which AJP requires) and an optional label for referring 
to the figure from elsewhere.  See Fig.~\ref{gasbulbdata} for an example.

\begin{figure}[h!]
% The bracketed code determines the figure's placement:  "h" stands for 
% "here", telling LaTeX to put the figure as close to the current location 
% as possible.  The ! overrides LaTeX's tendency to try to find a location 
% that it thinks is better.  But don't agonize over the exact figure placement 
% in your submitted manuscript.  For your initial submission, just make sure 
% each figure is reasonably close to where it's first referenced.
\centering
\includegraphics{GasBulbData.eps}
\caption{Pressure as a function of temperature for a fixed volume of air.  
The three data sets are for three different amounts of air in the container. 
For an ideal gas, the pressure would go to zero at $-273^\circ$C.  (Notice
that this is a vector graphic, so it can be viewed at any scale without
seeing pixels.)}
\label{gasbulbdata}
\end{figure}
% When an AJP manuscript is conditionally accepted for publication, we
% will request an editable copy of the manuscript in which the figures 
% themselves have been removed, and all figure captions have been moved
% to the end.  You should then comment-out the \includegraphics line
% and move the entire \begin{figure} ... \end{figure} block to the end
% of the source file, just before \end{document}.

Most \LaTeX\ implementations can import a variety of graphics formats.
For graphs and line drawings you should use vector (i.e., resolution-independent)
graphics saved in encapsulated PostScript (.eps) or portable document
format (.pdf).  Most good graphics software systems can save to one 
or both of these formats.  Please don't use a rasterized graphics format
(such as .jpg or .png or .tiff) for graphs or line drawings.

\begin{figure}[h!]
\centering
\includegraphics[width=5in]{ThreeSunsets.jpg}
% Notice the width specification.  Photographs should normally have a
% resolution of approximately 300 pixels per inch when printed, that is,
% a total width of about 1000 pixels for a photo to be printed one column
% wide.  Note also that this included photo is in .jpg format even though 
% a .tiff version should be submitted for final production.
\caption{Three overlaid sequences of photos of the setting sun, taken
near the December solstice (left), September equinox (center), and
June solstice (right), all from the same location at 41$^\circ$ north
latitude. The time interval between images in each sequence is approximately
four minutes.}
\label{sunsets}
\end{figure}

For photographs and other images that are \textit{inherently} made 
of pixels (that is, rasters or bitmaps), \LaTeX\ can 
(usually) handle the .jpg and .png formats as well as .eps and .pdf.  
Figure~\ref{sunsets} is a .jpg example. For final production, however, 
AJP prefers that raster images be in .tiff format.  Most \LaTeX\ systems 
can't import .tiff images, so we recommend using .png or .jpg with \LaTeX\ 
for your initial submission, while saving a higher-quality .tiff version 
to submit as a separate file after your manuscript is conditionally accepted
for publication.

Please refer to the AJP editor's web site\cite{editorsite} for more details 
on AJP's requirements for figure preparation.

\section{Tables}

Tables are somewhat similar to figures:  You use the \texttt{table} environment
to let them ``float'' to an appropriate location, and to automatically number
them and format their captions.  But whereas the content of a figure comes
from an external file, the content of a table is typeset directly in \LaTeX.
For that you use the \texttt{tabular} environment, which uses \verb/&/ and
\verb/\\/ for tabbing and ending rows, just like the \texttt{matrix} and
\texttt{eqnarray} environments discussed in Section~\ref{DispEqSection}.

Table~\ref{bosons} shows a fairly simple example.  Notice that the caption comes
before the table itself, so it will appear above the table instead of below.
The \texttt{ruledtabular} environment, which surrounds \texttt{tabular},
provides the double horizontal lines at the top and bottom, and stretches
the table horizontally out to the margins.  (This will look funny for tables
intended to fill only one column of a final journal page, but there's no 
need to worry about such cosmetic details.)

\begin{table}[h!]
\centering
\caption{Elementary bosons}
\begin{ruledtabular}
\begin{tabular}{l c c c c p{5cm}}
% The codes above determine the horizontal alignment in each column.
% Options are l (left), r (right), c (centered), and p (paragraph).
% The p option allows an entry to be broken into multiple lines, and
% therefore requires a width specification, in this case 5 centimeters.
Name & Symbol & Mass (GeV/$c^2$) & Spin & Discovered & Interacts with \\
\hline	% horizontal line to separate headings from data
Photon & $\gamma$ & \ \ 0 & 1 & 1905 & Electrically charged particles \\
Gluons & $g$ & \ \ 0 & 1 & 1978 & Strongly interacting particles (quarks and gluons) \\
Weak charged bosons & $W^\pm$ & \ 82 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$, $\gamma$ \\
Weak neutral boson & $Z^0$ & \ 91 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$ \\
Higgs boson & $H$ & 126 & 0 & 2012 & Massive particles (according to theory) \\
\end{tabular}
\end{ruledtabular}
\label{bosons}
\end{table}
% Tables, like figure captions, should be moved to the end when you submit 
% an editable manuscript for production, after conditional acceptance.
% Put the tables after the endnotes but before the figure captions.

Every table is a little bit different, and many tables will require
further tricks; see Refs.\ \onlinecite{wikibook} and~\onlinecite{latexbook}
for examples.  Note that the AJP style does not ordinarily use lines 
to separate rows and columns in the body of a table.

\section{Special formats}

\subsection{Block quotes}  % In subsection headings, only the first word is capitalized.

If a quoted passage is long or important, you can use the \texttt{quote} 
environment to typeset it as a block quote, as in this passage from The 
Feynman Lectures:\cite{feynman}
\begin{quote}
A poet once said, ``The whole universe is in a glass of wine.'' We will 
probably never know in what sense he meant that, for poets do not write 
to be understood. But it is true that if we look at a glass of wine closely 
enough we see the entire universe.
\end{quote}

\subsection{Numbered lists}

To create a numbered list, use the \texttt{enumerate} environment and start
each entry with the \verb/\item/ macro:
\begin{enumerate}
\item You can't win.
\item You can't even break even.
\item You can't get out of the game.
\end{enumerate}

\subsection{Unnumbered lists}

For a bulleted list, just use \texttt{itemize} instead of \texttt{enumerate}:
\begin{itemize}
\item Across a resistor, $\Delta V = \pm IR$.
\item Across a capacitor, $\Delta V = \pm Q/C$.
\item Across an inductor, $\Delta V = \pm L(dI/dt)$.
\end{itemize}

\subsection{Literal text}

For typesetting computer code, the \texttt{verbatim} environment reproduces
every character verbatim, in a typewriter font:
\begin{verbatim}
    u[t_] := NIntegrate[
        x^2 * Sqrt[x^2+t^-2] / (Exp[Sqrt[x^2+t^-2]] + 1), {x,0,Infinity}]
    f[t_] := NIntegrate[
        x^2 * Log[1+ Exp[-Sqrt[x2+t^-2]]], {x,0,Infinity}]
    Plot[((11Pi^4/90) / (u[t]+f[t]+(2Pi^4/45)))^(1/3), {t,0,3}]
\end{verbatim}
There's also a \verb/\verb/ macro for typesetting short snippets of verbatim
text within a paragraph. To use this macro, pick any character that doesn't
appear within the verbatim text to use as a delimiter. Most of the examples
in this article use \texttt{/} as a delimiter, but in \verb|{a/b}| we've used
\verb/|/ instead.

\section{Endnotes and references}

This article has already cited quite a few endnotes, using the \verb/\cite/
macro. See the end of this article (and source file) for the endnotes
themselves, which are in an environment called \texttt{thebibliography}
and are created with the \verb/\bibitem/ macro.  These macros require
you to give each endnote a name.  The notes will be numbered in the
order in which the \verb/\bibitem/ entries appear, and AJP requires that
this order coincide with the order in which the notes are first cited in 
the article.  You can cite multiple endnotes in a single \verb/\cite/, 
separating their names by commas.  And you can cite each note as many 
times as you like.

Notice that in the AJP (and Physical Review B) style, the citation numbers 
appear as superscripts. Think carefully about the optimal placement of
each citation, and try not to attach citations to math symbols where the
numbers might be misinterpreted as exponents. Often there will be a
punctuation symbol after the word where you attach the citation; you
should then put the citation \textit{after} the punctuation, not 
before.\cite{nevermindlogic}

If you want to refer directly to Ref.~\onlinecite{mermin} (or any other) 
in a sentence, you can do so with the \verb/\onlinecite/ macro.

Most endnotes consist of bibliographic citations.\cite{noBIBTeX}  Be sure 
to learn and use the AJP styles for citing books,\cite{latexbook} 
articles,\cite{dyson} edited volumes,\cite{examplevolume} and
URLs.\cite{latexsite}  For example, article titles are in double quotes, 
while book titles are in italics. Pay careful attention to all punctuation 
symbols in citations.  Note that AJP requires that all article citations 
include titles as well as beginning and ending page numbers.
Please use standard abbreviations, as listed in the AIP Style 
Manual,\cite{AIPstylemanual} for journal titles.

\section{Conclusion}

We hope this article will help you prepare beautifully typeset
manuscripts for the American Journal of Physics.  Good typesetting requires
considerable attention to detail, but this effort will pay off by making your
manuscript easier and more enjoyable to read.  Your colleagues, reviewers, 
and editors will be grateful for your effort.

Of course, we encourage you to put as much care into the \textit{content} 
of your manuscript as you put into its form.  The AIP Style 
Manual\cite{AIPstylemanual} is an indispensable reference on good physics 
writing, covering everything from planning and organization to standard 
spellings and abbreviations.

Most important of all, please familiarize yourself with the AJP Statement
of Editorial Policy,\cite{editorsite} which describes the types of manuscripts 
that AJP publishes and the audience for which AJP authors are expected to write.
You wouldn't want to put all that care into preparing a manuscript for AJP,
only to find that AJP is the wrong journal for your manuscript.

We look forward to receiving your submission to AJP.

\appendix*   % Omit the * if there's more than one appendix.

\section{Uninteresting stuff}

Appendices are for material that is needed for completeness but
not sufficiently interesting to include in the main body of the paper.  Most
articles don't need any appendices, but feel free to use them when
appropriate.  This sample article needs an appendix only to illustrate how 
to create an appendix.

\begin{acknowledgments}

We gratefully acknowledge Harvey Gould and Jan Tobochnik, who created an earlier 
AJP \LaTeX\ sample article that inspired this one.  This work was supported by the 
American Association of Physics Teachers.

\end{acknowledgments}

\begin{thebibliography}{99}
% The numeral (here 99) in curly braces is nominally the number of entries in
% the bibliography. It's supposed to affect the amount of space around the
% numerical labels, so only the number of digits should matter--and even that
% seems to make no discernible difference.

\bibitem{latexsite} \LaTeX\ Project Web Site, \url{<http://www.latex-project.org/>}.

\bibitem{wikibook} \textit{\LaTeX} (Wikibook), \url{<http://en.wikibooks.org/wiki/LaTeX/>}.

\bibitem{latexbook}Helmut Kopka and Patrick W. Daly, \textit{A Guide to
\LaTeX}, 4th edition (Addison-Wesley, Boston, 2004).

\bibitem{revtex} REV\TeX\ 4 Home Page, \url{<https://authors.aps.org/revtex4/>}.

\bibitem{cloudLaTeX} On the other hand, you can avoid the installation process
entirely by using a cloud-based \LaTeX\ processor such as ShareLaTeX,
\url{<https://www.sharelatex.com/>}, or write\LaTeX, \url{<https://www.writelatex.com/>}.

\bibitem{nevermindlogic} In typography, aesthetics often takes precedence over logic.

\bibitem{FontEncodingComment} Please don't try to handle foreign characters 
and accents with the \texttt{inputenc} and \texttt{fontenc} packages, which 
are incompatible with AJP's editing process.

\bibitem{wikimathpage} See the Mathematics chapter of Ref.~\onlinecite{wikibook}
for an excellent overview of math symbols and equations, with examples.

\bibitem{labelnames} Thinking up a good label name takes a moment, but 
it's worth the trouble; we strongly advise against using labels like 
\texttt{eq2}, which become extremely confusing after you decide to add 
another equation before Eq.~(\ref{deriv}).

\bibitem{footnotes} You need to process a file twice to get the counters correct.

\bibitem{mermin} N. David Mermin, ``What's wrong with these equations?,'' 
Phys. Today \textbf{42} (10), 9--11 (1989).  
% Note that the issue number (10) in this citation is required, because
% each issue of Physics Today starts over with page 1.  Also note the use of
% an en-dash (--), not a hyphen (-), for the page range.

\bibitem{editorsite} American Journal of Physics Editor's Web Site, 
\url{<http://ajp.dickinson.edu>}.

\bibitem{feynman} Richard P. Feynman, Robert B. Leighton, and Matthew Sands, 
\textit{The Feynman Lectures on Physics, Vol.\ 1} (Addison-Wesley, 1964), p.~3-10.
% Note that this book is paginated by chapter; "3-10" is a single page reference
% that uses a hyphen, not a range of pages that would us an en-dash (--).

\bibitem{noBIBTeX} Many \LaTeX\ users manage their bibliographic data with 
a tool called BIB\TeX.  Unfortunately, AJP cannot accept BIB\TeX\ files; all 
bibliographic references must be incorporated into the manuscript file
as shown here, at least when you send an editable file for production.

\bibitem{dyson} Freeman J. Dyson, ``Feynman's proof of the Maxwell equations,''
Am. J. Phys. \textbf{58} (3), 209--211.  
% The issue number (3) in this citation is optional, because AJP's pagination 
% is by volume.

\bibitem{examplevolume} M. R. Flannery, ``Elastic scattering,'' in 
\textit{Atomic, Molecular, and Optical Physics Handbook}, edited by
G. W. F. Drake (AIP Press, New York, 1996), p.~520.

\bibitem{AIPstylemanual} \textit{AIP Style Manual}, 4th edition (American 
Institute of Physics, New York, 1990). Available online at 
\url{<http://www.aip.org/pubservs/style/4thed/toc.html>}. Although parts of 
it have been made out of date by advancing technology, most of this manual 
is still as useful as ever. Just be sure to follow AJP's specific rules
whenever they conflict with those in the manual.

\end{thebibliography}

% If your manuscript is conditionally accepted, the editors will ask you to
% submit your editable LaTeX source file.  Before doing so, you should move
% all tables and figure captions to the end, as shown below.  Tables come 
% first, followed by figure captions (with figure inclusions commented-out).
% Figures should be submitted as separate files, collected with the
% LaTeX file into a single .zip archive.

%\newpage   % Start a new page for tables

%\begin{table}[h!]
%\centering
%\caption{Elementary bosons}
%\begin{ruledtabular}
%\begin{tabular}{l c c c c p{5cm}}
%Name & Symbol & Mass (GeV/$c^2$) & Spin & Discovered & Interacts with \\
%\hline
%Photon & $\gamma$ & \ \ 0 & 1 & 1905 & Electrically charged particles \\
%Gluons & $g$ & \ \ 0 & 1 & 1978 & Strongly interacting particles (quarks and gluons) \\
%Weak charged bosons & $W^\pm$ & \ 82 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$, $\gamma$ \\
%Weak neutral boson & $Z^0$ & \ 91 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$ \\
%Higgs boson & $H$ & 126 & 0 & 2012 & Massive particles (according to theory) \\
%\end{tabular}
%\end{ruledtabular}
%\label{bosons}
%\end{table}

%\newpage   % Start a new page for figure captions

%\section*{Figure captions}

%\begin{figure}[h!]
%\centering
%\includegraphics{GasBulbData.eps}   % This line stays commented-out
%\caption{Pressure as a function of temperature for a fixed volume of air.  
%The three data sets are for three different amounts of air in the container. 
%For an ideal gas, the pressure would go to zero at $-273^\circ$C.  (Notice
%that this is a vector graphic, so it can be viewed at any scale without
%seeing pixels.)}

%\label{gasbulbdata}
%\end{figure}

%\begin{figure}[h!]
%\centering
%\includegraphics[width=5in]{ThreeSunsets.jpg}   % This line stays commented-out
%\caption{Three overlaid sequences of photos of the setting sun, taken
%near the December solstice (left), September equinox (center), and
%June solstice (right), all from the same location at 41$^\circ$ north
%latitude. The time interval between images in each sequence is approximately
%four minutes.}
%\label{sunsets}
%\end{figure}

\end{document}

### 2017-07-04 manuscript_gravitationalconstant.tex
definitions with numerical factors
writing intro

@@
 
-\title{Could a more precise measurement of the gravitational constant lead to Planckian SI units?}
+\title{A thought-experiment for a Planckian standard kilogram}
 % In a long title you can use \\ to force a line break at a certain location.
 
-\author{Prasenjit Saha}
-\email{psaha@physik.uzh.ch}
+\author{Michael Ebersold}
+\email{michael.ebersold@uzh.ch} 
 % If there were a second author at the same address, we would put another 
@@
 % \author statement.
-\author{Michael Ebersold}
-\email{michael.ebersold@uzh.ch} 
+\author{Prasenjit Saha}
+\email{psaha@physik.uzh.ch}
 % Please provide a full mailing address here.
@@
 
-\section{Introduction} % Section titles are automatically converted to all-caps.
-% Section numbering is automatic.
+\section{Introduction}
+
+The reform of SI units to use quantum standards is an ongoing `news
+story' in physics.  At the heart of the reform are two quantum
+phenomena that appear on macroscopic scales: the Josephson effect
+makes $h/e$ measurable as a voltage-to-frequency ratio, while the
+quantum Hall effect makes $h/e^2$ a standard resistance (the
+von~Klitzing constant).  These enable electrical units to be defined
+in terms of $h$ and $e$.  A further ingenious instrument, known as a
+watt balance, precisely compares electrical and mechanical power, thus
+enabled mass to be standardized in terms of $h$.  For an simple
+introduction to the new SI, we refer the reader to the article on the
+``LEGO watt balance''[citation].
+
+The proposed redefinition of the kilogram is as an explicit value for
+$h$ and $c$, but we can think of it as
+\begin{equation}
+\mathrm{kg} \equiv 1.3563925\ldots \times 10^{50} \, \mathrm{s}^{-1}
+                   \times \frac{h}{c^2}
+\end{equation}
+with the exact value to be decided.  As we can see, the kilogram is
+coupled to the definition of a second.  That is not a problem in
+practice, as the second is standardized orders of magnitude better
+than any other unit.  Nonetheless, it is interesting to consider a
+logical further step of decoupling the kilogram from other
+definitions.  This could be done by introducing the gravitational
+constant, since $\sqrt{hc/G}$ has dimensions of mass.  Historically,
+there have been several proposed unit systems that included $G$ in
+some way,\cite{Tomilin1999} but the idea of including both gravity and
+quantum in a unit system comes from Planck\cite{Planck99}.  In the
+process of working towards the radiation law, Planck realized that
+$c,G,h$ and the Boltzmann constant $k_B$ (in his notation
+$G\rightarrow f$, $h\rightarrow b$, $h/k_B\rightarrow a$) naturally
+define units for mass, length, time, and temperature.  (Planck
+remarked that such units would be meaningful even in non-human and
+extraterrestrial cultures.)
+
+\begin{equation}
+\begin{aligned}
+\mathrm{kg} &= 4.594\ldots \times 10^7
+               \left(\frac{\hbar c}{G}\right)^{\!1/2} \\
+\mathrm{m}  &= 6.187\ldots \times 10^{34}
+               \left(\frac{\hbar G}{c^3}\right)^{\!1/2} \\
+\mathrm{s}  &= 1.854\ldots \times 10^{43}
+               \left(\frac{\hbar G}{c^5}\right)^{\!1/2} \\
+\mathrm{K}  &= 7.058\ldots \times 10^{-33}
+               \left(\frac{\hbar c^5}{Gk_B^2}\right)^{\!1/2}
+\end{aligned}
+\end{equation}
 
@@
 He worked out a new entropy law to explain the empirical Wien law of radiation.
-This required him to introduce two new physical constants, which nowadays are known as the Planck constant and the Boltzmann constant \cite{Tomilin1999}.
+This required him to introduce two new physical constants, which nowadays are known as the Planck constant and the Boltzmann constant .
 As a consequence, he described in 1899 a unit system which is based on fundamental natural constants only and thus free of anthropocentric arbitrariness.
@@
 \end{equation}
-Because these three natural constants would have fixed numerical values, this definition is exact.
+
+Because these four natural constants would have fixed numerical values, this definition is exact.
 Such a definition would lead to an SI system that is based on fundamental natural constants and therefore stable over time and realizable everywhere.
@@
 	\centering
-	\includegraphics[width=\textwidth]{img/plotGmeas.eps}
+	\includegraphics[width=\textwidth]{img/plotGmeas}
 	\caption{The data points represent six of the most recent measurement of the gravitational constant. The green line represents the recommended CODATA value and its uncertainty.}

### 2017-07-04 manuscript_gravitationalconstant.tex
revised introduction

@@
 
-\title{A thought-experiment for a Planckian standard kilogram}
+\title{A scenario for a Planckian standard kilogram}
 % In a long title you can use \\ to force a line break at a certain location.
@@
 \begin{abstract}
-We present a new idea how the gravitational constant could be measured more precisely and if it could lead to a true Planckian basis for the SI unit system of measurement.
+The kilogram could, in principle, be redefined as an integer multiple
+of the Planck mass (or 4594xxxx$\times\sqrt{\hbar c/G}$) with no
+significant change from its current value.  The practical hurdle is
+measuring $G$ three or four orders of magnitude than presently known,
+so as to find the unknown digits xxxx.  We study a possible scenario
+for doing so with an artificial two-body orbit.  Requirements for
+suppressing perturbing effects (notably tidal forces and radiation
+pressure), and obtaining the desired signal-to-noise are estimated.
 \end{abstract}
-% AJP requires an abstract for all regular article submissions.
-% Abstracts are optional for submissions to the "Notes and Discussions" section.
 
-\maketitle % title page is now complete
+\maketitle
 
@@
 introduction to the new SI, we refer the reader to the article on the
-``LEGO watt balance''[citation].
+``LEGO watt balance''[2015AmJPh..83..913C].
 
@@
 definitions.  This could be done by introducing the gravitational
-constant, since $\sqrt{hc/G}$ has dimensions of mass.  Historically,
-there have been several proposed unit systems that included $G$ in
-some way,\cite{Tomilin1999} but the idea of including both gravity and
-quantum in a unit system comes from Planck\cite{Planck99}.  In the
-process of working towards the radiation law, Planck realized that
-$c,G,h$ and the Boltzmann constant $k_B$ (in his notation
-$G\rightarrow f$, $h\rightarrow b$, $h/k_B\rightarrow a$) naturally
-define units for mass, length, time, and temperature.  (Planck
-remarked that such units would be meaningful even in non-human and
-extraterrestrial cultures.)
+constant, since $\sqrt{hc/G}$ has dimensions of mass.
 
-\begin{equation}
+Historically, there have been several proposed unit systems that
+included $G$ in some way,\cite{Tomilin1999} but the idea of including
+both gravity and quantum in a unit system comes from
+Planck\cite{Planck99}.  In the process of working towards the
+radiation law, Planck realized that $c,G,h$ and the Boltzmann constant
+$k_B$ (in his notation $G\rightarrow f$, $h\rightarrow b$,
+$h/k_B\rightarrow a$) naturally define units for mass, length, time,
+and temperature.  (Planck remarked that such units would be meaningful
+even in non-human and extraterrestrial cultures.)
+
+A hypothetical Planckian SI unit system would have
+\begin{equation} \label{eq:defs}
 \begin{aligned}
@@
 \end{equation}
+with the numerical coefficients chosen so as to match the present
+standards.  The square-rooted expressions are conventionally known as
+the Planck mass, Planck length, and so on.  (They are actually
+$\sqrt{2\pi}$ times Planck's definitions.)  Extension to electrical
+units is straightforward, but we will not discuss it here.  The Planck
+length, time, and temperature in themselves are extreme scales, not
+probed by any known physical process, and presumably the regime of
+quantum gravity.  But extreme scales do not harm if they are only part
+of some pression, as they are here.  The Planck mass is small but
+microscopically measurable: $\sim20\mu\mathrm{g}$.  This is of the
+same order as the uncertainty in the prototype kilogram itself.  Hence
+the kilogram could be redefined as an integer multiple of the Planck
+mass, without significantly perturbing its value.
 
-In the late 19th century, Max Planck was working on reports about the irreversible process of radiation.
+The difficulty with Eq.~\eqref{eq:defs} is that all the expressions
+involve $G$.  Given the current uncertainties in $G$,
+Eq.~\eqref{eq:defs} would allow units to be standardized only to four
+significant digits, which is obviously not enough.  Improvement by
+several orders of magnitude would be needed, to make the Planckian
+kilogram practicable.  In this paper, we study a scenario which may
+make such an improvement possible.  A Planckian second not a prospect
+with anything like present technology, because demands on the time
+standard are more stringent still.
+
+% In the late 19th century, Max Planck was working on reports about the irreversible process of radiation.
 He worked out a new entropy law to explain the empirical Wien law of radiation.
@@
 
-\begin{quote} ...ihre Bedeutung f\"{u}r alle Zeiten und f\"{u}r alle, auch au{\ss}erirdische und au{\ss}ermenschliche Kulturen notwendig behalten und welche daher als  ``nat\"{u}rliche Ma{\ss}einheiten" bezeichnet werden k\"{o}nnen...
+% \begin{quote} ...ihre Bedeutung f\"{u}r alle Zeiten und f\"{u}r alle, auch au{\ss}erirdische und au{\ss}ermenschliche Kulturen notwendig behalten und welche daher als  ``nat\"{u}rliche Ma{\ss}einheiten" bezeichnet werden k\"{o}nnen...
 \end{quote}
 
-\begin{quote} ...These necessarily retain their meaning for all times and for all civilizations, even extraterrestrial and non-human ones, and can therefore be designated as ``natural units"...
+% \begin{quote} ...These necessarily retain their meaning for all times and for all civilizations, even extraterrestrial and non-human ones, and can therefore be designated as ``natural units"...
 \end{quote}
 
-Planck units are defined in such a way that five universal physical constants are given by a numerical value of 1 when expressed in these units.
+% Planck units are defined in such a way that five universal physical constants are given by a numerical value of 1 when expressed in these units.
 Today the five constants are the speed of light in vacuum $c$, the gravitational constant $G$, the reduced Planck constant $\hbar$, the Boltzmann constant $k_B$ and the Coulomb constant $\left(4 \pi \epsilon_0\right)^{-1}$.
@@
 But the natural extension is to include the Coulomb constant, another possibility is to use the elementary charge $e$ to define a basic unit of charge \cite{Tomilin99}.\\
-These constants can each be linked with a fundamental theory in physics that is widely accepted and universal: $\hbar$ with quantum mechanics, $c$ with special relativity, $G$ with general relativity, $k_B$ with thermodynamics and statistical mechanics, and $e$ or $\left(4 \pi \epsilon_0\right)^{-1}$ with electrodynamics.\\
+% These constants can each be linked with a fundamental theory in physics that is widely accepted and universal: $\hbar$ with quantum mechanics, $c$ with special relativity, $G$ with general relativity, $k_B$ with thermodynamics and statistical mechanics, and $e$ or $\left(4 \pi \epsilon_0\right)^{-1}$ with electrodynamics.\\
 
-The International System of Units (SI) is the commonly used system of measurement.
+% The International System of Units (SI) is the commonly used system of measurement.
 Its beginnings go back to the French Revolution in 1799 as a precursor of the metric system was implemented.
@@
 
-To come away from the definitions based on artefacts, specific physical states and idealized experiments and because it is technologically possible to measure physical constants to high accuracy, the International Committee for Weights and Measures (CIPM) has proposed new definitions of the SI base units, which likely will be adopted in fall 2018 at the next General Conference on Weights and Measures.
+% To come away from the definitions based on artefacts, specific physical states and idealized experiments and because it is technologically possible to measure physical constants to high accuracy, the International Committee for Weights and Measures (CIPM) has proposed new definitions of the SI base units, which likely will be adopted in fall 2018 at the next General Conference on Weights and Measures.
 The revision of the SI unit system in 2018 goes towards a Planckian based system, since the values of seven physical constants get fixed and thereby define the seven base units.
-To get a truly Planckian, hence ``most natural", basis for the SI, one would have to exchange the ground state hyperfine splitting frequency of the caesium-133 atom $\Delta \nu_{\mathrm{Cs}}$ with the gravitational constant $G$ and then define the second by
-\begin{equation}
-\mathrm{s} = \sqrt{\frac{h \, G}{c^5}}.
-\end{equation}
+% To get a truly Planckian, hence ``most natural", basis for the SI, one would have to exchange the ground state hyperfine splitting frequency of the caesium-133 atom $\Delta \nu_{\mathrm{Cs}}$ with the gravitational constant $G$ and then define the second by
+% \begin{equation}
+% \mathrm{s} = \sqrt{\frac{h \, G}{c^5}}.
+% \end{equation}
 
-Because these four natural constants would have fixed numerical values, this definition is exact.
+% Because these four natural constants would have fixed numerical values, this definition is exact.
 Such a definition would lead to an SI system that is based on fundamental natural constants and therefore stable over time and realizable everywhere.
@@
 
-The big problem that this approach faces, is that the current definition of the second which is based on the hyperfine splitting frequency in the Caesium 33 atom, is much more accurate. \\
+% The big problem that this approach faces, is that the current definition of the second which is based on the hyperfine splitting frequency in the Caesium 33 atom, is much more accurate. \\
 

### 2017-10-21 manuscript_gravitationalconstant.tex
2. A Description of a new G Measurement modified.

@@
 included $G$ in some way,\cite{Tomilin1999} but the idea of including
-both gravity and quantum in a unit system comes from
+both gravity and quantum mechanics in a unit system comes from
 Planck\cite{Planck99}.  In the process of working towards the
@@
 with anything like present technology, because demands on the time
-standard are more stringent still.
-
-% In the late 19th century, Max Planck was working on reports about the irreversible process of radiation.
-He worked out a new entropy law to explain the empirical Wien law of radiation.
-This required him to introduce two new physical constants, which nowadays are known as the Planck constant and the Boltzmann constant .
-As a consequence, he described in 1899 a unit system which is based on fundamental natural constants only and thus free of anthropocentric arbitrariness.
-He pointed out the advantage of such a system in the following words:\cite{Planck99}\\
-
-% \begin{quote} ...ihre Bedeutung f\"{u}r alle Zeiten und f\"{u}r alle, auch au{\ss}erirdische und au{\ss}ermenschliche Kulturen notwendig behalten und welche daher als  ``nat\"{u}rliche Ma{\ss}einheiten" bezeichnet werden k\"{o}nnen...
-\end{quote}
-
-% \begin{quote} ...These necessarily retain their meaning for all times and for all civilizations, even extraterrestrial and non-human ones, and can therefore be designated as ``natural units"...
-\end{quote}
-
-% Planck units are defined in such a way that five universal physical constants are given by a numerical value of 1 when expressed in these units.
-Today the five constants are the speed of light in vacuum $c$, the gravitational constant $G$, the reduced Planck constant $\hbar$, the Boltzmann constant $k_B$ and the Coulomb constant $\left(4 \pi \epsilon_0\right)^{-1}$.
-Planck had defined them in a somewhat different form and did not adopt any electromagnetic unit.
-But the natural extension is to include the Coulomb constant, another possibility is to use the elementary charge $e$ to define a basic unit of charge \cite{Tomilin99}.\\
-% These constants can each be linked with a fundamental theory in physics that is widely accepted and universal: $\hbar$ with quantum mechanics, $c$ with special relativity, $G$ with general relativity, $k_B$ with thermodynamics and statistical mechanics, and $e$ or $\left(4 \pi \epsilon_0\right)^{-1}$ with electrodynamics.\\
-
-% The International System of Units (SI) is the commonly used system of measurement.
-Its beginnings go back to the French Revolution in 1799 as a precursor of the metric system was implemented.
-With the signing of the Convention of the Metre in 1875, new international prototypes of the metre and the kilogram were established.
-In the early twentieth century electromagnetic units joined the system and it underwent constant improvement, until in 1960 the modern form, called the Système International d'Unités (SI), was launched.
-Since the Mole joined the system of measurement in 1971, the SI unit system is in its present form.\\
-
-% To come away from the definitions based on artefacts, specific physical states and idealized experiments and because it is technologically possible to measure physical constants to high accuracy, the International Committee for Weights and Measures (CIPM) has proposed new definitions of the SI base units, which likely will be adopted in fall 2018 at the next General Conference on Weights and Measures.
-The revision of the SI unit system in 2018 goes towards a Planckian based system, since the values of seven physical constants get fixed and thereby define the seven base units.
-% To get a truly Planckian, hence ``most natural", basis for the SI, one would have to exchange the ground state hyperfine splitting frequency of the caesium-133 atom $\Delta \nu_{\mathrm{Cs}}$ with the gravitational constant $G$ and then define the second by
-% \begin{equation}
-% \mathrm{s} = \sqrt{\frac{h \, G}{c^5}}.
-% \end{equation}
-
-% Because these four natural constants would have fixed numerical values, this definition is exact.
-Such a definition would lead to an SI system that is based on fundamental natural constants and therefore stable over time and realizable everywhere.
-Also completely new and more precise measurements could be designed without having to revise the definitions of the units \cite{Fischer16}.
-The big problem is, that the uncertainty in the measurements of $G$ is very large large.
-In Fig.~\ref{fig:Gmeasurements} the latest and most precise measurements of the gravitational constant are plotted together with the recommended CODATA value and its uncertainty.
-At first glance one notices, that the measured values are not even in good agreement with each other.\\
-
-% The big problem that this approach faces, is that the current definition of the second which is based on the hyperfine splitting frequency in the Caesium 33 atom, is much more accurate. \\
+standard are more stringent still.\\
 
@@
 
-The measurements of the gravitational constant sketched in Fig.~\ref{fig:Gmeasurements} have all been done by measuring the very small force with a mechanical apparatus, expect the one with cold atom interferometry.
-However, it is difficult to exactly measure the weak gravitational force and it is doubtful if there will be significant improvements in measurement uncertainty with this techniques.
-Also the disagreement of current measurements suggests a demand for new, potentially different measurements.
-\\
+In Fig.~\ref{fig:Gmeasurements} we have plotted some of the most recent measurements of the gravitational constant.
+3 of them have been carried out using a torsion balance (), Schlamminger et al.
+used a beam balance and .......
+measured the separation of two simple pendulums in a gravitational field.
+They all tried to measure the very weak gravitational force with a mechanical apparatus.
+The sixth measurement was performed under another approach, using cold atom interferometry.
+Its uncertainty is a lot larger than the others, but it could become more competitive in the future.
+However, a brief glance on the plotted measurements shows the disagreement of current $G$-values and suggests a demand for new, potentially different techniques.\\
 
@@
 Newton's law of gravitation does not only explain why an apple falls down from a tree, it also explains orbits.
-So if one has two bodies of masses $m_1$ and $m_2$, on which the only force acting is their respective gravitational attraction, they will orbit around their common barycenter.
-This orbit is described by Kepler's laws.
-The third law, given in Eq.~(\ref{eq:kepler3}), states that the square of the orbital period $P$ is directly proportional to the cube of the semimajor axis $a$ of the orbit.
+If one has two bodies of masses $m_1$ and $m_2$, on which the only force acting is their respective gravitational attraction, they will orbit around their common barycenter in an ellipse described by Kepler's laws.
+The third law, given in Eq.~(\ref{eq:kepler3}), states that the square of the orbital period $P$ is directly proportional to the cube of the semimajor axis $a$.
 In this proportionality factor, the gravitational constant $G$ appears.
-To get a feeling what the dimensions of such an experiment could be, choose for example lead balls with a diameter of about 10 cm, their mass then is about 6 kg.
-If one then chooses a semimajor axis of 15 cm, the orbital period would be roughly 3.5 hours and the gravitational force acting between the two bodies is of order $10^{-8}$ N.
-In Fig.~\ref{fig:sketch} we show a sketch on how this would look like.
+\begin{equation}\label{eq:kepler3}
+P^2 = \frac{4 \, \pi^2}{G(m_1+m_2)}a^3
+\end{equation}
+If one can measure the position of the two masses very accurately and thus knows the orbit, it is possible to deduce the gravitational constant. 
+So what we need is a freely falling two-body system.
+The only way to achieve this over some time, is to go to space.
+Thus, one has to design a spacecraft involving a cavity that contains the two masses and a position measurement apparatus.
+The cavity should shield the two-body system from environmental influences.
+The spacecraft is then put in space, preferably to a Lagrange point of the earth-sun system, in order to prevent large inertial forces.\\
+
 \begin{figure}
@@
 \end{figure}
-\begin{equation}\label{eq:kepler3}
-P^2 = \frac{4 \, \pi^2}{G(m_1+m_2)}a^3
-\end{equation}
-If one measures the position of the two masses very accurately, it is possible to deduce the gravitational constant.
-The main difference to other techniques is that position measurements can be very accurate compared to directly measuring the gravitational force.\\
 
-So the goal is to have a two-body system which is freely falling.
-The only way to achieve this over some time, is to go to space.
-Thus, one has to design a spacecraft with a cavity that contains the two masses and a position measurement apparatus.
-The spacecraft is then put in space, preferably to a Lagrange point of the earth-sun system, in order to prevent large inertial forces.
-To get an improvement in the precision of the gravitational constant, the positions of the two balls have to be known very accurately.
-Best suitable would probably be a laser interferometry system, which can yield precisions down to some nanometers.\cite{Loughridge13} \\
-
-This approach appears simple, but it brings various difficulties with it.
-It is practically impossible to have a clean system, where only the respective gravitational force is acting between the two bodies, so one has find out what effects could possibly disturb the system and then either make them as small as possible or correct for them.
+To get a feeling what the dimensions of such an experiment could be, choose for example lead balls with a diameter of about 10 cm, their mass then is about 6 kg.
+If one then chooses a semimajor axis of 15 cm, the orbital period would be roughly 3.5 hours and the gravitational force acting between the two bodies is of order $10^{-8}$ N.
+In Fig.~\ref{fig:sketch} we show a sketch on how this would look like.
+For getting an improvement in the precision of the gravitational constant, the positions of the two balls have to be known very accurately.
+Best suitable would probably be a laser interferometry system, which can yield precisions down to some nanometers.\cite{Loughridge13}
+The main difference to other techniques is that position measurements can be very accurate compared to directly measuring the gravitational force.
+This new kind of measurement of the gravitational constant appears simple, but it brings various difficulties with it.
+It is practically impossible to have a clean system, where only the respective gravitational force is acting between the two bodies, so one has to find out what effects could possibly disturb the system and then either make them as small as possible or correct for them.
 \\

### 2017-10-21 manuscript_gravitationalconstant.tex
Section 2 B modified

@@
 
-\textbf{Radiation pressure:} In space, there is a constant bombardment of radiation and charged particles from the sun, the so called solar wind.
-Thus the envelope of the cavity has to protect the two balls.
-Since the activity of the sun and the direction of the solar wind varies much, the spacecraft must be able to correct its position around the freely falling masses inside the cavity.\\
+\textbf{Radiation pressure:} The envelope of the cavity needs to protect the two body-system from the constant bombardment of radiation and charged particles from the sun.
+Since the activity of the sun varies much, the spacecraft must be able to correct its position around the freely falling masses inside the cavity.\\
 Furthermore, there is thermal radiation inside the cavity, that could disturb the orbit.
-To estimate the force on a ball exerted by radiation, we use the Stefan-Boltzmann law.
-The radiation pressure $p_r$ can be written as a third of the energy density of the electromagnetic radiation.
-With fundamental thermodynamics one can relate the radiation pressure to the temperature $T$
+Using the Stefan-Boltzmann law, we can relate radiation pressure to the temperature inside the cavity. If we then specify to balls of radius $r$, we can express the force on the balls as 
 \begin{equation}
-\label{Stefan-Boltzmann}
-p_r = \frac{1}{3} u = \frac{1}{3} a T^4
+F = \frac{1}{3} \pi r^2 \sigma_a T^4.
 \end{equation}
-where the constant $a$ follows from Planck's radiation law and is
+with
 \begin{equation}
 \label{eq:a}
-a = \frac{8 \pi^5 {k_\mathrm{B}}^4}{15 c^3 h^3}.
+\sigma_a = \frac{8 \pi^5 {k_\mathrm{B}}^4}{15 c^3 h^3}
 \end{equation}
-We have now a direct relation between radiation pressure and the temperature in the cavity.
+being a constant that follows from Planck's radiation law.
+%
+%To estimate the force on a ball exerted by radiation, we use the Stefan-Boltzmann law.
+The radiation pressure $p_r$ can be written as a third of the energy density of the electromagnetic radiation and with fundamental thermodynamics one can relate the radiation pressure to the temperature $T$
+%
+%\begin{equation}
+%\label{Stefan-Boltzmann}
+%p_r = \frac{1}{3} u = \frac{1}{3} a T^4
+%\end{equation}
+%where the constant $a$ follows from Planck's radiation law and is
+%\begin{equation}
+%\label{eq:a}
+%a = \frac{8 \pi^5 {k_\mathrm{B}}^4}{15 c^3 h^3}.
+%\end{equation}
+%We have now a direct relation between radiation pressure and the temperature in the cavity.
 Then we can estimate the force exerted on a ball of radius $r$ by just multiplying the pressure with the area
-\begin{equation}
-F = \frac{1}{3} \pi r^2 a T^4.
-\end{equation}
+%\begin{equation}
+%F = \frac{1}{3} \pi r^2 a T^4.
+%\end{equation}
+%
 As we can see, this force is highly temperature dependent.
@@
 In fact, if a cooling system based on liquid helium is installed, temperature can be brought down to about 4 K.
-Such a low temperature results in a radiation pressure of about $10^{-14} \, \mathrm{N} \, \mathrm{m}^{-2}$, which leads to a force on the balls in the order of $10^{-16}$ N.
+Such a low temperature results in a force on the balls in the order of $10^{-16}$ N.
 Compared to the gravitational force, this is orders of magnitude less and thus we don't have to worry about effects of radiation pressure.\\
 
-\textbf{Influence of the position measurement:} In general, one has to pay attention as soon as one undertakes a measurement on a physical system, because every measurement can disturb the system.
+\textbf{Influence of the position measurement:} 
+The photons of the laser that measures the position of the two balls exert an additional force.
+If a laser with a power of 1 mW is used and not more than five measurements every second are performed, the force on the balls is in the same order as the influence of thermal radiation and thus negligible too.\\
+%
+%In general, one has to pay attention as soon as one undertakes a measurement on a physical system, because every measurement can disturb the system.
 In this case we have a laser that measures the position of two masses which are in an orbit but the photons from the laser exerts an additional force on the masses.
@@
 In terms of the power $P$ of the laser and the area of the balls $A$, the radiation pressure is
-\begin{equation}
-\label{eq:radpress}
-p_r = \frac{P}{c\,A}.
-\end{equation}
-On behalf of minimizing the impact of the position measurement, a laser with small power should be used.
+%\begin{equation}
+%\label{eq:radpress}
+%p_r = \frac{P}{c\,A}.
+%\end{equation}
+%On behalf of minimizing the impact of the position measurement, a laser with small power should be used.
 If we assume a laser with a power of 1 mW, the radiation pressure is in the order of $10^{-10} \, \mathrm{N} \, \mathrm{m}^{-2}$.
@@
 If this pulse has a duration of less than roughly $0.1$ ms, its disturbing effect on the orbit is in the same range as the effect of thermal radiation and is thus negligible too.\\
-
+%
 \textbf{Coulomb force:}
@@
 A possible source of charges are cosmic rays or the solar wind, so they have to be protected as good as possible.
-If we want that the Coulomb force between the balls is in the order of $10^{-16} \,\mathrm{N}$ or smaller, and thus negligible, the maximal allowed charge on the balls is about $6 \cdot 10^{-14}\,\mathrm{C}$, which corresponds to roughly $4 \cdot 10^5$ elementary charges.\\
+If we want that the Coulomb force between the balls is in the same order as the effect of thermal radiation and thus negligible, the maximal allowed charge on the balls is about $6 \cdot 10^{-14}\,\mathrm{C}$, which corresponds to roughly $4 \cdot 10^5$ elementary charges.\\
 
-\textbf{Coriolis effect}
+\textbf{Coriolis effect:}
 \label{sec:coriolis}
@@
 If we imagine the spacecraft located stationary at a Lagrange point of the earth-sun system, it is situated in a rotating frame around the earth-sun barycenter.
-With respect to this frame, the balls are on their orbit in movement.
-Thus, there will be a Coriolis acceleration
+Since the balls are moving with respect to this frame, there will be a Coriolis acceleration
 \begin{equation}
@@
 \end{equation}
-Here $\vec{\omega}$ is the angular velocity vector of the rotating frame and $\dot{\vec{r}}$ is the velocity vector in the two-body system.
-Since we don't know the exact orientation of our system with respect to the earth-sun orbital plane, we will have to fit for it.\\
+In this formula $\vec{\omega}$ is the angular velocity vector of the rotating frame and $\dot{\vec{r}}$ is the velocity vector in the two-body system.\\
 
-\textbf{Centrifugal and tidal forces}
+\textbf{Centrifugal and tidal forces:}
 \label{sec:tidal}
-The two masses in the spacecraft should be in a free fall and only feel their respective gravitational attraction. But this is not possible to achieve for both masses simultaneously.\\
-Since we are in a non-inertial, rotating frame, there is a centrifugal force.
+The free fall condition is not possible to achieve for both masses simultaneously since we are in a non-inertial, rotating frame and therefore have to account for centrifugal forces.
 The centrifugal acceleration $\ddot{\vec{r}}_{\mathrm{Z}}$ is proportional to the distance vector $\vec{r}$ and scales with $\omega^2$, where $\omega$ is the angular velocity of the sun-earth reference frame:
@@
 Thus it scales the same way as the centrifugal force.
-The effect is off course tiny, since the system under consideration is much smaller compared to the earth-sun system.
 To estimate the magnitude of the centrifugal and tidal acceleration relative to the gravitational acceleration between the two balls, we find that their ratio is proportional to the orbital periods squared
@@
 here $P_\odot$ corresponds to one year, whereas $P$ is the orbital period of the two balls.
-So tidal and centrifugal effects are about $10^{-7}$ times smaller than the respective gravity of the two balls.
+So tidal and centrifugal effects are about $10^{-7}$ times smaller than the respective gravity of the two balls.\\
+
+\textbf{Gravitational field:}
+Much attention has to be paid to the effect of the gravitational field of the spacecraft itself and the measurement apparatus.
+This certainly can't be neglected, but with a clever design, its effects can be minimized.
+For example an almost spherically symmetric spacecraft would probably be a good choice.
+It should also be possible to calculate the gravitational field caused by the components of the spacecraft at the positions of the balls.
+Then one can correct the equation of motion by adding an extra term that is accounting for the gravitational field.
+\\
+A source of an additional gravitational field is earth's moon and the other planets in the solar system.
+Fortunately, for this we don't need to correct if the whole system, consisting of the spacecraft and the two-body system, is moving through space together.
+Although, the spacecraft should be able to correct its position around the two balls to avoid a collision.\\
+
+\section{Extracting $G$ from position measurement data}
+
+Now we are going to simulate position data of the two balls that the laser interferometry measurement would provide.
+From this data we then try to recover the parameters in the orbital equation of motion and thus also the gravitational constant.
+But first we have to find the orbital equation of motion for the two balls.\\
+
+\subsection{Orbital equation of motion}
+From Newtonian dynamics the equation of motion for a two-body system is given by 
+\begin{equation}
+\label{eq:eomeasy}
+\ddot{\vec{r}} = - \frac{G M\, \vec{r}}{r^3}.
+\end{equation}
+
 In choosing the reference frame such that the net force in the system barycenter is zero, we can correct with a term in the equations of motion for the two-body system, which is proportional to the distance.
@@
 The matrix $C$ has six individual components which are not exactly known presumably, we will set constraints to their values and then fit for them. \\
-
-\textbf{Gravitational field:}
-A source of an additional gravitational field is earth's moon and the other planets in the solar system.
-Fortunately, for this we don't need to correct if the whole system, consisting of the spacecraft and the two-body system, is moving on a geodesic through space.
-Although, the spacecraft should be able to correct its position around the two balls to avoid a collision.
-However, much attention has to be paid to the effect of the gravitational field of the spacecraft itself and the measurement apparatus.
-This certainly can't be neglected, but with a clever design, its effects can be minimized.
-For example an almost spherically symmetric spacecraft would probably be a good choice.
-Its gravitational field doesn't have to vanish perfectly, because first order corrections are absorbed in the matrix $C$, for which will be fitted anyway.
-\\
-If this is not practicable or the effects are still too large, it should be possible to calculate the gravitational field caused by the components of the spacecraft at the positions of the balls.
-Then one can correct the equation of motion by adding an extra term that is accounting for this gravitational field.
-\\
-
-\section{Extracting $G$ from simulated data}
-
-Now we are going to simulate position data of the two balls that the laser interferometry measurement would provide.
-From this data we then try to recover the parameters in the orbital equation of motion and thus also the gravitational constant.
-But first we have to find the orbital equation of motion for the two balls.\\
-
-\subsection{Orbital equation of motion}
-From Newtonian dynamics the equation of motion for a two-body system is given by 
-\begin{equation}
-\label{eq:eomeasy}
-\ddot{\vec{r}} = - \frac{G M\, \vec{r}}{r^3}.
-\end{equation}
 Here $M$ denotes the sum of the masses $m_1$ and $m_2$, $G$ is the gravitational constant and $r$ is the relative distance between the two bodies.
@@
 For simplicity we will abbreviate the product of $GM$ with $k$.\\
+
 Since our two-body system is in a rotating frame and there are perhaps other perturbations, we have to add the terms developed before for the Coriolis effect and the other corrections.

### 2017-10-21 manuscript_gravitationalconstant.tex
Section 3 modified

@@
 In Fig.~\ref{fig:Gmeasurements} we have plotted some of the most recent measurements of the gravitational constant.
-3 of them have been carried out using a torsion balance (), Schlamminger et al.
-used a beam balance and .......
-measured the separation of two simple pendulums in a gravitational field.
+Three of them have been carried out using a torsion balance (BIPM-14\cite{Quinn14}, UCI-14\cite{Newman14}, HUST-09\cite{Luo09}), UZur-06\cite{Schlamminger06} used a beam balance and JILA-10\cite{Parks10} measured the separation of two simple pendulums in a gravitational field.
 They all tried to measure the very weak gravitational force with a mechanical apparatus.
-The sixth measurement was performed under another approach, using cold atom interferometry.
+The sixth measurement (LENS-14\cite{Rosi14}) was performed under another approach, using cold atom interferometry.
 Its uncertainty is a lot larger than the others, but it could become more competitive in the future.
@@
 
-Now we are going to simulate position data of the two balls that the laser interferometry measurement would provide.
-From this data we then try to recover the parameters in the orbital equation of motion and thus also the gravitational constant.
+In this section we are going to show how the gravitational constant can be recovered from position data of the two balls that the laser interferometry measurement would provide.
 But first we have to find the orbital equation of motion for the two balls.\\
@@
 \subsection{Orbital equation of motion}
-From Newtonian dynamics the equation of motion for a two-body system is given by 
+From Newtonian dynamics the equation of motion for a clean two-body system is given by 
 \begin{equation}
@@
 \end{equation}
-
-In choosing the reference frame such that the net force in the system barycenter is zero, we can correct with a term in the equations of motion for the two-body system, which is proportional to the distance.
-Because we are in a 3-dimensional space, and possibly the influences of the different axis could mix, we have to multiply the distance vector $\vec{r}$ with a symmetric $3 \times 3$ matrix $C$, such that
+Here $M$ denotes the sum of the masses $m_1$ and $m_2$, $G$ is the gravitational constant and $r$ is the relative distance between the two bodies.
+For simplicity we will abbreviate the product of $GM$ with $k$.
+Since out two-body system is in a rotating frame we have to add the term developed before for the Coriolis acceleration as well as a correction term proportional to the distance accounting for centrifugal and tidal forces.
+This last term can be written with a
+symmetric $3 \times 3$ matrix $C$ as follows  
 \begin{equation}
@@
 \end{equation}
-The matrix $C$ has six individual components which are not exactly known presumably, we will set constraints to their values and then fit for them. \\
-Here $M$ denotes the sum of the masses $m_1$ and $m_2$, $G$ is the gravitational constant and $r$ is the relative distance between the two bodies.
-This equation just describes the motion of the two-body system.
-There are no forces acting on the center of mass, so the whole system is moving on a geodesic together with the spacecraft.
-For simplicity we will abbreviate the product of $GM$ with $k$.\\
-
-Since our two-body system is in a rotating frame and there are perhaps other perturbations, we have to add the terms developed before for the Coriolis effect and the other corrections.
-Thus, the equation of motion for the two balls looks as follows:
+It can be thought of as a first order expansion and therefore also include other possible minor perturbations.
+The reference frame is chosen such that the barycenter of the two-body system is force-free.
+So the full equation of motion for the two balls looks as follows:
 \begin{equation}
@@
 $\vec{\omega}$ is a constant vector that points in the direction of the rotation axis of the earth-sun reference frame.
-We don't know the exact respective orientation of these two planes, but this is no problem, since we will fit for them.
-We just need to know the orientation to some degree, to provide good starting points for the fit.
-The symmetric matrix $C$ has six independent components which account for tidal forces, centrifugal forces and other perturbations.
-Also here we don't have exact knowledge on how big these components will be and so we have to make an estimation and then fit for them.
-\\
+We will fit for $\vec{\omega}$, so we don't have to know it exactly before, but it can be estimated well and thus provides good starting points for the fit.
+The same is valid for the six components of the matrix $C$.\\
 
@@
 They correspond to 6 initial conditions, 6 components of the matrix $C$, 3 components of the vector $\vec{\omega}$ and the object of main interest, $k$,  which contains the gravitational constant ($k = GM$).
-Fitting for so many parameters is not an easy task, but it should be possible because the parameters are not completely unknown and thus we have good starting points for the fit.\\
+Fitting for so many parameters is not an easy task, but it should be possible because the parameters are not completely unknown.\\
 
@@
 First we have to specify the prior probability distribution, so to say what values for the 16 parameters in the equation of motion actually make sense.
-In table~\ref{tab:parameters}, estimated ranges for each parameters are shown.
 Then, for all 16 parameters a uniform distribution within these ranges and zero probability everywhere else is assumed as the prior probability distribution.
@@
 
-We start with the parameter $k$, which is the product of the gravitational constant $G$ and the total mass $M$.
-If we look at the measured values for the gravitational constant in Fig.~\ref{fig:Gmeasurements}, it is reasonable to constrain its numerical value in SI units to values between $6.671 \cdot 10^{-11}$ and $6.676 \cdot 10^{-11}$.
-The masses of the two balls can be determined to more than $10^{-5}$ in relative uncertainty, so they will not contribute to a larger uncertainty in $k$.
-If we take the consideration of balls with a mass of 6 kg, we can give a lower and an upper bound for $k$ which are displayed in table~\ref{tab:parameters}.\\
-
+We briefly explain in what range the values of the parameters are estimated and display it in table~\ref{tab:parameters}.
+For the parameter $k$, which is the product of the gravitational constant $G$ and the total mass $M$ we look at the current measured values for the gravitational constant in Fig.~\ref{fig:Gmeasurements}, it is reasonable to constrain its numerical value in SI units to values between $6.671 \cdot 10^{-11}$ and $6.676 \cdot 10^{-11}$.
+The masses of the two balls will not contribute to a larger uncertainty in $k$, we choose them to be 6 kg.\\
 The vector $\vec{\omega}$ accounts for the rotation of the reference frame.
@@
 As mentioned before, the $x$ and $y$ components are small, so to say roughly in the range of the uncertainty in $w_z$.\\
-
-To estimate the six components of the matrix $C$, we first state again that the barycentre of the two balls is in free fall.
+The main contribution to the tidal term goes with $\omega^2$ and lies in the orbital plane.
+We are free to choose the $x$ and $y$ axis, so we choose it such that it is in $x$-direction.
+The other five components then should be smaller, but we give some extra range to account for possible other perturbations.\\
+% 
+%To estimate the six components of the matrix $C$, we first state again that the barycentre of the two balls is in free fall.
 So at this point all forces cancel out.
@@
 Also other perturbations are assumed to be constant, at least during some orbits.
-The main component of this term should be perpendicular to the rotation axis, for which we have chosen the $z$ - axis.
+%The main component of this term should be perpendicular to the rotation axis, for which we have chosen the $z$ - axis.
 Since we are free to set the $x$ and $y$ axis in the orbital plane, we can choose it such that the main contribution lies in the $x$ - axis.
@@
 \\
-
-The initial values for the positions can be guessed very accurately, since the position is directly measured precisely.
-We choose the coordinate system such that the orbit is in the $x-y$ plane and the origin is at the barycenter of the two balls.
-We set the $x$ - axis such that at the beginning it corresponds to the radius and the $y$ - component is zero.
-If we choose the initial positions like this, the initial velocities in $x-$ and $z$ - direction are very small, they just arise from perturbations.
-The velocity in $y$ - direction can be calculated from Kepler's third law and is therefore also linked with the parameter $k$.\\
+%
+The initial values for the positions can be guessed very accurately, since they are directly measured precisely.
+The initial velocity can be calculated easily and matched to the initial positions, therefore also yielding narrow parameter ranges.\\
 
@@
 This uncertainty stays for a systematic error in the laser interferometry measurement and also random statistic noise.
-Its value is just an estimation, it would depend highly on the measurement system that has been used.
-There are laser interferometers, which are able to measure positions with an accuracy of $10\,\mathrm{nm}$.\cite{Loughridge13} \\
+Its value is just an estimation, it would depend highly on the measurement system that has been used.\\
 
@@
 Along the diagonal, the marginalized distribution for each parameter independently is shown.
-From this distribution we can then estimate its best value and uncertainty.
 In Fig.~\ref{fig:plotCorner4} an excerpt of the full corner plot is shown.
@@
 
-To arrive at a best value for $k$ and an uncertainty, we take the median and the percentiles corresponding to one sigma from this distribution of $k$. For this example we get:
+To arrive at a best value for $k$ and an uncertainty, we take the median and the percentiles corresponding to one sigma from the distribution of the parameter $k$. For this example we get:
 \begin{equation}\label{eq:kfit}
@@
 
+\bibitem{Quinn14} T.
+Quinn, C.
+Speake, H.
+Parks and R.
+Davis, ``The BIPM measurements of the Newtonian constant of gravitation $G$'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (September 2014)
+
+\bibitem{Newman14} R.
+Newman, M.
+Bantel, E.
+Berg and W.
+Cross, ``A measurement of $G$ with a cryogenic torsion pendulum'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (September 2014)
+
+\bibitem{Luo09} J.
+Luo, W.
+Liu, L.
+Tu, C.
+Shao, L.Liu, S.
+Yang, Q.
+Li and Y.
+Zhang, ``Determination of the Newtonian gravitational constant $G$ with time-of-swing method'', \textit{Phys.
+Rev.
+Lett.}, 102:240801 (June 2009)
+
+\bibitem{Schlamminger06} S.
+Schlamminger, E.
+Holzschuh, W.
+Kündig, F.
+Nolting, R.E.
+Pixley, J.
+Schnurr and U.
+Straumann, ``Measurement of Newton's gravitational constant", \textit{Phys.
+Rev.
+D}, 74:082001 (October 2009)
+
+\bibitem{Parks10} H.V. Parks and J.E. Faller, ``Simple pendulum determination of the gravitational constant", \textit{Phys. Rev. Lett.}, 105:110801 (September 2010)
+
+\bibitem{Rosi14} G.
+Rosi, F.
+Sorrentino, L.
+Cacciapuoti, M.
+Prevedelli and G.M.
+Tino, ``Precision measurement of the Newtonian gravitational constant using cold atoms", \textit{Nature}, 510:518-521 (June 2014)
+
 \bibitem{esopycoffee} Fast and easy-to-implement Markov Chain Monte Carlo with the emcee package, ESO PyCoffee (2014),

### 2017-10-22 manuscript_gravitationalconstant.tex
Conclusion added, references added

@@
 introduction to the new SI, we refer the reader to the article on the
-``LEGO watt balance''[2015AmJPh..83..913C].
+``LEGO watt balance''[2015AmJPh..83..913C]\cite{Chao15}.
 
@@
 quantum gravity.  But extreme scales do not harm if they are only part
-of some pression, as they are here.  The Planck mass is small but
+of some expression, as they are here.  The Planck mass is small but
 microscopically measurable: $\sim20\mu\mathrm{g}$.  This is of the
@@
 
-A useful way to look at the samples of the posterior returned by the MCMC is doing a corner plot using a Python module named \textit{corner}\cite{corner}.
-The corner plot shows all the one and two dimensional projections of the posterior probability distributions and demonstrates quickly the covariances between parameters.
-Along the diagonal, the marginalized distribution for each parameter independently is shown.
-In Fig.~\ref{fig:plotCorner4} an excerpt of the full corner plot is shown.
-Here we only depict the parameters $x_0$, $v_{y_0}$, $\omega_z$, $C_{xx}$ and $k$.
-These are the more important ones, because for example the main contribution to $\vec{\omega}$ comes from its $z$-component.\\
-
 \begin{figure}[h]
@@
 
-To arrive at a best value for $k$ and an uncertainty, we take the median and the percentiles corresponding to one sigma from the distribution of the parameter $k$. For this example we get:
-\begin{equation}\label{eq:kfit}
-k = \left( 8.0088006 \, \substack{+0.0000005 \\ -0.0000008}\, \right) \cdot 10^{-10}
-\end{equation}
-Now we divide $k$ by the total mass of the two balls.
-Note, that we assume, that the uncertainty on the mass of the balls does not contribute to a larger uncertainty on $G$, because their mass should be determinable to a relative uncertainty of about $10^{-8}$, whereas the one of $k$ is roughly $10^{-7}$.
-We change the way to write the uncertainty from the 0.16 and 0.84 percentiles to the usual standard deviation, while adding some margin.
-With units put back in, we arrive at the following value for the gravitational constant $G$:
+A useful way to look at the samples of the posterior returned by the MCMC is doing a corner plot using a Python module named \textit{corner}\cite{corner}.
+The corner plot shows all the one and two dimensional projections of the posterior probability distributions and demonstrates quickly the covariances between parameters.
+Along the diagonal, the marginalized distribution for each parameter independently is shown.
+In Fig.~\ref{fig:plotCorner4} an excerpt of the full corner plot is shown. \\
+%
+%Here we only depict the parameters $x_0$, $v_{y_0}$, $\omega_z$, $C_{xx}$ and $k$.
+These are the more important ones, because for example the main contribution to $\vec{\omega}$ comes from its $z$-component.\\
+%
+
+To arrive at a best value with uncertainty for the gravitational constant, we take the mean and standard deviation of the marginalized distribution of the parameter $k$ and divide by the total mass of the balls.
+In this example the relative uncertainty of $k$ is roughly $10^{-7}$, so if the masses are measured to about the same precision, we can write for the gravitational constant $G$:
 \begin{equation}\label{Gfit}
@@
 
+%
+%we take the median and the percentiles corresponding to one sigma from the distribution of the parameter $k$. For this example we get:
+%\begin{equation}\label{eq:kfit}
+%k = \left( 8.0088006 \, \substack{+0.0000005 \\ -0.0000008}\, \right) \cdot 10^{-10}
+%\end{equation}
+%Now we divide $k$ by the total mass of the two balls.
+Note, that we assume, that the uncertainty on the mass of the balls does not contribute to a larger uncertainty on $G$, because their mass should be determinable to a relative uncertainty of about $10^{-8}$, whereas the one of $k$ is roughly $10^{-7}$.
+We change the way to write the uncertainty from the 0.16 and 0.84 percentiles to the usual standard deviation, while adding some margin.
+With units put back in, we arrive at the following value for the gravitational constant $G$:
+%\begin{equation}\label{Gfit}
+%G = \left(6.674005 \pm 0.000001 \right) \cdot 10^{-11}  \frac{\mathrm{m}^3}{\mathrm{kg \, s}^2}
+%\end{equation}
+%This corresponds to a relative uncertainty of $1.5 \cdot 10^{-7}$ or 15 parts in a hundred million.\\
+%
+
 \section{Conclusion}
+We have proposed a new way to measure the gravitational constant $G$ and estimated on what order of magnitude different disturbing effects occur and if one has to correct for them.
+We then simulated measurement data and showed how to extract the gravitational constant.
+Based on our estimations, it should be possible to measure the gravitational constant to about $10^{-7}$ relative uncertainty.
+This is a about a factor of 300 better than today's recommended CODATA value.\\
+If we are a bit optimistic, a further increase in precision is not out of reach, so that about the same relative uncertainty as for Planck's constant $h$ ($1.2 \cdot 10^{-8}$)\cite{CODATA16} could be achieved.
+This then would allow to redefine the kilogram as an integer multiple of the Planck mass.\\
 
@@
 
-Appendices are for material that is needed for completeness but
-not sufficiently interesting to include in the main body of the paper.  Most
-articles don't need any appendices, but feel free to use them when
-appropriate.  This sample article needs an appendix only to illustrate how 
-to create an appendix.
+%Appendices are for material that is needed for completeness but
+%not sufficiently interesting to include in the main body of the paper.  Most
+%articles don't need any appendices, but feel free to use them when
+%appropriate.  This sample article needs an appendix only to illustrate how 
+%to create an appendix.
 
 \begin{acknowledgments}
-
 Need acknowledgments?
@@
 
-\bibitem{vanRavenzwaaij16} D. van Ravenzwaji, and P. Cassey, and S. D. Brown, ``A simple introduction to Markov Chain Monte-Carlo sampling,'' 
-Psychonomic Bulletin {\&} Review, 1--12 (2016).  
-% Note that the issue number (10) in this citation is required, because
-% each issue of Physics Today starts over with page 1.  Also note the use of
-% an en-dash (--), not a hyphen (-), for the page range.
+\bibitem{Chao15} L.S.
+Chao, S.
+Schlamminger, D.B.
+Newell, J.R.
+Pratt, F.
+Seifert, X.
+Zhang, G.
+Sineriz, M.
+Liu and D.
+Haddad, ``A LEGO Watt balance: An apparatus to determine a mass based on the new SI", \textit{American Journal of Physics}, 83:11:913--922 (August 2015).
 
@@
 
-\bibitem{Tomilin99} D. K. Tomilin, ``Fine-structure constant and dimension analysis,'' 
-European Journal of Physics (20.5), L39 (1999).
-
-\bibitem{Fischer16} J. Ullrich, and J. Fischer, ``The new system of units,'' 
-Nature Physics (12.1), 4--7 (2016).
-
 \bibitem{Quinn14} T.
@@
 Parks and R.
-Davis, ``The BIPM measurements of the Newtonian constant of gravitation $G$'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (September 2014)
+Davis, ``The BIPM measurements of the Newtonian constant of gravitation $G$'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (September 2014).
 
@@
 Berg and W.
-Cross, ``A measurement of $G$ with a cryogenic torsion pendulum'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (September 2014)
+Cross, ``A measurement of $G$ with a cryogenic torsion pendulum'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (September 2014).
 
@@
 Rev.
-Lett.}, 102:240801 (June 2009)
+Lett.}, 102:240801 (June 2009).
 
@@
 Rev.
-D}, 74:082001 (October 2009)
+D}, 74:082001 (October 2009).
 
-\bibitem{Parks10} H.V. Parks and J.E. Faller, ``Simple pendulum determination of the gravitational constant", \textit{Phys. Rev. Lett.}, 105:110801 (September 2010)
+\bibitem{Parks10} H.V. Parks and J.E. Faller, ``Simple pendulum determination of the gravitational constant", \textit{Phys. Rev. Lett.}, 105:110801 (September 2010).
 
@@
 Prevedelli and G.M.
-Tino, ``Precision measurement of the Newtonian gravitational constant using cold atoms", \textit{Nature}, 510:518-521 (June 2014)
+Tino, ``Precision measurement of the Newtonian gravitational constant using cold atoms", \textit{Nature}, 510:518-521 (June 2014).
 
@@
 \url{<http://eso-python.github.io/ESOPythonTutorials/ESOPythonDemoDay8_MCMC_with_emcee.html>}.
+
+\bibitem{vanRavenzwaaij16} D. van Ravenzwaji, and P. Cassey, and S. D. Brown, ``A simple introduction to Markov Chain Monte-Carlo sampling,'' 
+Psychonomic Bulletin {\&} Review, 1--12 (2016).
 
@@
 
+\bibitem{CODATA16} P.J. Mohr, D.B. Newell and B.N. Taylor, ``CODATA recommended values of the fundamental physical constants: 2014*, \textit{Reviews of Modern Physics}, 88(3):035009 (July 2016).
+
 \end{thebibliography}

### 2017-10-24 manuscript_gravitationalconstant.tex
modified plot of G measurements
Table 1 reduced from 4 to 3 columns

@@
 The cavity should shield the two-body system from environmental influences.
-The spacecraft is then put in space, preferably to a Lagrange point of the earth-sun system, in order to prevent large inertial forces.\\
+The spacecraft is then put in space, preferably to a Lagrange point of the earth-sun system, in order to prevent large tidal forces.\\
 
@@
 \begin{equation}
-F = \frac{1}{3} \pi r^2 \sigma_a T^4.
+F = \frac{8 \pi^6 r^2 {k_\mathrm{B}}^4 T^4}{45 c^3 h^3}.
 \end{equation}
-with
-\begin{equation}
-\label{eq:a}
-\sigma_a = \frac{8 \pi^5 {k_\mathrm{B}}^4}{15 c^3 h^3}
-\end{equation}
-being a constant that follows from Planck's radiation law.
 %
@@
 	\centering
-	\caption{This table shows the ranges in which the parameters numerical values in SI units are estimated to make sense and and also the value which was chosen to generate data.}
+	\caption{This table shows the ranges in which the parameters numerical values in SI units are estimated to make sense and the value which was chosen to generate data.}
 	\begin{ruledtabular}
-		\begin{tabular}{l c c c}
+		\begin{tabular}{l c c}
 			% The codes above determine the horizontal alignment in each column.
@@
 			% therefore requires a width specification, in this case 5 centimeters.
-			Parameter & min. value & max. value & chosen value \\
+			parameter & range & chosen value \\
 			\hline	% horizontal line to separate headings from data
-			$k$ & $8.0052 \cdot 10^{-10}$ & $8.0112 \cdot 10^{-10}$ & $8.0088 \cdot 10^{-10}$ \\
-			$\omega_x$ & $-1.0 \cdot 10^{-8}$ & $-1.0 \cdot 10^{-8}$ & $0.02 \cdot 10^{-8}$ \\
-			$\omega_y$ & $-1.0 \cdot 10^{-8}$ & $-1.0 \cdot 10^{-8}$ & $-0.03 \cdot 10^{-8}$ \\
-			$\omega_z$ & $1.95 \cdot 10^{-7}$ & $2.05 \cdot 10^{-7}$ & $1.996 \cdot 10^{-7}$ \\
-			$C_{xx}$ & 0 & $5.0 \cdot 10^{-14}$ & $3.8 \cdot 10^{-14}$ \\
-			$C_{yy}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $0.3 \cdot 10^{-14}$ \\
-			$C_{zz}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $-0.2 \cdot 10^{-14}$ \\
-			$C_{xy} = C_{yx}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $0.3 \cdot 10^{-14}$ \\
-			$C_{yz} = C_{zy}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $0.1 \cdot 10^{-14}$ \\
-			$C_{xz} = C_{zx}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $-0.4 \cdot 10^{-14}$ \\
-			$x_0$ & $0.15$ & $0.1499999$ & $0.1500001$ \\
-			$y_0$ & $-1.0 \cdot 10^{-7}$ & $1.0 \cdot 10^{-7}$ & $0.0$ \\ 
-			$z_0$ & $-1.0 \cdot 10^{-7}$ & $1.0 \cdot 10^{-7}$ & $0.0$ \\ 
-			$v_{x_0}$ & $-1.0 \cdot 10^{-7}$ & $1.0 \cdot 10^{-7}$ & $0.0$ \\ 
-			$v_{y_0}$ & $7.30 \cdot 10^{-7}$ & $7.31 \cdot 10^{-7}$ & $7.30698296 \cdot 10^{-5}$ \\
-			$v_{z_0}$ & $-1.0 \cdot 10^{-7}$ & $1.0 \cdot 10^{-7}$ & $0.0$ \\
+			$k$ & $(8.0052$--$8.0112) \cdot 10^{-10}$ & $8.0088 \cdot 10^{-10}$ \\
+			$\omega_x$ & $\pm 1.0 \cdot 10^{-8}$ & $0.02 \cdot 10^{-8}$ \\
+			$\omega_y$ & $\pm 1.0 \cdot 10^{-8}$ & $-0.03 \cdot 10^{-8}$ \\
+			$\omega_z$ & $(1.95$--$2.05) \cdot 10^{-7}$ & $1.996 \cdot 10^{-7}$ \\
+			$C_{xx}$ & $0$--$5.0 \cdot 10^{-14}$ & $3.8 \cdot 10^{-14}$ \\
+			$C_{yy}$ & $\pm 10^{-14}$ & $0.3 \cdot 10^{-14}$ \\
+			$C_{zz}$ & $\pm 10^{-14}$ & $-0.2 \cdot 10^{-14}$ \\
+			$C_{xy} = C_{yx}$ & $\pm 10^{-14}$ & $0.3 \cdot 10^{-14}$ \\
+			$C_{yz} = C_{zy}$ & $\pm 10^{-14}$ & $0.1 \cdot 10^{-14}$ \\
+			$C_{xz} = C_{zx}$ & $\pm 10^{-14}$ & $-0.4 \cdot 10^{-14}$ \\
+			$x_0$ & $0.15 \pm 10^{-7}$ & $0.15$ \\
+			$y_0$ & $\pm 10^{-7}$ & $0.0$ \\ 
+			$z_0$ & $\pm 10^{-7}$ & $0.0$ \\ 
+			$v_{x_0}$ & $\pm 10^{-7}$ & $0.0$ \\ 
+			$v_{y_0}$ & ($7.30$--$7.31) \cdot 10^{-7}$ & $7.30698296 \cdot 10^{-5}$ \\
+			$v_{z_0}$ & $\pm 10^{-7}$ & $0.0$ \\
 		\end{tabular}

### 2017-10-24 manuscript_gravitationalconstant.tex
minor changes in literature references

@@
 
-\bibitem{Chao15} L.S.
+\bibitem{Chao15} L.
+S.
 Chao, S.
-Schlamminger, D.B.
-Newell, J.R.
+Schlamminger, D.
+B.
+Newell, J.
+R.
 Pratt, F.
@@
 Liu and D.
-Haddad, ``A LEGO Watt balance: An apparatus to determine a mass based on the new SI", \textit{American Journal of Physics}, 83:11:913--922 (August 2015).
+Haddad, ``A LEGO Watt balance: An apparatus to determine a mass based on the new SI", \textit{American Journal of Physics}, 83:11:913--922 (2015).
 
@@
 Parks and R.
-Davis, ``The BIPM measurements of the Newtonian constant of gravitation $G$'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (September 2014).
+Davis, ``The BIPM measurements of the Newtonian constant of gravitation $G$'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (2014).
 
@@
 Berg and W.
-Cross, ``A measurement of $G$ with a cryogenic torsion pendulum'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (September 2014).
+Cross, ``A measurement of $G$ with a cryogenic torsion pendulum'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (2014).
 
@@
 Tu, C.
-Shao, L.Liu, S.
+Shao, L.
+Liu, S.
 Yang, Q.
@@
 Rev.
-Lett.}, 102:240801 (June 2009).
+Lett.}, 102:240801 (2009).
 
@@
 Kündig, F.
-Nolting, R.E.
+Nolting, R.
+E.
 Pixley, J.
@@
 Rev.
-D}, 74:082001 (October 2009).
+D}, 74:082001 (2009).
 
-\bibitem{Parks10} H.V. Parks and J.E. Faller, ``Simple pendulum determination of the gravitational constant", \textit{Phys. Rev. Lett.}, 105:110801 (September 2010).
+\bibitem{Parks10} H. V. Parks and J. E. Faller, ``Simple pendulum determination of the gravitational constant", \textit{Phys. Rev. Lett.}, 105:110801 (2010).
 
@@
 Cacciapuoti, M.
-Prevedelli and G.M.
-Tino, ``Precision measurement of the Newtonian gravitational constant using cold atoms", \textit{Nature}, 510:518-521 (June 2014).
+Prevedelli and G.
+M.
+Tino, ``Precision measurement of the Newtonian gravitational constant using cold atoms", \textit{Nature}, 510:518--521 (2014).
 
@@
 
-\bibitem{vanRavenzwaaij16} D. van Ravenzwaji, and P. Cassey, and S. D. Brown, ``A simple introduction to Markov Chain Monte-Carlo sampling,'' 
+\bibitem{vanRavenzwaaij16} D. van Ravenzwaji, P. Cassey and S. D. Brown, ``A simple introduction to Markov Chain Monte-Carlo sampling,'' 
 Psychonomic Bulletin {\&} Review, 1--12 (2016).
 
-\bibitem{Loughridge13} R. Loughridge, and D. Y. Abramovitch, ``A tutorial on laser interferometry for precision measurements,'' 
+\bibitem{Loughridge13} R. Loughridge and D. Y. Abramovitch, ``A tutorial on laser interferometry for precision measurements,'' 
 American Control Conference, 3686--3703 (2013).
 
-\bibitem{corner} Daniel Foreman-Mackey, ``corner.py: Scatterplot matrices in Python,'' 
+\bibitem{corner} D. Foreman-Mackey, ``corner.py: Scatterplot matrices in Python,'' 
 The Journal of Open Source Software (10), (2016).
 
-\bibitem{CODATA16} P.J. Mohr, D.B. Newell and B.N. Taylor, ``CODATA recommended values of the fundamental physical constants: 2014*, \textit{Reviews of Modern Physics}, 88(3):035009 (July 2016).
+\bibitem{CODATA16} P. J. Mohr, D. B. Newell and B. N. Taylor, ``CODATA recommended values of the fundamental physical constants: 2014*, \textit{Reviews of Modern Physics}, 88(3):035009 (2016).
 

### 2017-10-26 manuscript_gravitationalconstant.tex
editing text

@@
 significant change from its current value.  The practical hurdle is
-measuring $G$ three or four orders of magnitude than presently known,
-so as to find the unknown digits xxxx.  We study a possible scenario
-for doing so with an artificial two-body orbit.  Requirements for
-suppressing perturbing effects (notably tidal forces and radiation
-pressure), and obtaining the desired signal-to-noise are estimated.
+measuring $G$ three or four orders of magnitude better than currently
+known, so as to find the unknown digits xxxx.  We study a possible
+scenario for doing so with an artificial two-body orbit.  The cleanest
+(admittedly, not the cheapest) option is to place the system on a
+trojan orbit to minimize external gravitational perturbations, and
+enclose it in a cavity chilled to liquid-helium temperatures, to
+suppress radiation pressure.  Data analysis would involve
+marginalizing over at least 15~nuisance parameters (6~for orbital
+parameters and 9~for fictitious forces) but that, we show, is
+feasible.
 \end{abstract}
@@
 
-The reform of SI units to use quantum standards is an ongoing `news
-story' in physics.  At the heart of the reform are two quantum
+The reform of SI units to use quantum standards is an ongoing ``news
+story'' in physics.  At the heart of the reform are two quantum
 phenomena that appear on macroscopic scales: the Josephson effect
@@
 watt balance, precisely compares electrical and mechanical power, thus
-enabled mass to be standardized in terms of $h$.  For an simple
+enabled mass to be standardized in terms of $h$.  For a simple
 introduction to the new SI, we refer the reader to the article on the
-``LEGO watt balance''[2015AmJPh..83..913C]\cite{Chao15}.
+``LEGO watt balance''\cite{Chao15}.
 
@@
 both gravity and quantum mechanics in a unit system comes from
-Planck\cite{Planck99}.  In the process of working towards the
-radiation law, Planck realized that $c,G,h$ and the Boltzmann constant
-$k_B$ (in his notation $G\rightarrow f$, $h\rightarrow b$,
-$h/k_B\rightarrow a$) naturally define units for mass, length, time,
-and temperature.  (Planck remarked that such units would be meaningful
-even in non-human and extraterrestrial cultures.)
+Planck.\cite{Planck99} In the process of working towards the radiation
+law, Planck realized that $c,G,h$ and the Boltzmann constant $k_B$ (in
+his notation $G\rightarrow f$, $h\rightarrow b$, $h/k_B\rightarrow a$)
+naturally define units for mass, length, time, and temperature.
+Indeed, Planck remarked that such units would be meaningful even in
+non-human and extraterrestrial cultures.
 
@@
 the Planck mass, Planck length, and so on.  (They are actually
-$\sqrt{2\pi}$ times Planck's definitions.)  Extension to electrical
-units is straightforward, but we will not discuss it here.  The Planck
-length, time, and temperature in themselves are extreme scales, not
-probed by any known physical process, and presumably the regime of
-quantum gravity.  But extreme scales do not harm if they are only part
-of some expression, as they are here.  The Planck mass is small but
-microscopically measurable: $\sim20\mu\mathrm{g}$.  This is of the
-same order as the uncertainty in the prototype kilogram itself.  Hence
-the kilogram could be redefined as an integer multiple of the Planck
-mass, without significantly perturbing its value.
+$\sqrt{2\pi}$ smaller than Planck's definitions.)  Extension to
+electrical units is straightforward, but we will not discuss it here.
+The Planck length, time, and temperature in themselves are extreme
+scales, not probed by any known physical process, and presumably the
+regime of quantum gravity.  But extreme scales do not harm if they are
+only part of some expression, as they are here.  The Planck mass is
+small but microscopically measurable: $\sim20\mu\mathrm{g}$.  This is
+of the same order as the uncertainty in the prototype kilogram itself.
+Hence the kilogram could be redefined as an integer multiple of the
+Planck mass, without significantly perturbing its value.
 
@@
 kilogram practicable.  In this paper, we study a scenario which may
-make such an improvement possible.  A Planckian second not a prospect
-with anything like present technology, because demands on the time
-standard are more stringent still.\\
+make such an improvement possible.  The same process would suffice to
+move the Kelvin scale to a Planckian basis as well.  A Planckian
+second or metre, however, are not a prospect with anything like
+present technology, because demands on the time standard are more
+stringent still.
 
@@
 
-In Fig.~\ref{fig:Gmeasurements} we have plotted some of the most recent measurements of the gravitational constant.
-Three of them have been carried out using a torsion balance (BIPM-14\cite{Quinn14}, UCI-14\cite{Newman14}, HUST-09\cite{Luo09}), UZur-06\cite{Schlamminger06} used a beam balance and JILA-10\cite{Parks10} measured the separation of two simple pendulums in a gravitational field.
-They all tried to measure the very weak gravitational force with a mechanical apparatus.
-The sixth measurement (LENS-14\cite{Rosi14}) was performed under another approach, using cold atom interferometry.
-Its uncertainty is a lot larger than the others, but it could become more competitive in the future.
-However, a brief glance on the plotted measurements shows the disagreement of current $G$-values and suggests a demand for new, potentially different techniques.\\
+In Fig.~\ref{fig:Gmeasurements} we plot the best-known recent
+measurements of the gravitational constant. Three of them
+(BIPM-14,\cite{Quinn14} UCI-14,\cite{Newman14}, and
+HUST-09\cite{Luo09}) were carried out using a torsion balance, whereas
+UZur-06\cite{Schlamminger06} used a beam balance, and
+JILA-10\cite{Parks10} measured the separation of two simple pendulums
+in a gravitational field. They all tried to measure the very weak
+gravitational force with a mechanical apparatus. The sixth measurement
+(LENS-14\cite{Rosi14}) was performed with another approach, using cold
+atom interferometry. Its uncertainty is a lot larger than the others,
+but it could become more competitive in the future. However, a brief
+glance on the plotted measurements shows the disagreement of current
+$G$-values and suggests a demand for new, potentially different
+techniques.
 
-\subsection{Description of new measurement}
-Newton's law of gravitation does not only explain why an apple falls down from a tree, it also explains orbits.
-If one has two bodies of masses $m_1$ and $m_2$, on which the only force acting is their respective gravitational attraction, they will orbit around their common barycenter in an ellipse described by Kepler's laws.
-The third law, given in Eq.~(\ref{eq:kepler3}), states that the square of the orbital period $P$ is directly proportional to the cube of the semimajor axis $a$.
-In this proportionality factor, the gravitational constant $G$ appears.
+\subsection{An artificial two-body gravitating system}
+Newton's law of gravitation does not only explain why an apple falls
+down from a tree, it also explains orbits. If one has two bodies of
+masses $m_1$ and $m_2$, on which the only force acting is their
+respective gravitational attraction, they will orbit around the common
+common center of mass, with the relative vector tracing an ellipse
+described by Kepler's laws. The third law, relates the
+orbital period $P$ to semimajor axis $a$ of the ellipse, as
 \begin{equation}\label{eq:kepler3}
@@
 \end{equation}
-If one can measure the position of the two masses very accurately and thus knows the orbit, it is possible to deduce the gravitational constant. 
-So what we need is a freely falling two-body system.
-The only way to achieve this over some time, is to go to space.
-Thus, one has to design a spacecraft involving a cavity that contains the two masses and a position measurement apparatus.
-The cavity should shield the two-body system from environmental influences.
-The spacecraft is then put in space, preferably to a Lagrange point of the earth-sun system, in order to prevent large tidal forces.\\
+with the gravitational constant $G$ appearing in the proportionality
+factor.  If one can measure the position of the two masses very
+accurately and thus know the orbit, it is possible to deduce the
+gravitational constant.  So what we need is a freely-falling two-body
+system. The only way to achieve this over some time, is to go into
+space. Thus, one has to design a spacecraft with a cavity that
+contains the two masses and a position measurement apparatus. The
+cavity should shield the two-body system from environmental
+influences. The spacecraft is then put in space, at a location where
+tidal forces are minimal.  The stable Lagrange points of the Earth-Sun
+system (that is, $L_4$ or $L_5$, also known as the Earth-Trojan
+locations) would be suitable.
 
@@
 
-To get a feeling what the dimensions of such an experiment could be, choose for example lead balls with a diameter of about 10 cm, their mass then is about 6 kg.
-If one then chooses a semimajor axis of 15 cm, the orbital period would be roughly 3.5 hours and the gravitational force acting between the two bodies is of order $10^{-8}$ N.
-In Fig.~\ref{fig:sketch} we show a sketch on how this would look like.
-For getting an improvement in the precision of the gravitational constant, the positions of the two balls have to be known very accurately.
-Best suitable would probably be a laser interferometry system, which can yield precisions down to some nanometers.\cite{Loughridge13}
-The main difference to other techniques is that position measurements can be very accurate compared to directly measuring the gravitational force.
-This new kind of measurement of the gravitational constant appears simple, but it brings various difficulties with it.
-It is practically impossible to have a clean system, where only the respective gravitational force is acting between the two bodies, so one has to find out what effects could possibly disturb the system and then either make them as small as possible or correct for them.
-\\
+To get a feeling what the dimensions of such an experiment could be,
+choose for example lead balls with a diameter of about 10~cm, their
+mass then is about 6~kg. If one then chooses a semimajor axis of
+15~cm, the orbital period would be roughly 3.5~hours and the
+gravitational force acting between the two bodies is of order
+$10^{-8}$N.  In Fig.~\ref{fig:sketch} we show a sketch on how this
+would look like.  To follow the mutual orbit of the two balls, best
+would be a laser interferometry system, which can yield precisions
+down to some nanometers.\cite{Loughridge13}
+
+Such a system, if it could be set up, promises two advantages.  One is
+the avoidance of any mechanical contact with the gravitating parts of
+the experiment.  The other advantage lies in the behavior of signal
+and noise.  The signal, which is essentially the distance travelled,
+is proportional to time.  The noise, however, would be almost
+time-independent.  This suggests that signal-to-noise would be
+proportional to the length of the experiment, until it was limited by
+systematic error.  The achievable accuracy would therefore depend
+entirely on how well external perturbations to the gravitational
+two-body problem could be eliminated, or corrected for.  In following,
+we consider the expected perturbations.
 
@@
 \end{document}
+
+@INPROCEEDINGS{2016APS..APR.R5001S,
+   author = {{Schlamminger}, S.},
+    title = ``{Measurements of the gravitational constant - why we need new ideas}'',
+booktitle = {APS April Meeting Abstracts},
+     year = 2016,
+    month = mar,
+   adsurl = {http://adsabs.harvard.edu/abs/2016APS..APR.R5001S},
+  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
+}

### 2017-10-27 manuscript_gravitationalconstant.tex
editing

@@
 introduction to the new SI, we refer the reader to the article on the
-``LEGO watt balance''\cite{Chao15}.
+``LEGO watt balance''.\cite{Chao15}
 
@@
 
-\textbf{Radiation pressure:} The envelope of the cavity needs to protect the two body-system from the constant bombardment of radiation and charged particles from the sun.
-Since the activity of the sun varies much, the spacecraft must be able to correct its position around the freely falling masses inside the cavity.\\
+\textbf{Radiation pressure:} The envelope of the cavity needs to protect the two body-system from the constant bombardment of radiation and charged particles from the Sun.
+Since the activity of the Sun varies much, the spacecraft must be able to correct its position around the freely falling masses inside the cavity.\\
 Furthermore, there is thermal radiation inside the cavity, that could disturb the orbit.
@@
 Since the electromagnetic force is orders of magnitude stronger than the gravitational force, the balls must be absolutely neutral.
-A possible source of charges are cosmic rays or the solar wind, so they have to be protected as good as possible.
-If we want that the Coulomb force between the balls is in the same order as the effect of thermal radiation and thus negligible, the maximal allowed charge on the balls is about $6 \cdot 10^{-14}\,\mathrm{C}$, which corresponds to roughly $4 \cdot 10^5$ elementary charges.\\
+A possible source of charges are cosmic rays or the solar wind, so the two bodies have to be adequately shielded by the enclosing shell.
+If we want that the Coulomb force between the balls is in the same order as the effect of thermal radiation and thus negligible, the maximal allowed charge on the balls is about $6 \cdot 10^{-14}\,\mathrm{C}$, which corresponds to roughly $4 \cdot 10^5$ elementary charges.
 
@@
 The Coriolis force is a fictitious force which only acts on moving bodies in a rotating reference frame.
-If we imagine the spacecraft located stationary at a Lagrange point of the earth-sun system, it is situated in a rotating frame around the earth-sun barycenter.
+If we imagine the spacecraft located stationary at a Lagrange point of the Earth-Sun system, it is situated in a rotating frame around the Earth-Sun barycenter.
 Since the balls are moving with respect to this frame, there will be a Coriolis acceleration
@@
 \end{equation}
-In this formula $\vec{\omega}$ is the angular velocity vector of the rotating frame and $\dot{\vec{r}}$ is the velocity vector in the two-body system.\\
+In this formula $\vec{\omega}$ is the angular velocity vector of the rotating frame and $\dot{\vec{r}}$ is the velocity vector in the two-body system.
 
@@
 The free fall condition is not possible to achieve for both masses simultaneously since we are in a non-inertial, rotating frame and therefore have to account for centrifugal forces.
-The centrifugal acceleration $\ddot{\vec{r}}_{\mathrm{Z}}$ is proportional to the distance vector $\vec{r}$ and scales with $\omega^2$, where $\omega$ is the angular velocity of the sun-earth reference frame:
+The centrifugal acceleration $\ddot{\vec{r}}_{\mathrm{Z}}$ is proportional to the distance vector $\vec{r}$ and scales with $\omega^2$, where $\omega$ is the angular velocity of the Sun-Earth reference frame:
 \begin{equation}
@@
 \end{equation}
-On the other hand, there are tidal forces.
-Imagine if one mass is closer to the sun-earth barycenter, the gravitational force on it is slightly bigger than on the other mass.
-This results in a correction proportional to the distance too.
+In addition, there are tidal forces.
+If one mass is closer to the Sun, the gravitational force on it is slightly bigger than on the other mass.
+This results in a force perturbation, which is also proportional to $r$.
 One can approximate the tidal acceleration as
@@
 \end{equation}
-In this equation $M_\odot$ is the solar mass and $R$ is the radius of the orbit around the sun.
-With Kepler's third law one can rewrite the tidal acceleration as a function of the orbital period squared of the sun-earth reference frame.
+In this equation $M_\odot$ is the solar mass and $R$ is the radius of the orbit around the Sun.
+With Kepler's third law one can rewrite the tidal acceleration as a function of the orbital period squared of the Sun-Earth reference frame.
 Thus it scales the same way as the centrifugal force.
@@
 \end{equation}
-here $P_\odot$ corresponds to one year, whereas $P$ is the orbital period of the two balls.
-So tidal and centrifugal effects are about $10^{-7}$ times smaller than the respective gravity of the two balls.\\
+where $P_\odot$ corresponds to one year, whereas $P$ is the orbital period of the two balls.
+So tidal and centrifugal effects are about $10^{-7}$ times smaller than the respective gravity of the two balls.
 
@@
 \\
-A source of an additional gravitational field is earth's moon and the other planets in the solar system.
+A source of an additional gravitational field is Earth's moon and the other planets in the solar system.
 Fortunately, for this we don't need to correct if the whole system, consisting of the spacecraft and the two-body system, is moving through space together.
@@
 We choose our coordinate system such that the orbital plane of the two-body system is in the $x-y$ plane.
-$\vec{\omega}$ is a constant vector that points in the direction of the rotation axis of the earth-sun reference frame.
+$\vec{\omega}$ is a constant vector that points in the direction of the rotation axis of the Earth-Sun reference frame.
 We will fit for $\vec{\omega}$, so we don't have to know it exactly before, but it can be estimated well and thus provides good starting points for the fit.
@@
 The vector $\vec{\omega}$ accounts for the rotation of the reference frame.
-If we say that the orbit of the balls lies in the same plane as the orbital plane of the earth, $\vec{\omega}$ will point in $z$ - direction with $x$ and $y$ components small.
+If we say that the orbit of the balls lies in the same plane as the orbital plane of the Earth, $\vec{\omega}$ will point in $z$ - direction with $x$ and $y$ components small.
 Thus $\omega_z$ is associated with the period $P_\odot$ of one year through $2\pi/P_\odot$.

### 2017-10-30 manuscript_gravitationalconstant.tex
corrections

--- 2017-10-24 manuscript_gravitationalconstant.tex
@@
 significant change from its current value.  The practical hurdle is
-measuring $G$ three or four orders of magnitude than presently known,
+measuring $G$ three or four orders of magnitude more precisely than presently known,
 so as to find the unknown digits xxxx.  We study a possible scenario
@@
 watt balance, precisely compares electrical and mechanical power, thus
-enabled mass to be standardized in terms of $h$.  For an simple
+enabled mass to be standardized in terms of $h$.  For a simple
 introduction to the new SI, we refer the reader to the article on the
-``LEGO watt balance''[2015AmJPh..83..913C]\cite{Chao15}.
+``LEGO watt balance''[2015AmJPh..83..913C].\cite{Chao15}
 
@@
 both gravity and quantum mechanics in a unit system comes from
-Planck\cite{Planck99}.  In the process of working towards the
+Planck.\cite{Planck99}  In the process of working towards the
 radiation law, Planck realized that $c,G,h$ and the Boltzmann constant
@@
 units is straightforward, but we will not discuss it here.  The Planck
-length, time, and temperature in themselves are extreme scales, not
+length, time, and temperature themselves are extreme scales, not
 probed by any known physical process, and presumably the regime of
@@
 microscopically measurable: $\sim20\mu\mathrm{g}$.  This is of the
-same order as the uncertainty in the prototype kilogram itself.  Hence
+same order as the uncertainty in the prototype kilogram itself.\cite{BIPM}  Hence
 the kilogram could be redefined as an integer multiple of the Planck
@@
 The difficulty with Eq.~\eqref{eq:defs} is that all the expressions
-involve $G$.  Given the current uncertainties in $G$,
+involve $G$.  Given the current uncertainties in $G$,\cite{CODATA16}
 Eq.~\eqref{eq:defs} would allow units to be standardized only to four
@@
 kilogram practicable.  In this paper, we study a scenario which may
-make such an improvement possible.  A Planckian second not a prospect
+make such an improvement possible.  A Planckian second is not a prospect
 with anything like present technology, because demands on the time
@@
 	\includegraphics[width=\textwidth]{img/plotGmeas}
-	\caption{The data points represent six of the most recent measurement of the gravitational constant. The green line represents the recommended CODATA value and its uncertainty.}
+	\caption{Six of the most recent measurements of the gravitational constant $G$ with their uncertainties are plotted.
+The large disagreement is recognised immediately.
+The green lines represents the current recommended CODATA value and its uncertainty.}
 	\label{fig:Gmeasurements}
@@
 In Fig.~\ref{fig:Gmeasurements} we have plotted some of the most recent measurements of the gravitational constant.
-Three of them have been carried out using a torsion balance (BIPM-14\cite{Quinn14}, UCI-14\cite{Newman14}, HUST-09\cite{Luo09}), UZur-06\cite{Schlamminger06} used a beam balance and JILA-10\cite{Parks10} measured the separation of two simple pendulums in a gravitational field.
-They all tried to measure the very weak gravitational force with a mechanical apparatus.
-The sixth measurement (LENS-14\cite{Rosi14}) was performed under another approach, using cold atom interferometry.
+Three of them have been carried out using a torsion balance [(BIPM-14)\cite{Quinn14}, (UCI-14)\cite{Newman14}, (HUST-09)\cite{Luo09}], (UZur-06)\cite{Schlamminger06} used a beam balance and (JILA-10)\cite{Parks10} measured the separation of two simple pendulums in a gravitational field.
+These measurements all tried to quantify the very weak gravitational force with a mechanical apparatus.
+The sixth measurement, (LENS-14)\cite{Rosi14}, was performed under another approach, using cold atom interferometry.
 Its uncertainty is a lot larger than the others, but it could become more competitive in the future.
@@
 \end{equation}
-If one can measure the position of the two masses very accurately and thus knows the orbit, it is possible to deduce the gravitational constant. 
+If one is able to measure the position of the two masses very accurately and thus knows the orbit, it is possible to deduce the gravitational constant. 
 So what we need is a freely falling two-body system.
@@
 In Fig.~\ref{fig:sketch} we show a sketch on how this would look like.
+Treating this system with Newtonian gravity is justified, because corrections from general relativity would be of order $(v^2/c^2)$ and $(GM/rc^2)$, which for our two-body orbit are both very small numbers.\\
+
 For getting an improvement in the precision of the gravitational constant, the positions of the two balls have to be known very accurately.
@@
 \end{equation}
-%
-%To estimate the force on a ball exerted by radiation, we use the Stefan-Boltzmann law.
-The radiation pressure $p_r$ can be written as a third of the energy density of the electromagnetic radiation and with fundamental thermodynamics one can relate the radiation pressure to the temperature $T$
-%
-%\begin{equation}
-%\label{Stefan-Boltzmann}
-%p_r = \frac{1}{3} u = \frac{1}{3} a T^4
-%\end{equation}
-%where the constant $a$ follows from Planck's radiation law and is
-%\begin{equation}
-%\label{eq:a}
-%a = \frac{8 \pi^5 {k_\mathrm{B}}^4}{15 c^3 h^3}.
-%\end{equation}
-%We have now a direct relation between radiation pressure and the temperature in the cavity.
-Then we can estimate the force exerted on a ball of radius $r$ by just multiplying the pressure with the area
-%\begin{equation}
-%F = \frac{1}{3} \pi r^2 a T^4.
-%\end{equation}
-%
 As we can see, this force is highly temperature dependent.
@@
 If a laser with a power of 1 mW is used and not more than five measurements every second are performed, the force on the balls is in the same order as the influence of thermal radiation and thus negligible too.\\
-%
-%In general, one has to pay attention as soon as one undertakes a measurement on a physical system, because every measurement can disturb the system.
-In this case we have a laser that measures the position of two masses which are in an orbit but the photons from the laser exerts an additional force on the masses.
-To give a rough estimation of this influence, we can compare the radiation pressure of the laser with the one of thermal radiation in the cavity, which we estimated before.
-In terms of the power $P$ of the laser and the area of the balls $A$, the radiation pressure is
-%\begin{equation}
-%\label{eq:radpress}
-%p_r = \frac{P}{c\,A}.
-%\end{equation}
-%On behalf of minimizing the impact of the position measurement, a laser with small power should be used.
-If we assume a laser with a power of 1 mW, the radiation pressure is in the order of $10^{-10} \, \mathrm{N} \, \mathrm{m}^{-2}$.
-This is a factor of $10^4$ more than radiation pressure of thermal radiation in the cavity, but the laser doesn't have to shoot photons on the balls constantly.
-Only for the actual measurement a short pulse has to be sent.
-If this pulse has a duration of less than roughly $0.1$ ms, its disturbing effect on the orbit is in the same range as the effect of thermal radiation and is thus negligible too.\\
-%
+
 \textbf{Coulomb force:}
@@
 For simplicity we will abbreviate the product of $GM$ with $k$.
-Since out two-body system is in a rotating frame we have to add the term developed before for the Coriolis acceleration as well as a correction term proportional to the distance accounting for centrifugal and tidal forces.
+Since our two-body system is in a rotating frame, we have to add the term developed before for the Coriolis acceleration as well as a correction term proportional to the distance accounting for centrifugal and tidal forces.
 This last term can be written with a
@@
 For the fit, we suggest to use a Markov Chain Monte-Carlo (MCMC) method because it does good work even if the parameter space is large.
-We will not describe in detail how the MCMC is working, rather refer to an online tutorial from ESO PyCoffee\cite{esopycoffee} or an introduction paper from van Ravenzwaaij et al.\cite{vanRavenzwaaij16} \\
-
 A Markov chain Monte-Carlo method is a Bayesian approach to data analysis.
 It uses the information provided by observed data about a set of parameters, to update a prior state of beliefs about the set of parameters to become a posterior state of beliefs about a set of parameters.
+We will not describe in detail how the MCMC is working, rather refer to an online tutorial from ESO PyCoffee\cite{esopycoffee} or an introduction paper from van Ravenzwaaij et al.\cite{vanRavenzwaaij16}
+
 First we have to specify the prior probability distribution, so to say what values for the 16 parameters in the equation of motion actually make sense.
-Then, for all 16 parameters a uniform distribution within these ranges and zero probability everywhere else is assumed as the prior probability distribution.
-\\
+Then, for all 16 parameters, a uniform distribution within these ranges and zero probability everywhere else is assumed as the prior probability distribution.
+We briefly explain in what range the values of the parameters are estimated and display it in Table~\ref{tab:parameters}.
+For the parameter $k$, which is the product of the gravitational constant $G$ and the total mass $M$, if we look at the current measured values for the gravitational constant in Fig.~\ref{fig:Gmeasurements}, it is reasonable to constrain its numerical value in SI units to values between $6.671 \cdot 10^{-11}$ and $6.676 \cdot 10^{-11}$.
+The masses of the two balls will not contribute to a larger uncertainty in $k$, we choose them to be 6 kg.
 
-We briefly explain in what range the values of the parameters are estimated and display it in table~\ref{tab:parameters}.
-For the parameter $k$, which is the product of the gravitational constant $G$ and the total mass $M$ we look at the current measured values for the gravitational constant in Fig.~\ref{fig:Gmeasurements}, it is reasonable to constrain its numerical value in SI units to values between $6.671 \cdot 10^{-11}$ and $6.676 \cdot 10^{-11}$.
-The masses of the two balls will not contribute to a larger uncertainty in $k$, we choose them to be 6 kg.\\
 The vector $\vec{\omega}$ accounts for the rotation of the reference frame.
@@
 Because the rotation axis are conceivably not exactly aligned, we add some uncertainty.
-As mentioned before, the $x$ and $y$ components are small, so to say roughly in the range of the uncertainty in $w_z$.\\
+As mentioned before, the $x$ and $y$ components are small, so to say roughly in the range of the uncertainty in $w_z$.
 The main contribution to the tidal term goes with $\omega^2$ and lies in the orbital plane.
 We are free to choose the $x$ and $y$ axis, so we choose it such that it is in $x$-direction.
-The other five components then should be smaller, but we give some extra range to account for possible other perturbations.\\
-% 
-%To estimate the six components of the matrix $C$, we first state again that the barycentre of the two balls is in free fall.
-So at this point all forces cancel out.
-If we imagine the ball on its orbit, the tidal force is stronger when its nearer to the earth-sun barycentre and the centrifugal force is stronger when it is in the opposite position.
-So over an orbit, the effect on the balls stays constant.
-Also other perturbations are assumed to be constant, at least during some orbits.
-%The main component of this term should be perpendicular to the rotation axis, for which we have chosen the $z$ - axis.
-Since we are free to set the $x$ and $y$ axis in the orbital plane, we can choose it such that the main contribution lies in the $x$ - axis.
-Its magnitude goes as $\omega^2$, so the $C_{xx}$ component should be around $4 \cdot 10^{-14}$.
-Because we assumed that the main effect is in the $x$ - direction, all the other components are smaller, we constrain them to somewhere between $\pm 10^{-14}$.
-Since the $C$ matrix also absorbs other perturbations, we give some more uncertainty here.
-\\
-%
+The other five components then should be smaller, but we give some extra range to account for possible other perturbations.
 The initial values for the positions can be guessed very accurately, since they are directly measured precisely.
-The initial velocity can be calculated easily and matched to the initial positions, therefore also yielding narrow parameter ranges.\\
-
-In the next step, we set the parameters to a fixed ``true" value within the range estimated.
-We have to keep in mind that $k$, $x_0$ and $v_{y_0}$ are linked together and there must not be contradictions in the true values.
-The chosen values are displayed in the right column in table~\ref{tab:parameters}.\\
+The initial velocity can be calculated easily and matched to the initial positions, therefore also yielding narrow parameter ranges.
 
@@
 
+In the next step, we set the parameters to a fixed ``true" value within the range estimated.
+We have to keep in mind that $k$, $x_0$ and $v_{y_0}$ are linked together and there must not be contradictions in the true values.
+The chosen values are displayed in the right column in Table~\ref{tab:parameters}.
 To simulate data we would obtain from the position measurements, we integrate the equations of motion.
@@
 This uncertainty stays for a systematic error in the laser interferometry measurement and also random statistic noise.
-Its value is just an estimation, it would depend highly on the measurement system that has been used.\\
+Its value is just an estimation, it would depend highly on the measurement system that has been used.
 
@@
 Along the diagonal, the marginalized distribution for each parameter independently is shown.
-In Fig.~\ref{fig:plotCorner4} an excerpt of the full corner plot is shown. \\
-%
-%Here we only depict the parameters $x_0$, $v_{y_0}$, $\omega_z$, $C_{xx}$ and $k$.
-These are the more important ones, because for example the main contribution to $\vec{\omega}$ comes from its $z$-component.\\
-%
+In Fig.~\ref{fig:plotCorner4} an excerpt of the full corner plot is shown.
 
@@
 \end{equation}
-This corresponds to a relative uncertainty of $1.5 \cdot 10^{-7}$ or 15 parts in a hundred million.\\
-
-%
-%we take the median and the percentiles corresponding to one sigma from the distribution of the parameter $k$. For this example we get:
-%\begin{equation}\label{eq:kfit}
-%k = \left( 8.0088006 \, \substack{+0.0000005 \\ -0.0000008}\, \right) \cdot 10^{-10}
-%\end{equation}
-%Now we divide $k$ by the total mass of the two balls.
-Note, that we assume, that the uncertainty on the mass of the balls does not contribute to a larger uncertainty on $G$, because their mass should be determinable to a relative uncertainty of about $10^{-8}$, whereas the one of $k$ is roughly $10^{-7}$.
-We change the way to write the uncertainty from the 0.16 and 0.84 percentiles to the usual standard deviation, while adding some margin.
-With units put back in, we arrive at the following value for the gravitational constant $G$:
-%\begin{equation}\label{Gfit}
-%G = \left(6.674005 \pm 0.000001 \right) \cdot 10^{-11}  \frac{\mathrm{m}^3}{\mathrm{kg \, s}^2}
-%\end{equation}
-%This corresponds to a relative uncertainty of $1.5 \cdot 10^{-7}$ or 15 parts in a hundred million.\\
-%
+This corresponds to a relative uncertainty of $1.5 \cdot 10^{-7}$ or 15 parts in a hundred million.
 
@@
 Based on our estimations, it should be possible to measure the gravitational constant to about $10^{-7}$ relative uncertainty.
-This is a about a factor of 300 better than today's recommended CODATA value.\\
+This is a about a factor of 300 better than today's recommended CODATA value.
+
 If we are a bit optimistic, a further increase in precision is not out of reach, so that about the same relative uncertainty as for Planck's constant $h$ ($1.2 \cdot 10^{-8}$)\cite{CODATA16} could be achieved.
@@
 %to create an appendix.
-
-\begin{acknowledgments}
-Need acknowledgments?
-\end{acknowledgments}
 
@@
 Sitzungsberichte der K\"{o}niglich Preussischen Akademie der Wissenschaften zu Berlin, 479--480 (1899).
+
+\bibitem{BIPM} Bureau International des Poids et Mesures, Calibration and measurement services: Mass, \url{<https://www.bipm.org/utils/common/pdf/cms_m.pdf>}, (2015).
+
+\bibitem{CODATA16} P. J. Mohr, D. B. Newell and B. N. Taylor, ``CODATA recommended values of the fundamental physical constants: 2014*, \textit{Reviews of Modern Physics}, 88(3):035009 (2016).
 
@@
 
+\bibitem{Loughridge13} R. Loughridge and D. Y. Abramovitch, ``A tutorial on laser interferometry for precision measurements,'' 
+American Control Conference, 3686--3703 (2013).
+
 \bibitem{esopycoffee} Fast and easy-to-implement Markov Chain Monte Carlo with the emcee package, ESO PyCoffee (2014),
@@
 
-\bibitem{Loughridge13} R. Loughridge and D. Y. Abramovitch, ``A tutorial on laser interferometry for precision measurements,'' 
-American Control Conference, 3686--3703 (2013).
-
 \bibitem{corner} D. Foreman-Mackey, ``corner.py: Scatterplot matrices in Python,'' 
 The Journal of Open Source Software (10), (2016).
-
-\bibitem{CODATA16} P. J. Mohr, D. B. Newell and B. N. Taylor, ``CODATA recommended values of the fundamental physical constants: 2014*, \textit{Reviews of Modern Physics}, 88(3):035009 (2016).
 

### 2017-10-30 manuscript_gravitationalconstant.tex

--- 2017-10-27 manuscript_gravitationalconstant.tex
@@
 ``LEGO watt balance''.\cite{Chao15}
-
 The proposed redefinition of the kilogram is as an explicit value for
@@
 constant, since $\sqrt{hc/G}$ has dimensions of mass.
-
 Historically, there have been several proposed unit systems that
@@
 \section{A new approach to measure $G$}
-
 In Fig.~\ref{fig:Gmeasurements} we plot the best-known recent
@@
 respective gravitational attraction, they will orbit around the common
-common center of mass, with the relative vector tracing an ellipse
+center of mass, with the relative vector tracing an ellipse
 described by Kepler's laws. The third law, relates the
@@
 $10^{-8}$N.  In Fig.~\ref{fig:sketch} we show a sketch on how this
-would look like.  To follow the mutual orbit of the two balls, best
+would look like.
+Treating this system with Newtonian gravity is justified, because corrections from general relativity would be of order $(v^2/c^2)$ and $(GM/rc^2)$, which for our two-body orbit are both very small numbers.
+To follow the mutual orbit of the two balls, best
 would be a laser interferometry system, which can yield precisions
@@
 But first we have to find the orbital equation of motion for the two balls.\\
-
+git 
 \subsection{Orbital equation of motion}
@@
 For the fit, we suggest to use a Markov Chain Monte-Carlo (MCMC) method because it does good work even if the parameter space is large.
-We will not describe in detail how the MCMC is working, rather refer to an online tutorial from ESO PyCoffee\cite{esopycoffee} or an introduction paper from van Ravenzwaaij et al.\cite{vanRavenzwaaij16} \\
-
 A Markov chain Monte-Carlo method is a Bayesian approach to data analysis.
 It uses the information provided by observed data about a set of parameters, to update a prior state of beliefs about the set of parameters to become a posterior state of beliefs about a set of parameters.
-First we have to specify the prior probability distribution, so to say what values for the 16 parameters in the equation of motion actually make sense.
-Then, for all 16 parameters a uniform distribution within these ranges and zero probability everywhere else is assumed as the prior probability distribution.
-\\
+We will not describe in detail how the MCMC is working, rather refer to an online tutorial from ESO PyCoffee\cite{esopycoffee} or an introduction paper from van Ravenzwaaij et al.\cite{vanRavenzwaaij16}
 
@@
 For the parameter $k$, which is the product of the gravitational constant $G$ and the total mass $M$ we look at the current measured values for the gravitational constant in Fig.~\ref{fig:Gmeasurements}, it is reasonable to constrain its numerical value in SI units to values between $6.671 \cdot 10^{-11}$ and $6.676 \cdot 10^{-11}$.
-The masses of the two balls will not contribute to a larger uncertainty in $k$, we choose them to be 6 kg.\\
+The masses of the two balls will not contribute to a larger uncertainty in $k$, we choose them to be 6 kg.
 The vector $\vec{\omega}$ accounts for the rotation of the reference frame.
@@
 Because the rotation axis are conceivably not exactly aligned, we add some uncertainty.
-As mentioned before, the $x$ and $y$ components are small, so to say roughly in the range of the uncertainty in $w_z$.\\
+As mentioned before, the $x$ and $y$ components are small, so to say roughly in the range of the uncertainty in $w_z$.
+
 The main contribution to the tidal term goes with $\omega^2$ and lies in the orbital plane.
 We are free to choose the $x$ and $y$ axis, so we choose it such that it is in $x$-direction.
-The other five components then should be smaller, but we give some extra range to account for possible other perturbations.\\
-% 
-%To estimate the six components of the matrix $C$, we first state again that the barycentre of the two balls is in free fall.
-So at this point all forces cancel out.
-If we imagine the ball on its orbit, the tidal force is stronger when its nearer to the earth-sun barycentre and the centrifugal force is stronger when it is in the opposite position.
-So over an orbit, the effect on the balls stays constant.
-Also other perturbations are assumed to be constant, at least during some orbits.
-%The main component of this term should be perpendicular to the rotation axis, for which we have chosen the $z$ - axis.
-Since we are free to set the $x$ and $y$ axis in the orbital plane, we can choose it such that the main contribution lies in the $x$ - axis.
-Its magnitude goes as $\omega^2$, so the $C_{xx}$ component should be around $4 \cdot 10^{-14}$.
-Because we assumed that the main effect is in the $x$ - direction, all the other components are smaller, we constrain them to somewhere between $\pm 10^{-14}$.
-Since the $C$ matrix also absorbs other perturbations, we give some more uncertainty here.
-\\
-%
+The other five components then should be smaller, but we give some extra range to account for possible other perturbations.
 The initial values for the positions can be guessed very accurately, since they are directly measured precisely.
-The initial velocity can be calculated easily and matched to the initial positions, therefore also yielding narrow parameter ranges.\\
-
-In the next step, we set the parameters to a fixed ``true" value within the range estimated.
-We have to keep in mind that $k$, $x_0$ and $v_{y_0}$ are linked together and there must not be contradictions in the true values.
-The chosen values are displayed in the right column in table~\ref{tab:parameters}.\\
+The initial velocity can be calculated easily and matched to the initial positions, therefore also yielding narrow parameter ranges.
 

### 2017-10-31 manuscript_gravitationalconstant.tex
corrections

@@
 ``LEGO watt balance''.\cite{Chao15}
-The proposed redefinition of the kilogram is as an explicit value for
+The proposed redefinition of the kilogram is an explicit value for
 $h$ and $c$, but we can think of it as

### 2017-10-31 manuscript_gravitationalconstant.tex
small edits

--- 2017-10-30 manuscript_gravitationalconstant.tex
@@
 (admittedly, not the cheapest) option is to place the system on a
-trojan orbit to minimize external gravitational perturbations, and
+Trojan orbit to minimize external gravitational perturbations, and
 enclose it in a cavity chilled to liquid-helium temperatures, to
@@
 Furthermore, there is thermal radiation inside the cavity, that could disturb the orbit.
-Using the Stefan-Boltzmann law, we can relate radiation pressure to the temperature inside the cavity. If we then specify to balls of radius $r$, we can express the force on the balls as 
+Using the Stefan-Boltzmann law, we can relate radiation pressure to the temperature inside the cavity. If we then specify to balls of diameter $d$, we can express the force on the balls as 
 \begin{equation}
-F = \frac{8 \pi^6 r^2 {k_\mathrm{B}}^4 T^4}{45 c^3 h^3}.
+F = \frac{2 \pi^6 d^2 {k_\mathrm{B}}^4 T^4}{45 c^3 h^3}.
 \end{equation}
@@
 
-In this section we are going to show how the gravitational constant can be recovered from position data of the two balls that the laser interferometry measurement would provide.
-But first we have to find the orbital equation of motion for the two balls.\\
-git 
+In this section we will show how the gravitational constant can be
+recovered from the position data of the two balls that the laser
+interferometry measurement would provide.  But first we have to find
+the orbital equation of motion for the two balls.
 \subsection{Orbital equation of motion}
@@
 \end{equation}
-Here $M$ denotes the sum of the masses $m_1$ and $m_2$, $G$ is the gravitational constant and $r$ is the relative distance between the two bodies.
-For simplicity we will abbreviate the product of $GM$ with $k$.
-Since our two-body system is in a rotating frame, we have to add the term developed before for the Coriolis acceleration as well as a correction term proportional to the distance accounting for centrifugal and tidal forces.
-This last term can be written with a
-symmetric $3 \times 3$ matrix $C$ as follows  
+Here $M$ denotes the sum of the masses $m_1$ and $m_2$, $G$ is the
+gravitational constant and $r$ is the relative distance between the
+two bodies. For simplicity we will abbreviate the product of $GM$ with
+$k$.  Since our two-body system is in a rotating frame, we have to add
+the term developed before for the Coriolis acceleration, as well as a
+correction term for centrifugal and tidal forces. The latter can be
+written with a constant symmetric $3 \times 3$ matrix $C$ as follows
 \begin{equation}
 \label{eq:tidal}
-\ddot{\vec{r}}_{\mathrm{C}} = C \cdot \vec{r}.
+\ddot{\vec{r}}_{\mathrm{C}} = C \cdot \vec{r},
 \end{equation}
@@
 \end{equation}
-It can be thought of as a first order expansion and therefore also include other possible minor perturbations.
-The reference frame is chosen such that the barycenter of the two-body system is force-free.
-So the full equation of motion for the two balls looks as follows:
+The reference frame is chosen such that the barycenter of the two-body
+system is freely falling and has no tidal or fictitious forces acting
+on it.  The balls, however, do experience such forces, because they
+are not at the centre of mass.  The $C$ term can be thought of as a
+first-order expansion of these forces.  So the full equation of motion
+for the two balls looks as follows:
 \begin{equation}
@@
 Since all are second order differential equations, this leaves us with six initial conditions.
-In other words to determine the orbit, we need to give six starting values.\\
+In other words to determine the orbit, we need to give six starting values.
+
 We choose our coordinate system such that the orbital plane of the two-body system is in the $x-y$ plane.
@@
 We will fit for $\vec{\omega}$, so we don't have to know it exactly before, but it can be estimated well and thus provides good starting points for the fit.
-The same is valid for the six components of the matrix $C$.\\
+The same is valid for the six components of the matrix $C$.
 
-Counting all unknown parameters in the equation of motion, we get 16.
-They correspond to 6 initial conditions, 6 components of the matrix $C$, 3 components of the vector $\vec{\omega}$ and the object of main interest, $k$,  which contains the gravitational constant ($k = GM$).
-Fitting for so many parameters is not an easy task, but it should be possible because the parameters are not completely unknown.\\
+Counting all unknown parameters in the equation of motion, we get
+16. They correspond to 6 initial conditions, 6 components of the
+matrix $C$, 3 components of the vector $\vec{\omega}$ and the object
+of main interest, $k$, which contains the gravitational constant ($k =
+GM$). Fitting for so many parameters is not an easy task, but it
+should be possible because the parameters are approximately known in
+advance.
 
@@
 
-Our problem has 16 unknown parameters, but the only one we are really interested in is $k$, which contains the gravitational constant.
-For the fit, we suggest to use a Markov Chain Monte-Carlo (MCMC) method because it does good work even if the parameter space is large.
-A Markov chain Monte-Carlo method is a Bayesian approach to data analysis.
-It uses the information provided by observed data about a set of parameters, to update a prior state of beliefs about the set of parameters to become a posterior state of beliefs about a set of parameters.
-We will not describe in detail how the MCMC is working, rather refer to an online tutorial from ESO PyCoffee\cite{esopycoffee} or an introduction paper from van Ravenzwaaij et al.\cite{vanRavenzwaaij16}
+To fit for $k$ and the 15 accompanying nuisance parameters, we suggest
+using a Markov Chain Monte-Carlo (MCMC) method, which are widely used
+for similarly large parameter spaces.  MCMC is a Bayesian approach,
+which uses the information provided by observed data about a set of
+parameters, to update a prior state of knowledge/ignorance about the
+set of parameters to become a posterior state of knowledge/ignorance
+about a set of parameters. We will not describe in detail how MCMC
+works, but refer the reader to an online tutorial from ESO
+PyCoffee\cite{esopycoffee} or an introduction paper from van
+Ravenzwaaij et al.\cite{vanRavenzwaaij16}
 
-We briefly explain in what range the values of the parameters are estimated and display it in table~\ref{tab:parameters}.
-For the parameter $k$, which is the product of the gravitational constant $G$ and the total mass $M$ we look at the current measured values for the gravitational constant in Fig.~\ref{fig:Gmeasurements}, it is reasonable to constrain its numerical value in SI units to values between $6.671 \cdot 10^{-11}$ and $6.676 \cdot 10^{-11}$.
-The masses of the two balls will not contribute to a larger uncertainty in $k$, we choose them to be 6 kg.
-The vector $\vec{\omega}$ accounts for the rotation of the reference frame.
-If we say that the orbit of the balls lies in the same plane as the orbital plane of the Earth, $\vec{\omega}$ will point in $z$ - direction with $x$ and $y$ components small.
-Thus $\omega_z$ is associated with the period $P_\odot$ of one year through $2\pi/P_\odot$.
-Because the rotation axis are conceivably not exactly aligned, we add some uncertainty.
-As mentioned before, the $x$ and $y$ components are small, so to say roughly in the range of the uncertainty in $w_z$.
+We now briefly explain in what range the values of the parameters are
+estimated.  Numbers are given in Table~\ref{tab:parameters}.  For the
+parameter $k$, which is the product of the gravitational constant $G$
+and the total mass $M$ we look at the current measured values for the
+gravitational constant in Fig.~\ref{fig:Gmeasurements}, it is
+reasonable to constrain its numerical value in SI units to values
+between $6.671 \cdot 10^{-11}$ and $6.676 \cdot 10^{-11}$. The masses
+of the two balls will not contribute to a larger uncertainty in $k$,
+we choose them to be 6~kg.  The vector $\vec{\omega}$ accounts for the
+rotation of the reference frame. If we say that the orbit of the balls
+lies in the same plane as the orbital plane of the Earth,
+$\vec{\omega}$ will point in $z$-direction with $x$ and $y$
+components small. Thus $\omega_z$ is associated with the period
+$P_\odot$ of one year through $2\pi/P_\odot$. Because the rotation
+axis are conceivably not exactly aligned, we add some uncertainty. As
+mentioned before, the $x$ and $y$ components are small, that is to
+say, near zero in roughly in the range of the uncertainty in
+$\omega_z$.
 
@@
 
-In the next step, we set the parameters to a fixed ``true" value within the range estimated.
-We have to keep in mind that $k$, $x_0$ and $v_{y_0}$ are linked together and there must not be contradictions in the true values.
-The chosen values are displayed in the right column in Table~\ref{tab:parameters}.
-To simulate data we would obtain from the position measurements, we integrate the equations of motion.
-The time for one orbit without perturbations can be estimated using Kepler's third law (\ref{eq:kepler3}).
-For the value of $k$ assumed above and a semi-major axis of $0.15 \, \mathrm{m}$, this results in an orbital period of roughly $12900 \, \mathrm{seconds}$ or $3.5 \, \mathrm{hours}$.
-Here we integrate two orbits in $100000$ steps, that would correspond to about $4$ measurements per second, which should be feasible.
-To the generated data, we add normal distributed noise with a standard deviation of $10 \, \mathrm{nm}$.
-This uncertainty stays for a systematic error in the laser interferometry measurement and also random statistic noise.
-Its value is just an estimation, it would depend highly on the measurement system that has been used.
+In the next step, we set the parameters to a fixed ``true" value
+within the range estimated. We have to keep in mind that $k$, $x_0$
+and $v_{y_0}$ are linked together and there must not be contradictions
+in the true values. The chosen values are displayed in the right
+column in Table~\ref{tab:parameters}.  To simulate data we would
+obtain from the position measurements, we integrate the equations of
+motion. The time for one orbit without perturbations can be estimated
+using Kepler's third law (\ref{eq:kepler3}). For the value of $k$
+assumed above and a semi-major axis of $0.15 \, \mathrm{m}$, this
+results in an orbital period of roughly $12900 \, \mathrm{seconds}$ or
+$3.5 \, \mathrm{hours}$. Here we integrate two orbits in $100000$
+steps, that would correspond to about $4$ measurements per second,
+which should be feasible. To the generated data, we add Gaussian noise
+with a standard deviation of $10 \, \mathrm{nm}$. This uncertainty
+stays for a systematic error in the laser interferometry measurement
+and also random statistic noise. The value we use is just an estimate,
+it would depend strongly on the measurement system that has been used.
 
@@
 
-A useful way to look at the samples of the posterior returned by the MCMC is doing a corner plot using a Python module named \textit{corner}\cite{corner}.
-The corner plot shows all the one and two dimensional projections of the posterior probability distributions and demonstrates quickly the covariances between parameters.
+A useful way to look at the samples of the posterior returned by the MCMC is to make a corner plot using a Python module named \textit{corner}.\cite{corner} The corner plot shows all the one- and two-dimensional projections of the posterior probability distributions and demonstrates quickly the covariances between parameters.
 Along the diagonal, the marginalized distribution for each parameter independently is shown.
@@
 \section{Conclusion}
-We have proposed a new way to measure the gravitational constant $G$ and estimated on what order of magnitude different disturbing effects occur and if one has to correct for them.
-We then simulated measurement data and showed how to extract the gravitational constant.
-Based on our estimations, it should be possible to measure the gravitational constant to about $10^{-7}$ relative uncertainty.
-This is a about a factor of 300 better than today's recommended CODATA value.
-
-If we are a bit optimistic, a further increase in precision is not out of reach, so that about the same relative uncertainty as for Planck's constant $h$ ($1.2 \cdot 10^{-8}$)\cite{CODATA16} could be achieved.
-This then would allow to redefine the kilogram as an integer multiple of the Planck mass.\\
-
-\appendix*   % Omit the * if there's more than one appendix.
-
-\section{Uninteresting stuff}
-
-%Appendices are for material that is needed for completeness but
-%not sufficiently interesting to include in the main body of the paper.  Most
-%articles don't need any appendices, but feel free to use them when
-%appropriate.  This sample article needs an appendix only to illustrate how 
-%to create an appendix.
+We have outlined an orbit experiment to measure the gravitational
+constant $G$, and estimated the level of various disturbing effects
+and how to correct for them.  Simulating the measurement process and
+extraction of the gravitational constant indicates that $G$ could be
+estimated to about $10^{-7}$ relative uncertainty.  This is a about a
+factor of 300 better than today's recommended CODATA value.  If we are
+a bit optimistic, a further increase in precision is not out of reach,
+so that about the same relative uncertainty as for Planck's constant
+$h$ ($1.2 \cdot 10^{-8}$)\cite{CODATA16} could be achieved. This then
+would allow a future redefination of the kilogram as an integer
+multiple of the Planck mass.
 

### 2017-10-31 manuscript_gravitationalconstant.tex
again corrections

--- 2017-10-31 manuscript_gravitationalconstant.tex
@@
 The large disagreement is recognised immediately.
-The green lines represents the current recommended CODATA value and its uncertainty.}
+The green lines represent the current recommended CODATA value and its uncertainty.\cite{CODATA16}}
 	\label{fig:Gmeasurements}
@@
 factor.  If one can measure the position of the two masses very
-accurately and thus know the orbit, it is possible to deduce the
+accurately and thus the orbit is known, it is possible to deduce the
 gravitational constant.  So what we need is a freely-falling two-body
@@
 gravitational force acting between the two bodies is of order
-$10^{-8}$N.  In Fig.~\ref{fig:sketch} we show a sketch on how this
+$10^{-8}$~N.  In Fig.~\ref{fig:sketch} we show a sketch on how this
 would look like.
-Treating this system with Newtonian gravity is justified, because corrections from general relativity would be of order $(v^2/c^2)$ and $(GM/rc^2)$, which for our two-body orbit are both very small numbers.
+Treating this system with Newtonian gravity is justified, because corrections from general relativity would be of order $(v^2/c^2)$ and $(GM/rc^2)$, which for our two-body system are both very small numbers.
 To follow the mutual orbit of the two balls, best
@@
 Such a low temperature results in a force on the balls in the order of $10^{-16}$ N.
-Compared to the gravitational force, this is orders of magnitude less and thus we don't have to worry about effects of radiation pressure.\\
+Compared to the gravitational force, this is orders of magnitude less and thus we don't have to worry about effects of radiation pressure.
 
@@
 The photons of the laser that measures the position of the two balls exert an additional force.
-If a laser with a power of 1 mW is used and not more than five measurements every second are performed, the force on the balls is in the same order as the influence of thermal radiation and thus negligible too.\\
+If a laser with a power of 1 mW is used and not more than five measurements every second are performed, the force on the balls is in the same order as the influence of thermal radiation and thus negligible too.
 
@@
 \end{equation}
-In this formula $\vec{\omega}$ is the angular velocity vector of the rotating frame and $\dot{\vec{r}}$ is the velocity vector in the two-body system.
+In this formula, $\vec{\omega}$ is the angular velocity vector of the rotating frame and $\dot{\vec{r}}$ is the velocity vector in the two-body system.
 
@@
 Fortunately, for this we don't need to correct if the whole system, consisting of the spacecraft and the two-body system, is moving through space together.
-Although, the spacecraft should be able to correct its position around the two balls to avoid a collision.\\
+Although, the spacecraft should be able to correct its position around the two balls to avoid a collision.
 
@@
 In this section we are going to show how the gravitational constant can be recovered from position data of the two balls that the laser interferometry measurement would provide.
-But first we have to find the orbital equation of motion for the two balls.\\
-git 
+But first we have to find the orbital equation of motion for the two balls.
+
 \subsection{Orbital equation of motion}
@@
 \label{eq:tidal}
-\ddot{\vec{r}}_{\mathrm{C}} = C \cdot \vec{r}.
+\ddot{\vec{r}}_{\mathrm{C}} = C \cdot \vec{r}
 \end{equation}
@@
 \end{equation}
-These are actually three coupled equations of motion, one for each coordinate axis.
-Since all are second order differential equations, this leaves us with six initial conditions.
-In other words to determine the orbit, we need to give six starting values.\\
+These are actually three coupled equations of motion, one for each spatial coordinate.
+Since all are second order differential equations, we need to give six initial conditions to determine the orbit.\\
 We choose our coordinate system such that the orbital plane of the two-body system is in the $x-y$ plane.
@@
 We will fit for $\vec{\omega}$, so we don't have to know it exactly before, but it can be estimated well and thus provides good starting points for the fit.
-The same is valid for the six components of the matrix $C$.\\
+The same is valid for the six components of the matrix $C$.
 
@@
 Our problem has 16 unknown parameters, but the only one we are really interested in is $k$, which contains the gravitational constant.
-For the fit, we suggest to use a Markov Chain Monte-Carlo (MCMC) method because it does good work even if the parameter space is large.
+For the fit, we suggest to use a Markov Chain Monte-Carlo (MCMC) method, because it does good work even if the parameter space is large.
 A Markov chain Monte-Carlo method is a Bayesian approach to data analysis.
@@
 We briefly explain in what range the values of the parameters are estimated and display it in table~\ref{tab:parameters}.
-For the parameter $k$, which is the product of the gravitational constant $G$ and the total mass $M$ we look at the current measured values for the gravitational constant in Fig.~\ref{fig:Gmeasurements}, it is reasonable to constrain its numerical value in SI units to values between $6.671 \cdot 10^{-11}$ and $6.676 \cdot 10^{-11}$.
+For the parameter $k$, which is the product of the gravitational constant $G$ and the total mass $M$, if we look at the current measured values for the gravitational constant in Fig.~\ref{fig:Gmeasurements}, it is reasonable to constrain its numerical value in SI units to values between $6.671 \cdot 10^{-11}$ and $6.676 \cdot 10^{-11}$.
 The masses of the two balls will not contribute to a larger uncertainty in $k$, we choose them to be 6 kg.
@@
 Because the rotation axis are conceivably not exactly aligned, we add some uncertainty.
-As mentioned before, the $x$ and $y$ components are small, so to say roughly in the range of the uncertainty in $w_z$.
+As mentioned before, the $x$ and $y$ components are small, so to say roughly in the range of the uncertainty in $\omega_z$.
 
 The main contribution to the tidal term goes with $\omega^2$ and lies in the orbital plane.
-We are free to choose the $x$ and $y$ axis, so we choose it such that it is in $x$-direction.
+We are free to choose the $x$ and $y$ axis, so we choose it such that the $\omega^2$-contribution is in $x$-direction.
 The other five components then should be smaller, but we give some extra range to account for possible other perturbations.
@@
 The time for one orbit without perturbations can be estimated using Kepler's third law (\ref{eq:kepler3}).
-For the value of $k$ assumed above and a semi-major axis of $0.15 \, \mathrm{m}$, this results in an orbital period of roughly $12900 \, \mathrm{seconds}$ or $3.5 \, \mathrm{hours}$.
+For the value of $k$ assumed above and a semi-major axis of $0.15$~m, this results in an orbital period of roughly $12900$ seconds or $3.5$ hours.
 Here we integrate two orbits in $100000$ steps, that would correspond to about $4$ measurements per second, which should be feasible.
-To the generated data, we add normal distributed noise with a standard deviation of $10 \, \mathrm{nm}$.
+To the generated data, we add normal distributed noise with a standard deviation of $10$~nm.
 This uncertainty stays for a systematic error in the laser interferometry measurement and also random statistic noise.

### 2017-10-31 manuscript_gravitationalconstant.tex

--- 2017-10-31 manuscript_gravitationalconstant.tex
@@
 the orbital equation of motion for the two balls.
+
 \subsection{Orbital equation of motion}
@@
 \end{equation}
-These are actually three coupled equations of motion, one for each coordinate axis.
-Since all are second order differential equations, this leaves us with six initial conditions.
-In other words to determine the orbit, we need to give six starting values.
 
+These are actually three coupled equations of motion, one for each spatial coordinate.
+Since all are second order differential equations, we need to give six initial conditions to determine the orbit.\\
+We choose our coordinate system such that the orbital plane of the two-body system is in the $x-y$ plane.
+$\vec{\omega}$ is a constant vector that points in the direction of the rotation axis of the Earth-Sun reference frame.
+We will fit for $\vec{\omega}$, so we don't have to know it exactly before, but it can be estimated well and thus provides good starting points for the fit.
+The same is valid for the six components of the matrix $C$.
 We choose our coordinate system such that the orbital plane of the two-body system is in the $x-y$ plane.
@@
 The main contribution to the tidal term goes with $\omega^2$ and lies in the orbital plane.
-We are free to choose the $x$ and $y$ axis, so we choose it such that it is in $x$-direction.
+We are free to choose the $x$ and $y$ axis, so we choose it such that the $\omega^2$-contribution is in $x$-direction.
 The other five components then should be smaller, but we give some extra range to account for possible other perturbations.

### 2017-10-31 manuscript_gravitationalconstant.tex
spelling errors corrected
conclusion edited

@@
 using Kepler's third law (\ref{eq:kepler3}). For the value of $k$
-assumed above and a semi-major axis of $0.15 \, \mathrm{m}$, this
-results in an orbital period of roughly $12900 \, \mathrm{seconds}$ or
-$3.5 \, \mathrm{hours}$. Here we integrate two orbits in $100000$
-steps, that would correspond to about $4$ measurements per second,
+assumed above and a semi-major axis of $0.15$~m, this
+results in an orbital period of roughly 12900 seconds or
+3.5 hours. Here we integrate two orbits in 100000
+steps, that would correspond to about 4 measurements per second,
 which should be feasible. To the generated data, we add Gaussian noise
-with a standard deviation of $10 \, \mathrm{nm}$. This uncertainty
-stays for a systematic error in the laser interferometry measurement
-and also random statistic noise. The value we use is just an estimate,
+with a standard deviation of 10~nm. The value we use is just an estimate,
 it would depend strongly on the measurement system that has been used.
@@
 estimated to about $10^{-7}$ relative uncertainty.  This is a about a
-factor of 300 better than today's recommended CODATA value.  If we are
-a bit optimistic, a further increase in precision is not out of reach,
-so that about the same relative uncertainty as for Planck's constant
+factor of 300 better than today's recommended CODATA value.
+A further increase in precision could be obtained by running the experiment longer.
+Measuring for 200 instead of two orbits could increase the precision by a factor of 10.
+Hence, about the same relative uncertainty as for Planck's constant
 $h$ ($1.2 \cdot 10^{-8}$)\cite{CODATA16} could be achieved. This then
-would allow a future redefination of the kilogram as an integer
+would allow a future redefinition of the kilogram as an integer
 multiple of the Planck mass.
+
+We are not supposing the measurement of the gravitational constant 
+using an artificial two-body system at an Earth-Sun Lagrange point to be a stand alone mission. It could just be part of 
+a spacecraft reaching a Lagrange point. But our estimates suggest that this approach to increase the precision of the gravitational constant should be taken seriously.
 

### 2017-10-31 manuscript_gravitationalconstant.tex
Final version for first submission

@@
 The reform of SI units to use quantum standards is an ongoing ``news
-story'' in physics.  At the heart of the reform are two quantum
+story'' in physics.\cite{BIPM16}  At the heart of the reform are two quantum
 phenomena that appear on macroscopic scales: the Josephson effect
@@
 small but microscopically measurable: $\sim20\mu\mathrm{g}$.  This is
-of the same order as the uncertainty in the prototype kilogram itself.
+of the same order as the uncertainty in the prototype kilogram itself.\cite{BIPM}
 Hence the kilogram could be redefined as an integer multiple of the
@@
 measurements of the gravitational constant. Three of them
-(BIPM-14,\cite{Quinn14} UCI-14,\cite{Newman14}, and
+(BIPM-14,\cite{Quinn14} UCI-14,\cite{Newman14} and
 HUST-09\cite{Luo09}) were carried out using a torsion balance, whereas
@@
 In fact, if a cooling system based on liquid helium is installed, temperature can be brought down to about 4 K.
-Such a low temperature results in a force on the balls in the order of $10^{-16}$ N.
+Such a low temperature results in a force on the balls in the order of $10^{-16}$~N.
 Compared to the gravitational force, this is orders of magnitude less and thus we don't have to worry about effects of radiation pressure.
@@
 The photons of the laser that measures the position of the two balls exert an additional force.
-If a laser with a power of 1 mW is used and not more than five measurements every second are performed, the force on the balls is in the same order as the influence of thermal radiation and thus negligible too.
+If a laser with a power of 1~mW is used and not more than five measurements every second are performed, the force on the balls is in the same order as the influence of thermal radiation and thus negligible too.
 
@@
 A possible source of charges are cosmic rays or the solar wind, so the two bodies have to be adequately shielded by the enclosing shell.
-If we want that the Coulomb force between the balls is in the same order as the effect of thermal radiation and thus negligible, the maximal allowed charge on the balls is about $6 \cdot 10^{-14}\,\mathrm{C}$, which corresponds to roughly $4 \cdot 10^5$ elementary charges.
+If we want that the Coulomb force between the balls is in the same order as the effect of thermal radiation and thus negligible, the maximal allowed charge on the balls is about $6 \cdot 10^{-14}$~C, which corresponds to roughly $4 \cdot 10^5$ elementary charges.
 
@@
 mentioned before, the $x$ and $y$ components are small, that is to
-say, near zero in roughly in the range of the uncertainty in
+say, near zero in roughly the range of the uncertainty in
 $\omega_z$.
@@
 in the true values. The chosen values are displayed in the right
-column in Table~\ref{tab:parameters}.  To simulate data we would
+column of Table~\ref{tab:parameters}.  To simulate data we would
 obtain from the position measurements, we integrate the equations of
@@
 We are not supposing the measurement of the gravitational constant 
-using an artificial two-body system at an Earth-Sun Lagrange point to be a stand alone mission. It could just be part of 
+using an artificial two-body system at an Earth-Sun Lagrange point to be a stand alone mission. It could be part of 
 a spacecraft reaching a Lagrange point. But our estimates suggest that this approach to increase the precision of the gravitational constant should be taken seriously.
@@
 \begin{thebibliography}{99}
+\bibitem{BIPM16} International Bureau of Weights and Measures, ``DRAFT 9th edition of the SI Brochure", BIPM, (2016)
 

### 2017-11-29 manuscript_gravitationalconstant.tex
some edits

--- 2017-10-31 manuscript_gravitationalconstant.tex
@@
 (admittedly, not the cheapest) option is to place the system on a
-Trojan orbit to minimize external gravitational perturbations, and
+trojan orbit to minimize external gravitational perturbations, and
 enclose it in a cavity chilled to liquid-helium temperatures, to
@@
 ``LEGO watt balance''.\cite{Chao15}
-The proposed redefinition of the kilogram is an explicit value for
+The proposed redefinition of the kilogram is as an explicit value for
 $h$ and $c$, but we can think of it as
@@
 The large disagreement is recognised immediately.
-The green lines represent the current recommended CODATA value and its uncertainty.\cite{CODATA16}}
+The green lines represents the current recommended CODATA value and its uncertainty.}
 	\label{fig:Gmeasurements}
@@
 factor.  If one can measure the position of the two masses very
-accurately and thus the orbit is known, it is possible to deduce the
+accurately and thus know the orbit, it is possible to deduce the
 gravitational constant.  So what we need is a freely-falling two-body
@@
 gravitational force acting between the two bodies is of order
-$10^{-8}$~N.  In Fig.~\ref{fig:sketch} we show a sketch on how this
+$10^{-8}$N.  In Fig.~\ref{fig:sketch} we show a sketch on how this
 would look like.
-Treating this system with Newtonian gravity is justified, because corrections from general relativity would be of order $(v^2/c^2)$ and $(GM/rc^2)$, which for our two-body system are both very small numbers.
+Treating this system with Newtonian gravity is justified, because corrections from general relativity would be of order $(v^2/c^2)$ and $(GM/rc^2)$, which for our two-body orbit are both very small numbers.
 To follow the mutual orbit of the two balls, best
@@
 Furthermore, there is thermal radiation inside the cavity, that could disturb the orbit.
-Using the Stefan-Boltzmann law, we can relate radiation pressure to the temperature inside the cavity. If we then specify to balls of diameter $d$, we can express the force on the balls as 
+Using the Stefan-Boltzmann law, we can relate radiation pressure to the temperature inside the cavity. If we then specify to balls of radius $r$, we can express the force on the balls as 
 \begin{equation}
-F = \frac{2 \pi^6 d^2 {k_\mathrm{B}}^4 T^4}{45 c^3 h^3}.
+F = \frac{8 \pi^6 r^2 {k_\mathrm{B}}^4 T^4}{45 c^3 h^3}.
 \end{equation}
@@
 Such a low temperature results in a force on the balls in the order of $10^{-16}$ N.
-Compared to the gravitational force, this is orders of magnitude less and thus we don't have to worry about effects of radiation pressure.
+Compared to the gravitational force, this is orders of magnitude less and thus we don't have to worry about effects of radiation pressure.\\
 
@@
 The photons of the laser that measures the position of the two balls exert an additional force.
-If a laser with a power of 1 mW is used and not more than five measurements every second are performed, the force on the balls is in the same order as the influence of thermal radiation and thus negligible too.
+If a laser with a power of 1 mW is used and not more than five measurements every second are performed, the force on the balls is in the same order as the influence of thermal radiation and thus negligible too.\\
 
@@
 \end{equation}
-In this formula, $\vec{\omega}$ is the angular velocity vector of the rotating frame and $\dot{\vec{r}}$ is the velocity vector in the two-body system.
+In this formula $\vec{\omega}$ is the angular velocity vector of the rotating frame and $\dot{\vec{r}}$ is the velocity vector in the two-body system.
 
@@
 Fortunately, for this we don't need to correct if the whole system, consisting of the spacecraft and the two-body system, is moving through space together.
-Although, the spacecraft should be able to correct its position around the two balls to avoid a collision.
+Although, the spacecraft should be able to correct its position around the two balls to avoid a collision.\\
 
@@
 
-In this section we will show how the gravitational constant can be
-recovered from the position data of the two balls that the laser
-interferometry measurement would provide.  But first we have to find
-the orbital equation of motion for the two balls.
-
+In this section we are going to show how the gravitational constant can be recovered from position data of the two balls that the laser interferometry measurement would provide.
+But first we have to find the orbital equation of motion for the two balls.\\
+git 
 \subsection{Orbital equation of motion}
@@
 \end{equation}
-Here $M$ denotes the sum of the masses $m_1$ and $m_2$, $G$ is the
-gravitational constant and $r$ is the relative distance between the
-two bodies. For simplicity we will abbreviate the product of $GM$ with
-$k$.  Since our two-body system is in a rotating frame, we have to add
-the term developed before for the Coriolis acceleration, as well as a
-correction term for centrifugal and tidal forces. The latter can be
-written with a constant symmetric $3 \times 3$ matrix $C$ as follows
+Here $M$ denotes the sum of the masses $m_1$ and $m_2$, $G$ is the gravitational constant and $r$ is the relative distance between the two bodies.
+For simplicity we will abbreviate the product of $GM$ with $k$.
+Since our two-body system is in a rotating frame, we have to add the term developed before for the Coriolis acceleration as well as a correction term proportional to the distance accounting for centrifugal and tidal forces.
+This last term can be written with a
+symmetric $3 \times 3$ matrix $C$ as follows  
 \begin{equation}
 \label{eq:tidal}
-\ddot{\vec{r}}_{\mathrm{C}} = C \cdot \vec{r},
+\ddot{\vec{r}}_{\mathrm{C}} = C \cdot \vec{r}.
 \end{equation}
@@
 \end{equation}
-The reference frame is chosen such that the barycenter of the two-body
-system is freely falling and has no tidal or fictitious forces acting
-on it.  The balls, however, do experience such forces, because they
-are not at the centre of mass.  The $C$ term can be thought of as a
-first-order expansion of these forces.  So the full equation of motion
-for the two balls looks as follows:
+It can be thought of as a first order expansion and therefore also include other possible minor perturbations.
+The reference frame is chosen such that the barycenter of the two-body system is force-free.
+So the full equation of motion for the two balls looks as follows:
 \begin{equation}
@@
 \end{equation}
-
-These are actually three coupled equations of motion, one for each spatial coordinate.
-Since all are second order differential equations, we need to give six initial conditions to determine the orbit.\\
+These are actually three coupled equations of motion, one for each coordinate axis.
+Since all are second order differential equations, this leaves us with six initial conditions.
+In other words to determine the orbit, we need to give six starting values.\\
 We choose our coordinate system such that the orbital plane of the two-body system is in the $x-y$ plane.
@@
 We will fit for $\vec{\omega}$, so we don't have to know it exactly before, but it can be estimated well and thus provides good starting points for the fit.
-The same is valid for the six components of the matrix $C$.
-We choose our coordinate system such that the orbital plane of the two-body system is in the $x-y$ plane.
-$\vec{\omega}$ is a constant vector that points in the direction of the rotation axis of the Earth-Sun reference frame.
-We will fit for $\vec{\omega}$, so we don't have to know it exactly before, but it can be estimated well and thus provides good starting points for the fit.
-The same is valid for the six components of the matrix $C$.
+The same is valid for the six components of the matrix $C$.\\
 
-Counting all unknown parameters in the equation of motion, we get
-16. They correspond to 6 initial conditions, 6 components of the
-matrix $C$, 3 components of the vector $\vec{\omega}$ and the object
-of main interest, $k$, which contains the gravitational constant ($k =
-GM$). Fitting for so many parameters is not an easy task, but it
-should be possible because the parameters are approximately known in
-advance.
+Counting all unknown parameters in the equation of motion, we get 16.
+They correspond to 6 initial conditions, 6 components of the matrix $C$, 3 components of the vector $\vec{\omega}$ and the object of main interest, $k$,  which contains the gravitational constant ($k = GM$).
+Fitting for so many parameters is not an easy task, but it should be possible because the parameters are not completely unknown.\\
 
@@
 
-To fit for $k$ and the 15 accompanying nuisance parameters, we suggest
-using a Markov Chain Monte-Carlo (MCMC) method, which are widely used
-for similarly large parameter spaces.  MCMC is a Bayesian approach,
-which uses the information provided by observed data about a set of
-parameters, to update a prior state of knowledge/ignorance about the
-set of parameters to become a posterior state of knowledge/ignorance
-about a set of parameters. We will not describe in detail how MCMC
-works, but refer the reader to an online tutorial from ESO
-PyCoffee\cite{esopycoffee} or an introduction paper from van
-Ravenzwaaij et al.\cite{vanRavenzwaaij16}
+Our problem has 16 unknown parameters, but the only one we are really interested in is $k$, which contains the gravitational constant.
+For the fit, we suggest to use a Markov Chain Monte-Carlo (MCMC) method because it does good work even if the parameter space is large.
+A Markov chain Monte-Carlo method is a Bayesian approach to data analysis.
+It uses the information provided by observed data about a set of parameters, to update a prior state of beliefs about the set of parameters to become a posterior state of beliefs about a set of parameters.
+We will not describe in detail how the MCMC is working, rather refer to an online tutorial from ESO PyCoffee\cite{esopycoffee} or an introduction paper from van Ravenzwaaij et al.\cite{vanRavenzwaaij16}
 
-We now briefly explain in what range the values of the parameters are
-estimated.  Numbers are given in Table~\ref{tab:parameters}.  For the
-parameter $k$, which is the product of the gravitational constant $G$
-and the total mass $M$ we look at the current measured values for the
-gravitational constant in Fig.~\ref{fig:Gmeasurements}, it is
-reasonable to constrain its numerical value in SI units to values
-between $6.671 \cdot 10^{-11}$ and $6.676 \cdot 10^{-11}$. The masses
-of the two balls will not contribute to a larger uncertainty in $k$,
-we choose them to be 6~kg.  The vector $\vec{\omega}$ accounts for the
-rotation of the reference frame. If we say that the orbit of the balls
-lies in the same plane as the orbital plane of the Earth,
-$\vec{\omega}$ will point in $z$-direction with $x$ and $y$
-components small. Thus $\omega_z$ is associated with the period
-$P_\odot$ of one year through $2\pi/P_\odot$. Because the rotation
-axis are conceivably not exactly aligned, we add some uncertainty. As
-mentioned before, the $x$ and $y$ components are small, that is to
-say, near zero in roughly in the range of the uncertainty in
-$\omega_z$.
+We briefly explain in what range the values of the parameters are estimated and display it in table~\ref{tab:parameters}.
+For the parameter $k$, which is the product of the gravitational constant $G$ and the total mass $M$ we look at the current measured values for the gravitational constant in Fig.~\ref{fig:Gmeasurements}, it is reasonable to constrain its numerical value in SI units to values between $6.671 \cdot 10^{-11}$ and $6.676 \cdot 10^{-11}$.
+The masses of the two balls will not contribute to a larger uncertainty in $k$, we choose them to be 6 kg.
+The vector $\vec{\omega}$ accounts for the rotation of the reference frame.
+If we say that the orbit of the balls lies in the same plane as the orbital plane of the Earth, $\vec{\omega}$ will point in $z$ - direction with $x$ and $y$ components small.
+Thus $\omega_z$ is associated with the period $P_\odot$ of one year through $2\pi/P_\odot$.
+Because the rotation axis are conceivably not exactly aligned, we add some uncertainty.
+As mentioned before, the $x$ and $y$ components are small, so to say roughly in the range of the uncertainty in $w_z$.
 
 The main contribution to the tidal term goes with $\omega^2$ and lies in the orbital plane.
-We are free to choose the $x$ and $y$ axis, so we choose it such that the $\omega^2$-contribution is in $x$-direction.
+We are free to choose the $x$ and $y$ axis, so we choose it such that it is in $x$-direction.
 The other five components then should be smaller, but we give some extra range to account for possible other perturbations.
@@
 
-In the next step, we set the parameters to a fixed ``true" value
-within the range estimated. We have to keep in mind that $k$, $x_0$
-and $v_{y_0}$ are linked together and there must not be contradictions
-in the true values. The chosen values are displayed in the right
-column in Table~\ref{tab:parameters}.  To simulate data we would
-obtain from the position measurements, we integrate the equations of
-motion. The time for one orbit without perturbations can be estimated
-using Kepler's third law (\ref{eq:kepler3}). For the value of $k$
-assumed above and a semi-major axis of $0.15 \, \mathrm{m}$, this
-results in an orbital period of roughly $12900 \, \mathrm{seconds}$ or
-$3.5 \, \mathrm{hours}$. Here we integrate two orbits in $100000$
-steps, that would correspond to about $4$ measurements per second,
-which should be feasible. To the generated data, we add Gaussian noise
-with a standard deviation of $10 \, \mathrm{nm}$. This uncertainty
-stays for a systematic error in the laser interferometry measurement
-and also random statistic noise. The value we use is just an estimate,
-it would depend strongly on the measurement system that has been used.
+In the next step, we set the parameters to a fixed ``true" value within the range estimated.
+We have to keep in mind that $k$, $x_0$ and $v_{y_0}$ are linked together and there must not be contradictions in the true values.
+The chosen values are displayed in the right column in Table~\ref{tab:parameters}.
+To simulate data we would obtain from the position measurements, we integrate the equations of motion.
+The time for one orbit without perturbations can be estimated using Kepler's third law (\ref{eq:kepler3}).
+For the value of $k$ assumed above and a semi-major axis of $0.15 \, \mathrm{m}$, this results in an orbital period of roughly $12900 \, \mathrm{seconds}$ or $3.5 \, \mathrm{hours}$.
+Here we integrate two orbits in $100000$ steps, that would correspond to about $4$ measurements per second, which should be feasible.
+To the generated data, we add normal distributed noise with a standard deviation of $10 \, \mathrm{nm}$.
+This uncertainty stays for a systematic error in the laser interferometry measurement and also random statistic noise.
+Its value is just an estimation, it would depend highly on the measurement system that has been used.
 
@@
 
-A useful way to look at the samples of the posterior returned by the MCMC is to make a corner plot using a Python module named \textit{corner}.\cite{corner} The corner plot shows all the one- and two-dimensional projections of the posterior probability distributions and demonstrates quickly the covariances between parameters.
+A useful way to look at the samples of the posterior returned by the MCMC is doing a corner plot using a Python module named \textit{corner}\cite{corner}.
+The corner plot shows all the one and two dimensional projections of the posterior probability distributions and demonstrates quickly the covariances between parameters.
 Along the diagonal, the marginalized distribution for each parameter independently is shown.
@@
 \section{Conclusion}
-We have outlined an orbit experiment to measure the gravitational
-constant $G$, and estimated the level of various disturbing effects
-and how to correct for them.  Simulating the measurement process and
-extraction of the gravitational constant indicates that $G$ could be
-estimated to about $10^{-7}$ relative uncertainty.  This is a about a
-factor of 300 better than today's recommended CODATA value.  If we are
-a bit optimistic, a further increase in precision is not out of reach,
-so that about the same relative uncertainty as for Planck's constant
-$h$ ($1.2 \cdot 10^{-8}$)\cite{CODATA16} could be achieved. This then
-would allow a future redefination of the kilogram as an integer
-multiple of the Planck mass.
+We have proposed a new way to measure the gravitational constant $G$ and estimated on what order of magnitude different disturbing effects occur and if one has to correct for them.
+We then simulated measurement data and showed how to extract the gravitational constant.
+Based on our estimations, it should be possible to measure the gravitational constant to about $10^{-7}$ relative uncertainty.
+This is a about a factor of 300 better than today's recommended CODATA value.
+
+If we are a bit optimistic, a further increase in precision is not out of reach, so that about the same relative uncertainty as for Planck's constant $h$ ($1.2 \cdot 10^{-8}$)\cite{CODATA16} could be achieved.
+This then would allow to redefine the kilogram as an integer multiple of the Planck mass.\\
+
+\appendix*   % Omit the * if there's more than one appendix.
+
+\section{Uninteresting stuff}
+
+%Appendices are for material that is needed for completeness but
+%not sufficiently interesting to include in the main body of the paper.  Most
+%articles don't need any appendices, but feel free to use them when
+%appropriate.  This sample article needs an appendix only to illustrate how 
+%to create an appendix.
 
@@
 }
+
+@ARTICLE{2005MNRAS.356..587C,
+   author = {{Christensen-Dalsgaard}, J. and {Di Mauro}, M.~P. and {Schlattl}, H. and 
+     {Weiss}, A.},
+    title = ``{On helioseismic tests of basic physics}'',
+  journal = {\mnras},
+ keywords = {Sun: fundamental parameters, Sun: helioseismology, Sun: interior, cosmological parameters},
+     year = 2005,
+    month = jan,
+   volume = 356,
+    pages = {587-595},
+      doi = {10.1111/j.1365-2966.2004.08477.x},
+   adsurl = {http://adsabs.harvard.edu/abs/2005MNRAS.356..587C},
+  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
+}

### 2017-11-30 manuscript_gravitationalconstant.tex
some edits

@@
 \begin{abstract}
-The kilogram could, in principle, be redefined as an integer multiple
-of the Planck mass (or 4594xxxx$\times\sqrt{\hbar c/G}$) with no
-significant change from its current value.  The practical hurdle is
-measuring $G$ three or four orders of magnitude better than currently
-known, so as to find the unknown digits xxxx.  We study a possible
-scenario for doing so with an artificial two-body orbit.  The cleanest
-(admittedly, not the cheapest) option is to place the system on a
-Trojan orbit to minimize external gravitational perturbations, and
-enclose it in a cavity chilled to liquid-helium temperatures, to
-suppress radiation pressure.  Data analysis would involve
-marginalizing over at least 15~nuisance parameters (6~for orbital
-parameters and 9~for fictitious forces) but that, we show, is
+As the kilogram assumes its new definition in terms of $h,c,$ and the
+standard second, it is interesting to think about a possible future
+definition entirely in terms of fundamental constants.  A kilogram
+defined as an integer multiple of the Planck mass (or
+4594xxxx$\times\sqrt{\hbar c/G}$) would cause no significant change
+from its current value.  The practical hurdle to this Planckian
+kilogram is measuring $G$ three or four orders of magnitude better
+than currently known, so as to find the unknown digits xxxx.  We study
+a possible scenario for doing so with an artificial two-body orbit.
+The cleanest (admittedly, not the cheapest) option is to place the
+system on a Trojan orbit to minimize external gravitational
+perturbations, and enclose it in a cavity chilled to liquid-helium
+temperatures, to suppress radiation pressure.  Data analysis would
+involve marginalizing over at least 15~nuisance parameters (6~for
+orbital parameters and 9~for fictitious forces) but that, we show, is
 feasible.
@@
 $G$-values and suggests a demand for new, potentially different
-techniques.
+techniques.  One remarkable idea is to use the helioseismic modes of
+the Sun, because they depend on both the mass and $G$ times the mass
+of the Sun,\cite{Ch-Dalsgaard05} but this strategy does not yet give
+competitive accuracy in $G$.
 
@@
 
+\bibitem{Ch-Dalsgaard05} J. Christensen-Dalsgaard, M.~P. Di Mauro,
+  H. Schlattl and A. Weiss, ``On helioseismic tests of basic
+  physics'', \textit{MNRAS}, 356:587--595 (2005).
+
 \bibitem{Loughridge13} R. Loughridge and D. Y. Abramovitch, ``A tutorial on laser interferometry for precision measurements,'' 

### 2017-11-30 manuscript_gravitationalconstant.tex
some words on low-Earth orbits

@@
 
-We are not supposing the measurement of the gravitational constant 
-using an artificial two-body system at an Earth-Sun Lagrange point to be a stand alone mission. It could be part of 
-a spacecraft reaching a Lagrange point. But our estimates suggest that this approach to increase the precision of the gravitational constant should be taken seriously.
+We have not attempted in this paper to consider the cost of such an
+experiment.  A mission to an Earth-Sun $L_4$ or $L_5$ with
+liquid-helium cryogenics would obviously be very expensive, and also
+carry an enhanced risk of unrepairable malfunctions killing the
+experiment.  If the goals could be achieved in low-Earth orbit, the
+prospects would be much more realistic.  The difficulty in low-Earth
+orbit is that tidal acceleration due to the Earth would become
+comparable to the two-body gravitational acceleration, with the Moon
+and Sun also tidally perturbing the system.  The two-body system would
+have a complicated orbit, very different from the nearly circular
+orbit we have considered, and the initial conditions would have to be
+chosen so as to avoid chaotic orbits.  Whether a sufficiently detailed
+model for the tidal acceleration could be constructed and fitted to
+the two-body orbital data is an open question.
 

### 2018-03-03 ms.tex
moving to bibtex

--- 2017-11-30 manuscript_gravitationalconstant.tex
@@
 The difficulty with Eq.~\eqref{eq:defs} is that all the expressions
-involve $G$.  Given the current uncertainties in $G$,\cite{CODATA16}
+involve $G$.  Given the current uncertainties in $G$,\cite{CODATA17}
 Eq.~\eqref{eq:defs} would allow units to be standardized only to four
@@
 The large disagreement is recognised immediately.
-The green lines represent the current recommended CODATA value and its uncertainty.\cite{CODATA16}}
+The green lines represent the current recommended CODATA value and its uncertainty.\cite{CODATA17}}
 	\label{fig:Gmeasurements}
@@
 extraction of the gravitational constant indicates that $G$ could be
-estimated to about $10^{-7}$ relative uncertainty.  This is a about a
+estimated to about $10^{-7}$ relative uncertainty.  This is about a
 factor of 300 better than today's recommended CODATA value.
@@
 Hence, about the same relative uncertainty as for Planck's constant
-$h$ ($1.2 \cdot 10^{-8}$)\cite{CODATA16} could be achieved. This then
+$h$ ($1.2 \cdot 10^{-8}$)\cite{CODATA17} could be achieved. This then
 would allow a future redefinition of the kilogram as an integer
@@
 \begin{thebibliography}{99}
-\bibitem{BIPM16} International Bureau of Weights and Measures, ``DRAFT 9th edition of the SI Brochure", BIPM, (2016)
+\bibliography{ms.bib}
+\end{thebibliography}
 
-\bibitem{Chao15} L.
+\end{document}
+
+bbibitem{BIPM16} International Bureau of Weights and Measures, ``DRAFT 9th edition of the SI Brochure", BIPM, (2016)
+
+bbibitem{Chao15} L.
 S.
@@
 Haddad, ``A LEGO Watt balance: An apparatus to determine a mass based on the new SI", \textit{American Journal of Physics}, 83:11:913--922 (2015).
+% 2015AmJPh..83..913C
 
-\bibitem{Tomilin1999} D. K. Tomilin, ``Natural Systems of Units. To the Centenary Anniversary of the Planck System,'' 
+bbibitem{Tomilin1999} D. K. Tomilin, ``Natural Systems of Units. To the Centenary Anniversary of the Planck System,'' 
 Proceedings of the XXII Workshop on high Energy Physics and field theory, 290 (1999).
 
-\bibitem{Planck99} M. Planck, ``\"{U}ber irreversible {S}trahlungsvorg\"{a}nge,'' 
+bbibitem{Planck99} M. Planck, ``\"{U}ber irreversible {S}trahlungsvorg\"{a}nge,'' 
 Sitzungsberichte der K\"{o}niglich Preussischen Akademie der Wissenschaften zu Berlin, 479--480 (1899).
 
-\bibitem{BIPM} Bureau International des Poids et Mesures, Calibration and measurement services: Mass, \url{<https://www.bipm.org/utils/common/pdf/cms_m.pdf>}, (2015).
+bbibitem{BIPM} Bureau International des Poids et Mesures, Calibration and measurement services: Mass, \url{<https://www.bipm.org/utils/common/pdf/cms_m.pdf>}, (2015).
 
-\bibitem{CODATA16} P. J. Mohr, D. B. Newell and B. N. Taylor, ``CODATA recommended values of the fundamental physical constants: 2014*, \textit{Reviews of Modern Physics}, 88(3):035009 (2016).
+bbibitem{CODATA16} P. J. Mohr, D. B. Newell and B. N. Taylor, ``CODATA recommended values of the fundamental physical constants: 2014*, \textit{Reviews of Modern Physics}, 88(3):035009 (2016).
 
-\bibitem{Quinn14} T.
+bbibitem{Quinn14} T.
 Quinn, C.
@@
 
-\bibitem{Newman14} R.
+bbibitem{Newman14} R.
 Newman, M.
@@
 
-\bibitem{Luo09} J.
+bbibitem{Luo09} J.
 Luo, W.
@@
 
-\bibitem{Schlamminger06} S.
+bbibitem{Schlamminger06} S.
 Schlamminger, E.
@@
 
-\bibitem{Parks10} H. V. Parks and J. E. Faller, ``Simple pendulum determination of the gravitational constant", \textit{Phys. Rev. Lett.}, 105:110801 (2010).
+bbibitem{Parks10} H. V. Parks and J. E. Faller, ``Simple pendulum determination of the gravitational constant", \textit{Phys. Rev. Lett.}, 105:110801 (2010).
 
-\bibitem{Rosi14} G.
+bbibitem{Rosi14} G.
 Rosi, F.
@@
 
-\bibitem{Ch-Dalsgaard05} J. Christensen-Dalsgaard, M.~P. Di Mauro,
+bbibitem{Ch-Dalsgaard05} J. Christensen-Dalsgaard, M.~P. Di Mauro,
   H. Schlattl and A. Weiss, ``On helioseismic tests of basic
@@
 
-\bibitem{Loughridge13} R. Loughridge and D. Y. Abramovitch, ``A tutorial on laser interferometry for precision measurements,'' 
+bbibitem{Loughridge13} R. Loughridge and D. Y. Abramovitch, ``A tutorial on laser interferometry for precision measurements,'' 
 American Control Conference, 3686--3703 (2013).
 
-\bibitem{esopycoffee} Fast and easy-to-implement Markov Chain Monte Carlo with the emcee package, ESO PyCoffee (2014),
+bbibitem{esopycoffee} Fast and easy-to-implement Markov Chain Monte Carlo with the emcee package, ESO PyCoffee (2014),
 \url{<http://eso-python.github.io/ESOPythonTutorials/ESOPythonDemoDay8_MCMC_with_emcee.html>}.
 
-\bibitem{vanRavenzwaaij16} D. van Ravenzwaji, P. Cassey and S. D. Brown, ``A simple introduction to Markov Chain Monte-Carlo sampling,'' 
+bbibitem{vanRavenzwaaij16} D. van Ravenzwaji, P. Cassey and S. D. Brown, ``A simple introduction to Markov Chain Monte-Carlo sampling,'' 
 Psychonomic Bulletin {\&} Review, 1--12 (2016).
 
-\bibitem{corner} D. Foreman-Mackey, ``corner.py: Scatterplot matrices in Python,'' 
+bbibitem{corner} D. Foreman-Mackey, ``corner.py: Scatterplot matrices in Python,'' 
 The Journal of Open Source Software (10), (2016).
-
-\end{thebibliography}
-
-\end{document}
-
-@INPROCEEDINGS{2016APS..APR.R5001S,
-   author = {{Schlamminger}, S.},
-    title = ``{Measurements of the gravitational constant - why we need new ideas}'',
-booktitle = {APS April Meeting Abstracts},
-     year = 2016,
-    month = mar,
-   adsurl = {http://adsabs.harvard.edu/abs/2016APS..APR.R5001S},
-  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
-}
-
-@ARTICLE{2005MNRAS.356..587C,
-   author = {{Christensen-Dalsgaard}, J. and {Di Mauro}, M.~P. and {Schlattl}, H. and 
-     {Weiss}, A.},
-    title = ``{On helioseismic tests of basic physics}'',
-  journal = {\mnras},
- keywords = {Sun: fundamental parameters, Sun: helioseismology, Sun: interior, cosmological parameters},
-     year = 2005,
-    month = jan,
-   volume = 356,
-    pages = {587-595},
-      doi = {10.1111/j.1365-2966.2004.08477.x},
-   adsurl = {http://adsabs.harvard.edu/abs/2005MNRAS.356..587C},
-  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
-}

### 2018-03-03 ms.tex
moving to bibtex

@@
 
-\begin{thebibliography}{99}
 \bibliography{ms.bib}
-\end{thebibliography}
 
@@
 
-bbibitem{BIPM16} International Bureau of Weights and Measures, ``DRAFT 9th edition of the SI Brochure", BIPM, (2016)
+\bibitem{BIPM16} International Bureau of Weights and Measures, ``DRAFT 9th edition of the SI Brochure", BIPM, (2016)
 
-bbibitem{Chao15} L.
+\bibitem{Chao15} L.
 S.
@@
 
-bbibitem{Tomilin1999} D. K. Tomilin, ``Natural Systems of Units. To the Centenary Anniversary of the Planck System,'' 
+\bibitem{Tomilin1999} D. K. Tomilin, ``Natural Systems of Units. To the Centenary Anniversary of the Planck System,'' 
 Proceedings of the XXII Workshop on high Energy Physics and field theory, 290 (1999).
 
-bbibitem{Planck99} M. Planck, ``\"{U}ber irreversible {S}trahlungsvorg\"{a}nge,'' 
+\bibitem{Planck99} M. Planck, ``\"{U}ber irreversible {S}trahlungsvorg\"{a}nge,'' 
 Sitzungsberichte der K\"{o}niglich Preussischen Akademie der Wissenschaften zu Berlin, 479--480 (1899).
 
-bbibitem{BIPM} Bureau International des Poids et Mesures, Calibration and measurement services: Mass, \url{<https://www.bipm.org/utils/common/pdf/cms_m.pdf>}, (2015).
+\bibitem{BIPM} Bureau International des Poids et Mesures, Calibration and measurement services: Mass, \url{<https://www.bipm.org/utils/common/pdf/cms_m.pdf>}, (2015).
 
-bbibitem{CODATA16} P. J. Mohr, D. B. Newell and B. N. Taylor, ``CODATA recommended values of the fundamental physical constants: 2014*, \textit{Reviews of Modern Physics}, 88(3):035009 (2016).
+\bibitem{CODATA16} P. J. Mohr, D. B. Newell and B. N. Taylor, ``CODATA recommended values of the fundamental physical constants: 2014*, \textit{Reviews of Modern Physics}, 88(3):035009 (2016).
 
-bbibitem{Quinn14} T.
+\bibitem{Quinn14} T.
 Quinn, C.
@@
 
-bbibitem{Newman14} R.
+\bibitem{Newman14} R.
 Newman, M.
@@
 
-bbibitem{Luo09} J.
+\bibitem{Luo09} J.
 Luo, W.
@@
 
-bbibitem{Schlamminger06} S.
+\bibitem{Schlamminger06} S.
 Schlamminger, E.
@@
 
-bbibitem{Parks10} H. V. Parks and J. E. Faller, ``Simple pendulum determination of the gravitational constant", \textit{Phys. Rev. Lett.}, 105:110801 (2010).
+\bibitem{Parks10} H. V. Parks and J. E. Faller, ``Simple pendulum determination of the gravitational constant", \textit{Phys. Rev. Lett.}, 105:110801 (2010).
 
-bbibitem{Rosi14} G.
+\bibitem{Rosi14} G.
 Rosi, F.
@@
 
-bbibitem{Ch-Dalsgaard05} J. Christensen-Dalsgaard, M.~P. Di Mauro,
+\bibitem{Ch-Dalsgaard05} J. Christensen-Dalsgaard, M.~P. Di Mauro,
   H. Schlattl and A. Weiss, ``On helioseismic tests of basic
@@
 
-bbibitem{Loughridge13} R. Loughridge and D. Y. Abramovitch, ``A tutorial on laser interferometry for precision measurements,'' 
+\bibitem{Loughridge13} R. Loughridge and D. Y. Abramovitch, ``A tutorial on laser interferometry for precision measurements,'' 
 American Control Conference, 3686--3703 (2013).
 
-bbibitem{esopycoffee} Fast and easy-to-implement Markov Chain Monte Carlo with the emcee package, ESO PyCoffee (2014),
+\bibitem{esopycoffee} Fast and easy-to-implement Markov Chain Monte Carlo with the emcee package, ESO PyCoffee (2014),
 \url{<http://eso-python.github.io/ESOPythonTutorials/ESOPythonDemoDay8_MCMC_with_emcee.html>}.
 
-bbibitem{vanRavenzwaaij16} D. van Ravenzwaji, P. Cassey and S. D. Brown, ``A simple introduction to Markov Chain Monte-Carlo sampling,'' 
+\bibitem{vanRavenzwaaij16} D. van Ravenzwaji, P. Cassey and S. D. Brown, ``A simple introduction to Markov Chain Monte-Carlo sampling,'' 
 Psychonomic Bulletin {\&} Review, 1--12 (2016).
 
-bbibitem{corner} D. Foreman-Mackey, ``corner.py: Scatterplot matrices in Python,'' 
+\bibitem{corner} D. Foreman-Mackey, ``corner.py: Scatterplot matrices in Python,'' 
 The Journal of Open Source Software (10), (2016).

### 2018-03-03 ms.tex
formatted in A&A style

--- 2018-03-03 ms.tex
@@
-\documentclass[prb,preprint]{revtex4-1} 
-% The line above defines the type of LaTeX document.
-% Note that AJP uses the same style as Phys. Rev. B (prb).
+%\documentclass[referee]{aa} % for a referee version
+\documentclass[onecolumn]{aa} % for a paper on 1 column  
+%\documentclass[longauth]{aa} % for the long lists of affiliations 
+%\documentclass[letter]{aa} % for the letters 
+%\documentclass[bibyear]{aa} % if the references are not structured 
+%                              according to the author-year natbib style
+%\documentclass{aa}
 
-% The % character begins a comment, which continues to the end of the line.
-
-\usepackage{amsmath}  % needed for \tfrac, \bmatrix, etc.
-\usepackage{amsfonts} % needed for bold Greek, Fraktur, and blackboard bold
-\usepackage{graphicx} % needed for figures
-\usepackage{epstopdf}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{txfonts}
 
@@
 
-% Be sure to use the \title, \author, \affiliation, and \abstract macros
-% to format your title page.  Don't use lower-level macros to  manually
-% adjust the fonts and centering.
+\title{Towards a Planckian standard kilogram}
+\subtitle{}
 
-\title{A scenario for a Planckian standard kilogram}
-% In a long title you can use \\ to force a line break at a certain location.
+\author{Michael Ebersold\thanks{michael.ebersold@uzh.ch}%\inst{1}
+        \and
+        Prasenjit Saha%\inst{2}\fnmsep
+       }
 
-\author{Michael Ebersold}
-\email{michael.ebersold@uzh.ch} 
-% If there were a second author at the same address, we would put another 
-% \author{} statement here.  Don't combine multiple authors in a single
-% \author statement.
-\author{Prasenjit Saha}
-\email{psaha@physik.uzh.ch}
-% Please provide a full mailing address here.
-\affiliation{Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland}
+\institute{Physik-Institut, University of Zurich, Winterthurerstrasse
+  190, 8057 Zurich, Switzerland}
 
-% See the REVTeX documentation for more examples of author and affiliation lists.
+\date{}
 
-\date{\today}
-
-\begin{abstract}
-As the kilogram assumes its new definition in terms of $h,c,$ and the
+\abstract
+% context heading (optional)
+% {} leave it empty if necessary  
+{As the kilogram assumes its new definition in terms of $h,c,$ and the
   standard second, it is interesting to think about a possible future
@@
   4594xxxx$\times\sqrt{\hbar c/G}$) would cause no significant change
-from its current value.  The practical hurdle to this Planckian
-kilogram is measuring $G$ three or four orders of magnitude better
-than currently known, so as to find the unknown digits xxxx.  We study
-a possible scenario for doing so with an artificial two-body orbit.
-The cleanest (admittedly, not the cheapest) option is to place the
+  from its current value.}
+% aims heading (mandatory)
+{The practical hurdle to this Planckian kilogram is measuring $G$
+  three or four orders of magnitude better than currently known, so as
+  to find the unknown digits xxxx.  We study a possible scenario for
+  doing so with an artificial two-body orbit.}
+% methods heading (mandatory)
+{The cleanest (admittedly, not the cheapest) option is to place the
   system on a Trojan orbit to minimize external gravitational
   perturbations, and enclose it in a cavity chilled to liquid-helium
-temperatures, to suppress radiation pressure.  Data analysis would
-involve marginalizing over at least 15~nuisance parameters (6~for
-orbital parameters and 9~for fictitious forces) but that, we show, is
-feasible.
-\end{abstract}
+  temperatures, to suppress radiation pressure.}
+% results heading (mandatory)
+{Data analysis would involve marginalizing over at least 15~nuisance
+  parameters (6~for orbital parameters and 9~for fictitious forces)
+  but that, we show, is feasible.}
+% conclusions heading (optional), leave it empty if necessary 
+{}
+
+\keywords{}
 
@@
 The reform of SI units to use quantum standards is an ongoing ``news
-story'' in physics.\cite{BIPM16}  At the heart of the reform are two quantum
-phenomena that appear on macroscopic scales: the Josephson effect
-makes $h/e$ measurable as a voltage-to-frequency ratio, while the
-quantum Hall effect makes $h/e^2$ a standard resistance (the
-von~Klitzing constant).  These enable electrical units to be defined
-in terms of $h$ and $e$.  A further ingenious instrument, known as a
-watt balance, precisely compares electrical and mechanical power, thus
-enabled mass to be standardized in terms of $h$.  For a simple
-introduction to the new SI, we refer the reader to the article on the
-``LEGO watt balance''.\cite{Chao15}
-The proposed redefinition of the kilogram is an explicit value for
-$h$ and $c$, but we can think of it as
+story'' in physics.\footnote{International Bureau of Weights and
+  Measures, ``DRAFT 9th edition of the SI Brochure", BIPM.}  At the
+heart of the reform are two quantum phenomena that appear on
+macroscopic scales: the Josephson effect makes $h/e$ measurable as a
+voltage-to-frequency ratio, while the quantum Hall effect makes
+$h/e^2$ a standard resistance (the von~Klitzing constant).  These
+enable electrical units to be defined in terms of $h$ and $e$.  A
+further ingenious instrument, known as a watt balance, precisely
+compares electrical and mechanical power, thus enabled mass to be
+standardized in terms of $h$.  For a simple introduction to the new
+SI, we refer the reader to the article on the ``LEGO watt
+balance''.\citep{Chao15} The proposed redefinition of the kilogram is
+an explicit value for $h$ and $c$, but we can think of it as
 \begin{equation}
@@
 small but microscopically measurable: $\sim20\mu\mathrm{g}$.  This is
-of the same order as the uncertainty in the prototype kilogram itself.\cite{BIPM}
+of the same order as the uncertainty in the prototype kilogram
+itself.\footnote{\url{<https://www.bipm.org/utils/common/pdf/cms_m.pdf>}}
 Hence the kilogram could be redefined as an integer multiple of the
@@
 works, but refer the reader to an online tutorial from ESO
-PyCoffee\cite{esopycoffee} or an introduction paper from van
+PyCoffee\footnote{\url{<http://eso-python.github.io/ESOPythonTutorials/ESOPythonDemoDay8_MCMC_with_emcee.html>}}
+or an introduction paper from van
 Ravenzwaaij et al.\cite{vanRavenzwaaij16}
@@
 
-\begin{table}[h]
+\begin{table}%[ht]
 	\centering
 	\caption{This table shows the ranges in which the parameters numerical values in SI units are estimated to make sense and the value which was chosen to generate data.}
-	\begin{ruledtabular}
+%	\begin{ruledtabular}
 		\begin{tabular}{l c c}
@@
 		\end{tabular}
-	\end{ruledtabular}
+%	\end{ruledtabular}
 	\label{tab:parameters}
@@
 
-\begin{figure}[h]
+\begin{figure}%[ht]
 	\centering
@@
 
-\begin{thebibliography}{99}
+\bibliographystyle{aa}
 \bibliography{ms.bib}
-\end{thebibliography}
 

### 2018-03-03 manuscript_gravitationalconstant.tex
typos fixed

--- 2017-11-29 manuscript_gravitationalconstant.tex
@@
 \begin{abstract}
-The kilogram could, in principle, be redefined as an integer multiple
-of the Planck mass (or 4594xxxx$\times\sqrt{\hbar c/G}$) with no
-significant change from its current value.  The practical hurdle is
-measuring $G$ three or four orders of magnitude better than currently
-known, so as to find the unknown digits xxxx.  We study a possible
-scenario for doing so with an artificial two-body orbit.  The cleanest
-(admittedly, not the cheapest) option is to place the system on a
-Trojan orbit to minimize external gravitational perturbations, and
-enclose it in a cavity chilled to liquid-helium temperatures, to
-suppress radiation pressure.  Data analysis would involve
-marginalizing over at least 15~nuisance parameters (6~for orbital
-parameters and 9~for fictitious forces) but that, we show, is
-feasible.
+
 \end{abstract}
@@
 \maketitle
-
-\section{Introduction}
-
-The reform of SI units to use quantum standards is an ongoing ``news
-story'' in physics.\cite{BIPM16}  At the heart of the reform are two quantum
-phenomena that appear on macroscopic scales: the Josephson effect
-makes $h/e$ measurable as a voltage-to-frequency ratio, while the
-quantum Hall effect makes $h/e^2$ a standard resistance (the
-von~Klitzing constant).  These enable electrical units to be defined
-in terms of $h$ and $e$.  A further ingenious instrument, known as a
-watt balance, precisely compares electrical and mechanical power, thus
-enabled mass to be standardized in terms of $h$.  For a simple
-introduction to the new SI, we refer the reader to the article on the
-``LEGO watt balance''.\cite{Chao15}
-The proposed redefinition of the kilogram is an explicit value for
-$h$ and $c$, but we can think of it as
-\begin{equation}
-\mathrm{kg} \equiv 1.3563925\ldots \times 10^{50} \, \mathrm{s}^{-1}
-                   \times \frac{h}{c^2}
-\end{equation}
-with the exact value to be decided.  As we can see, the kilogram is
-coupled to the definition of a second.  That is not a problem in
-practice, as the second is standardized orders of magnitude better
-than any other unit.  Nonetheless, it is interesting to consider a
-logical further step of decoupling the kilogram from other
-definitions.  This could be done by introducing the gravitational
-constant, since $\sqrt{hc/G}$ has dimensions of mass.
-Historically, there have been several proposed unit systems that
-included $G$ in some way,\cite{Tomilin1999} but the idea of including
-both gravity and quantum mechanics in a unit system comes from
-Planck.\cite{Planck99} In the process of working towards the radiation
-law, Planck realized that $c,G,h$ and the Boltzmann constant $k_B$ (in
-his notation $G\rightarrow f$, $h\rightarrow b$, $h/k_B\rightarrow a$)
-naturally define units for mass, length, time, and temperature.
-Indeed, Planck remarked that such units would be meaningful even in
-non-human and extraterrestrial cultures.
-
-A hypothetical Planckian SI unit system would have
-\begin{equation} \label{eq:defs}
-\begin{aligned}
-\mathrm{kg} &= 4.594\ldots \times 10^7
-               \left(\frac{\hbar c}{G}\right)^{\!1/2} \\
-\mathrm{m}  &= 6.187\ldots \times 10^{34}
-               \left(\frac{\hbar G}{c^3}\right)^{\!1/2} \\
-\mathrm{s}  &= 1.854\ldots \times 10^{43}
-               \left(\frac{\hbar G}{c^5}\right)^{\!1/2} \\
-\mathrm{K}  &= 7.058\ldots \times 10^{-33}
-               \left(\frac{\hbar c^5}{Gk_B^2}\right)^{\!1/2}
-\end{aligned}
-\end{equation}
-with the numerical coefficients chosen so as to match the present
-standards.  The square-rooted expressions are conventionally known as
-the Planck mass, Planck length, and so on.  (They are actually
-$\sqrt{2\pi}$ smaller than Planck's definitions.)  Extension to
-electrical units is straightforward, but we will not discuss it here.
-The Planck length, time, and temperature in themselves are extreme
-scales, not probed by any known physical process, and presumably the
-regime of quantum gravity.  But extreme scales do not harm if they are
-only part of some expression, as they are here.  The Planck mass is
-small but microscopically measurable: $\sim20\mu\mathrm{g}$.  This is
-of the same order as the uncertainty in the prototype kilogram itself.\cite{BIPM}
-Hence the kilogram could be redefined as an integer multiple of the
-Planck mass, without significantly perturbing its value.
-
-The difficulty with Eq.~\eqref{eq:defs} is that all the expressions
-involve $G$.  Given the current uncertainties in $G$,\cite{CODATA16}
-Eq.~\eqref{eq:defs} would allow units to be standardized only to four
-significant digits, which is obviously not enough.  Improvement by
-several orders of magnitude would be needed, to make the Planckian
-kilogram practicable.  In this paper, we study a scenario which may
-make such an improvement possible.  The same process would suffice to
-move the Kelvin scale to a Planckian basis as well.  A Planckian
-second or metre, however, are not a prospect with anything like
-present technology, because demands on the time standard are more
-stringent still.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{img/plotGmeas}
-	\caption{Six of the most recent measurements of the gravitational constant $G$ with their uncertainties are plotted.
-The large disagreement is recognised immediately.
-The green lines represent the current recommended CODATA value and its uncertainty.\cite{CODATA16}}
-	\label{fig:Gmeasurements}
-\end{figure}
-
-\section{A new approach to measure $G$}
-In Fig.~\ref{fig:Gmeasurements} we plot the best-known recent
-measurements of the gravitational constant. Three of them
-(BIPM-14,\cite{Quinn14} UCI-14,\cite{Newman14} and
-HUST-09\cite{Luo09}) were carried out using a torsion balance, whereas
-UZur-06\cite{Schlamminger06} used a beam balance, and
-JILA-10\cite{Parks10} measured the separation of two simple pendulums
-in a gravitational field. They all tried to measure the very weak
-gravitational force with a mechanical apparatus. The sixth measurement
-(LENS-14\cite{Rosi14}) was performed with another approach, using cold
-atom interferometry. Its uncertainty is a lot larger than the others,
-but it could become more competitive in the future. However, a brief
-glance on the plotted measurements shows the disagreement of current
-$G$-values and suggests a demand for new, potentially different
-techniques.
-
-\subsection{An artificial two-body gravitating system}
-Newton's law of gravitation does not only explain why an apple falls
-down from a tree, it also explains orbits. If one has two bodies of
-masses $m_1$ and $m_2$, on which the only force acting is their
-respective gravitational attraction, they will orbit around the common
-center of mass, with the relative vector tracing an ellipse
-described by Kepler's laws. The third law, relates the
-orbital period $P$ to semimajor axis $a$ of the ellipse, as
-\begin{equation}\label{eq:kepler3}
-P^2 = \frac{4 \, \pi^2}{G(m_1+m_2)}a^3
-\end{equation}
-with the gravitational constant $G$ appearing in the proportionality
-factor.  If one can measure the position of the two masses very
-accurately and thus the orbit is known, it is possible to deduce the
-gravitational constant.  So what we need is a freely-falling two-body
-system. The only way to achieve this over some time, is to go into
-space. Thus, one has to design a spacecraft with a cavity that
-contains the two masses and a position measurement apparatus. The
-cavity should shield the two-body system from environmental
-influences. The spacecraft is then put in space, at a location where
-tidal forces are minimal.  The stable Lagrange points of the Earth-Sun
-system (that is, $L_4$ or $L_5$, also known as the Earth-Trojan
-locations) would be suitable.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.9\textwidth]{img/sketchnonumb.pdf}
-	\caption{Sketch on how the two masses inside the cavity of a spacecraft orbit around each other.}
-	\label{fig:sketch}
-\end{figure}
-
-To get a feeling what the dimensions of such an experiment could be,
-choose for example lead balls with a diameter of about 10~cm, their
-mass then is about 6~kg. If one then chooses a semimajor axis of
-15~cm, the orbital period would be roughly 3.5~hours and the
-gravitational force acting between the two bodies is of order
-$10^{-8}$~N.  In Fig.~\ref{fig:sketch} we show a sketch on how this
-would look like.
-Treating this system with Newtonian gravity is justified, because corrections from general relativity would be of order $(v^2/c^2)$ and $(GM/rc^2)$, which for our two-body system are both very small numbers.
-To follow the mutual orbit of the two balls, best
-would be a laser interferometry system, which can yield precisions
-down to some nanometers.\cite{Loughridge13}
-
-Such a system, if it could be set up, promises two advantages.  One is
-the avoidance of any mechanical contact with the gravitating parts of
-the experiment.  The other advantage lies in the behavior of signal
-and noise.  The signal, which is essentially the distance travelled,
-is proportional to time. The noise, however, would be almost
-time-independent. This suggests that signal-to-noise would be
-proportional to the length of the experiment, until it was limited by
-systematic error. The achievable accuracy would therefore depend
-entirely on how well external perturbations to the gravitational
-two-body problem could be eliminated, or corrected for.  In following,
-we consider the expected perturbations.
-
-\subsection{Disturbing effects}
-
-\textbf{Radiation pressure:} The envelope of the cavity needs to protect the two body-system from the constant bombardment of radiation and charged particles from the Sun.
-Since the activity of the Sun varies much, the spacecraft must be able to correct its position around the freely falling masses inside the cavity.\\
-Furthermore, there is thermal radiation inside the cavity, that could disturb the orbit.
-Using the Stefan-Boltzmann law, we can relate radiation pressure to the temperature inside the cavity. If we then specify to balls of diameter $d$, we can express the force on the balls as 
-\begin{equation}
-F = \frac{2 \pi^6 d^2 {k_\mathrm{B}}^4 T^4}{45 c^3 h^3}.
-\end{equation}
-As we can see, this force is highly temperature dependent.
-In order to minimize this influence, one should deploy a temperature as small as possible in the cavity.
-In fact, if a cooling system based on liquid helium is installed, temperature can be brought down to about 4 K.
-Such a low temperature results in a force on the balls in the order of $10^{-16}$~N.
-Compared to the gravitational force, this is orders of magnitude less and thus we don't have to worry about effects of radiation pressure.
-
-\textbf{Influence of the position measurement:} 
-The photons of the laser that measures the position of the two balls exert an additional force.
-If a laser with a power of 1~mW is used and not more than five measurements every second are performed, the force on the balls is in the same order as the influence of thermal radiation and thus negligible too.
-
-\textbf{Coulomb force:}
-Since the electromagnetic force is orders of magnitude stronger than the gravitational force, the balls must be absolutely neutral.
-A possible source of charges are cosmic rays or the solar wind, so the two bodies have to be adequately shielded by the enclosing shell.
-If we want that the Coulomb force between the balls is in the same order as the effect of thermal radiation and thus negligible, the maximal allowed charge on the balls is about $6 \cdot 10^{-14}$~C, which corresponds to roughly $4 \cdot 10^5$ elementary charges.
-
-\textbf{Coriolis effect:}
-\label{sec:coriolis}
-The Coriolis force is a fictitious force which only acts on moving bodies in a rotating reference frame.
-If we imagine the spacecraft located stationary at a Lagrange point of the Earth-Sun system, it is situated in a rotating frame around the Earth-Sun barycenter.
-Since the balls are moving with respect to this frame, there will be a Coriolis acceleration
-\begin{equation}
-\label{eq:coriolis}
-\ddot{\vec{r}}_\mathrm{c} = - 2 \; \vec{\omega} \times \dot{\vec{r}}.
-\end{equation}
-In this formula, $\vec{\omega}$ is the angular velocity vector of the rotating frame and $\dot{\vec{r}}$ is the velocity vector in the two-body system.
-
-\textbf{Centrifugal and tidal forces:}
-\label{sec:tidal}
-The free fall condition is not possible to achieve for both masses simultaneously since we are in a non-inertial, rotating frame and therefore have to account for centrifugal forces.
-The centrifugal acceleration $\ddot{\vec{r}}_{\mathrm{Z}}$ is proportional to the distance vector $\vec{r}$ and scales with $\omega^2$, where $\omega$ is the angular velocity of the Sun-Earth reference frame:
-\begin{equation}
-\label{eq:centrifugalacc}
-\ddot{\vec{r}}_{\mathrm{Z}} = \vec{\omega} \times \left( \vec{\omega} \times \vec{r} \right) 
-\end{equation}
-In addition, there are tidal forces.
-If one mass is closer to the Sun, the gravitational force on it is slightly bigger than on the other mass.
-This results in a force perturbation, which is also proportional to $r$.
-One can approximate the tidal acceleration as
-\begin{equation}
-\label{eq:tidalacc}
-\ddot{\vec{r}}_{\mathrm{\tau}} \approx \frac{2 \, G \, M_\odot}{R^3} \, \vec{r}.
-\end{equation}
-In this equation $M_\odot$ is the solar mass and $R$ is the radius of the orbit around the Sun.
-With Kepler's third law one can rewrite the tidal acceleration as a function of the orbital period squared of the Sun-Earth reference frame.
-Thus it scales the same way as the centrifugal force.
-To estimate the magnitude of the centrifugal and tidal acceleration relative to the gravitational acceleration between the two balls, we find that their ratio is proportional to the orbital periods squared
-\begin{equation}\label{a_ratio}
-\frac{\ddot{r}_{\mathrm{\tau}}}{\ddot{r}_\mathrm{G}} \propto \frac{P^2}{{P_\odot}^2} \approx 10^{-7},
-\end{equation}
-where $P_\odot$ corresponds to one year, whereas $P$ is the orbital period of the two balls.
-So tidal and centrifugal effects are about $10^{-7}$ times smaller than the respective gravity of the two balls.
-
-\textbf{Gravitational field:}
-Much attention has to be paid to the effect of the gravitational field of the spacecraft itself and the measurement apparatus.
-This certainly can't be neglected, but with a clever design, its effects can be minimized.
-For example an almost spherically symmetric spacecraft would probably be a good choice.
-It should also be possible to calculate the gravitational field caused by the components of the spacecraft at the positions of the balls.
-Then one can correct the equation of motion by adding an extra term that is accounting for the gravitational field.
-\\
-A source of an additional gravitational field is Earth's moon and the other planets in the solar system.
-Fortunately, for this we don't need to correct if the whole system, consisting of the spacecraft and the two-body system, is moving through space together.
-Although, the spacecraft should be able to correct its position around the two balls to avoid a collision.
-
-\section{Extracting $G$ from position measurement data}
-
-In this section we will show how the gravitational constant can be
-recovered from the position data of the two balls that the laser
-interferometry measurement would provide.  But first we have to find
-the orbital equation of motion for the two balls.
-
-\subsection{Orbital equation of motion}
-From Newtonian dynamics the equation of motion for a clean two-body system is given by 
-\begin{equation}
-\label{eq:eomeasy}
-\ddot{\vec{r}} = - \frac{G M\, \vec{r}}{r^3}.
-\end{equation}
-Here $M$ denotes the sum of the masses $m_1$ and $m_2$, $G$ is the
-gravitational constant and $r$ is the relative distance between the
-two bodies. For simplicity we will abbreviate the product of $GM$ with
-$k$.  Since our two-body system is in a rotating frame, we have to add
-the term developed before for the Coriolis acceleration, as well as a
-correction term for centrifugal and tidal forces. The latter can be
-written with a constant symmetric $3 \times 3$ matrix $C$ as follows
-\begin{equation}
-\label{eq:tidal}
-\ddot{\vec{r}}_{\mathrm{C}} = C \cdot \vec{r},
-\end{equation}
-or in terms of the individual components 
-\begin{equation}
-\label{eq:tidacom}
-\left(\ddot{r}_\mathrm{C}\right)_i = \sum_{k=1}^{3} C_{ik} \: r_k.
-\end{equation}
-The reference frame is chosen such that the barycenter of the two-body
-system is freely falling and has no tidal or fictitious forces acting
-on it.  The balls, however, do experience such forces, because they
-are not at the centre of mass.  The $C$ term can be thought of as a
-first-order expansion of these forces.  So the full equation of motion
-for the two balls looks as follows:
-\begin{equation}
-\label{eq:eom}
-\ddot{\vec{r}} = - \frac{k\,\vec{r}}{r^3} - 2 \; \vec{\omega} \times \dot{\vec{r}} + C \cdot \vec{r}
-\end{equation}
-
-These are actually three coupled equations of motion, one for each spatial coordinate.
-Since all are second order differential equations, we need to give six initial conditions to determine the orbit.\\
-We choose our coordinate system such that the orbital plane of the two-body system is in the $x-y$ plane.
-$\vec{\omega}$ is a constant vector that points in the direction of the rotation axis of the Earth-Sun reference frame.
-We will fit for $\vec{\omega}$, so we don't have to know it exactly before, but it can be estimated well and thus provides good starting points for the fit.
-The same is valid for the six components of the matrix $C$.
-We choose our coordinate system such that the orbital plane of the two-body system is in the $x-y$ plane.
-$\vec{\omega}$ is a constant vector that points in the direction of the rotation axis of the Earth-Sun reference frame.
-We will fit for $\vec{\omega}$, so we don't have to know it exactly before, but it can be estimated well and thus provides good starting points for the fit.
-The same is valid for the six components of the matrix $C$.
-
-Counting all unknown parameters in the equation of motion, we get
-16. They correspond to 6 initial conditions, 6 components of the
-matrix $C$, 3 components of the vector $\vec{\omega}$ and the object
-of main interest, $k$, which contains the gravitational constant ($k =
-GM$). Fitting for so many parameters is not an easy task, but it
-should be possible because the parameters are approximately known in
-advance.
-
-\subsection{Markov Chain Monte-Carlo fit}
-
-To fit for $k$ and the 15 accompanying nuisance parameters, we suggest
-using a Markov Chain Monte-Carlo (MCMC) method, which are widely used
-for similarly large parameter spaces.  MCMC is a Bayesian approach,
-which uses the information provided by observed data about a set of
-parameters, to update a prior state of knowledge/ignorance about the
-set of parameters to become a posterior state of knowledge/ignorance
-about a set of parameters. We will not describe in detail how MCMC
-works, but refer the reader to an online tutorial from ESO
-PyCoffee\cite{esopycoffee} or an introduction paper from van
-Ravenzwaaij et al.\cite{vanRavenzwaaij16}
-
-We now briefly explain in what range the values of the parameters are
-estimated.  Numbers are given in Table~\ref{tab:parameters}.  For the
-parameter $k$, which is the product of the gravitational constant $G$
-and the total mass $M$ we look at the current measured values for the
-gravitational constant in Fig.~\ref{fig:Gmeasurements}, it is
-reasonable to constrain its numerical value in SI units to values
-between $6.671 \cdot 10^{-11}$ and $6.676 \cdot 10^{-11}$. The masses
-of the two balls will not contribute to a larger uncertainty in $k$,
-we choose them to be 6~kg.  The vector $\vec{\omega}$ accounts for the
-rotation of the reference frame. If we say that the orbit of the balls
-lies in the same plane as the orbital plane of the Earth,
-$\vec{\omega}$ will point in $z$-direction with $x$ and $y$
-components small. Thus $\omega_z$ is associated with the period
-$P_\odot$ of one year through $2\pi/P_\odot$. Because the rotation
-axis are conceivably not exactly aligned, we add some uncertainty. As
-mentioned before, the $x$ and $y$ components are small, that is to
-say, near zero in roughly the range of the uncertainty in
-$\omega_z$.
-
-The main contribution to the tidal term goes with $\omega^2$ and lies in the orbital plane.
-We are free to choose the $x$ and $y$ axis, so we choose it such that the $\omega^2$-contribution is in $x$-direction.
-The other five components then should be smaller, but we give some extra range to account for possible other perturbations.
-The initial values for the positions can be guessed very accurately, since they are directly measured precisely.
-The initial velocity can be calculated easily and matched to the initial positions, therefore also yielding narrow parameter ranges.
-
-\begin{table}[h]
-	\centering
-	\caption{This table shows the ranges in which the parameters numerical values in SI units are estimated to make sense and the value which was chosen to generate data.}
-	\begin{ruledtabular}
-		\begin{tabular}{l c c}
-			% The codes above determine the horizontal alignment in each column.
-			% Options are l (left), r (right), c (centered), and p (paragraph).
-			% The p option allows an entry to be broken into multiple lines, and
-			% therefore requires a width specification, in this case 5 centimeters.
-			parameter & range & chosen value \\
-			\hline	% horizontal line to separate headings from data
-			$k$ & $(8.0052$--$8.0112) \cdot 10^{-10}$ & $8.0088 \cdot 10^{-10}$ \\
-			$\omega_x$ & $\pm 1.0 \cdot 10^{-8}$ & $0.02 \cdot 10^{-8}$ \\
-			$\omega_y$ & $\pm 1.0 \cdot 10^{-8}$ & $-0.03 \cdot 10^{-8}$ \\
-			$\omega_z$ & $(1.95$--$2.05) \cdot 10^{-7}$ & $1.996 \cdot 10^{-7}$ \\
-			$C_{xx}$ & $0$--$5.0 \cdot 10^{-14}$ & $3.8 \cdot 10^{-14}$ \\
-			$C_{yy}$ & $\pm 10^{-14}$ & $0.3 \cdot 10^{-14}$ \\
-			$C_{zz}$ & $\pm 10^{-14}$ & $-0.2 \cdot 10^{-14}$ \\
-			$C_{xy} = C_{yx}$ & $\pm 10^{-14}$ & $0.3 \cdot 10^{-14}$ \\
-			$C_{yz} = C_{zy}$ & $\pm 10^{-14}$ & $0.1 \cdot 10^{-14}$ \\
-			$C_{xz} = C_{zx}$ & $\pm 10^{-14}$ & $-0.4 \cdot 10^{-14}$ \\
-			$x_0$ & $0.15 \pm 10^{-7}$ & $0.15$ \\
-			$y_0$ & $\pm 10^{-7}$ & $0.0$ \\ 
-			$z_0$ & $\pm 10^{-7}$ & $0.0$ \\ 
-			$v_{x_0}$ & $\pm 10^{-7}$ & $0.0$ \\ 
-			$v_{y_0}$ & ($7.30$--$7.31) \cdot 10^{-7}$ & $7.30698296 \cdot 10^{-5}$ \\
-			$v_{z_0}$ & $\pm 10^{-7}$ & $0.0$ \\
-		\end{tabular}
-	\end{ruledtabular}
-	\label{tab:parameters}
-\end{table}
-
-In the next step, we set the parameters to a fixed ``true" value
-within the range estimated. We have to keep in mind that $k$, $x_0$
-and $v_{y_0}$ are linked together and there must not be contradictions
-in the true values. The chosen values are displayed in the right
-column of Table~\ref{tab:parameters}.  To simulate data we would
-obtain from the position measurements, we integrate the equations of
-motion. The time for one orbit without perturbations can be estimated
-using Kepler's third law (\ref{eq:kepler3}). For the value of $k$
-assumed above and a semi-major axis of $0.15$~m, this
-results in an orbital period of roughly 12900 seconds or
-3.5 hours. Here we integrate two orbits in 100000
-steps, that would correspond to about 4 measurements per second,
-which should be feasible. To the generated data, we add Gaussian noise
-with a standard deviation of 10~nm. The value we use is just an estimate,
-it would depend strongly on the measurement system that has been used.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1.0\textwidth]{img/4cornerfit.png}
-	\caption{Corner plot of the posterior for 4 parameters: $x_0$, $v_{y_0}$, $\omega_z$ and $k$.
-Indicated with blue lines are the values we calculated the data from.
-The dashed lines in the histograms along the diagonal represent the median and the 0.16 and 0.84 percentiles respectively.}
-	\label{fig:plotCorner4}
-\end{figure}
-
-A useful way to look at the samples of the posterior returned by the MCMC is to make a corner plot using a Python module named \textit{corner}.\cite{corner} The corner plot shows all the one- and two-dimensional projections of the posterior probability distributions and demonstrates quickly the covariances between parameters.
-Along the diagonal, the marginalized distribution for each parameter independently is shown.
-In Fig.~\ref{fig:plotCorner4} an excerpt of the full corner plot is shown.
-
-To arrive at a best value with uncertainty for the gravitational constant, we take the mean and standard deviation of the marginalized distribution of the parameter $k$ and divide by the total mass of the balls.
-In this example the relative uncertainty of $k$ is roughly $10^{-7}$, so if the masses are measured to about the same precision, we can write for the gravitational constant $G$:
-\begin{equation}\label{Gfit}
-G = \left(6.674005 \pm 0.000001 \right) \cdot 10^{-11}  \frac{\mathrm{m}^3}{\mathrm{kg \, s}^2}
-\end{equation}
-This corresponds to a relative uncertainty of $1.5 \cdot 10^{-7}$ or 15 parts in a hundred million.
-
-\section{Conclusion}
-We have outlined an orbit experiment to measure the gravitational
-constant $G$, and estimated the level of various disturbing effects
-and how to correct for them.  Simulating the measurement process and
-extraction of the gravitational constant indicates that $G$ could be
-estimated to about $10^{-7}$ relative uncertainty.  This is a about a
-factor of 300 better than today's recommended CODATA value.
-A further increase in precision could be obtained by running the experiment longer.
-Measuring for 200 instead of two orbits could increase the precision by a factor of 10.
-Hence, about the same relative uncertainty as for Planck's constant
-$h$ ($1.2 \cdot 10^{-8}$)\cite{CODATA16} could be achieved. This then
-would allow a future redefinition of the kilogram as an integer
-multiple of the Planck mass.
-
-We are not supposing the measurement of the gravitational constant 
-using an artificial two-body system at an Earth-Sun Lagrange point to be a stand alone mission. It could be part of 
-a spacecraft reaching a Lagrange point. But our estimates suggest that this approach to increase the precision of the gravitational constant should be taken seriously.
 

### 2018-03-03 ms.tex

@@
 SI, we refer the reader to the article on the ``LEGO watt
-balance''.\citep{Chao15} The proposed redefinition of the kilogram is
+balance'' \citep{Chao15}. The proposed redefinition of the kilogram is
 an explicit value for $h$ and $c$, but we can think of it as
@@
 definitions.  This could be done by introducing the gravitational
-constant, since $\sqrt{hc/G}$ has dimensions of mass.
-Historically, there have been several proposed unit systems that
-included $G$ in some way,\cite{Tomilin1999} but the idea of including
-both gravity and quantum mechanics in a unit system comes from
-Planck.\cite{Planck99} In the process of working towards the radiation
-law, Planck realized that $c,G,h$ and the Boltzmann constant $k_B$ (in
-his notation $G\rightarrow f$, $h\rightarrow b$, $h/k_B\rightarrow a$)
-naturally define units for mass, length, time, and temperature.
-Indeed, Planck remarked that such units would be meaningful even in
-non-human and extraterrestrial cultures.
+constant, since $\sqrt{hc/G}$ has dimensions of mass.  Historically,
+there have been several proposed unit systems that included $G$ in
+some way \citep[for a review, see][]{Tomilin1999}, but the idea of
+including both gravity and quantum mechanics in a unit system comes
+from \cite{Planck99}. In the process of working towards the
+radiation law, Planck realized that $c,G,h$ and the Boltzmann constant
+$k_B$ (in his notation $G\rightarrow f$, $h\rightarrow b$,
+$h/k_B\rightarrow a$) naturally define units for mass, length, time,
+and temperature.  Indeed, Planck remarked that such units would be
+meaningful even in non-human and extraterrestrial cultures.
 
@@
 The difficulty with Eq.~\eqref{eq:defs} is that all the expressions
-involve $G$.  Given the current uncertainties in $G$,\cite{CODATA17}
+involve $G$.  Given the current uncertainties in $G$ \citep{CODATA17},
 Eq.~\eqref{eq:defs} would allow units to be standardized only to four
@@
 The large disagreement is recognised immediately.
-The green lines represent the current recommended CODATA value and its uncertainty.\cite{CODATA17}}
+The green lines represent the current recommended CODATA value and its uncertainty \citep{CODATA17}.}
 	\label{fig:Gmeasurements}
@@
 measurements of the gravitational constant. Three of them
-(BIPM-14,\cite{Quinn14} UCI-14,\cite{Newman14} and
-HUST-09\cite{Luo09}) were carried out using a torsion balance, whereas
-UZur-06\cite{Schlamminger06} used a beam balance, and
-JILA-10\cite{Parks10} measured the separation of two simple pendulums
+(BIPM-14 \citep{Quinn14}, UCI-14 \citep{Newman14}, and
+HUST-09 \citep{Luo09}) were carried out using a torsion balance, whereas
+UZur-06 \citep{Schlamminger06} used a beam balance, and
+JILA-10 \citep{Parks10} measured the separation of two simple pendulums
 in a gravitational field. They all tried to measure the very weak
 gravitational force with a mechanical apparatus. The sixth measurement
-(LENS-14\cite{Rosi14}) was performed with another approach, using cold
+\citep[LENS-14][]{Rosi14} was performed with another approach, using cold
 atom interferometry. Its uncertainty is a lot larger than the others,
@@
 the Sun, because they depend on both the mass and $G$ times the mass
-of the Sun,\cite{Ch-Dalsgaard05} but this strategy does not yet give
+of the Sun \citep{Ch-Dalsgaard05}, but this strategy does not yet give
 competitive accuracy in $G$.
@@
 would be a laser interferometry system, which can yield precisions
-down to some nanometers.\cite{Loughridge13}
+down to some nanometers \citep{Loughridge13}.
 
@@
 PyCoffee\footnote{\url{<http://eso-python.github.io/ESOPythonTutorials/ESOPythonDemoDay8_MCMC_with_emcee.html>}}
-or an introduction paper from van
-Ravenzwaaij et al.\cite{vanRavenzwaaij16}
+or an introduction paper from \cite{vanRavenzwaaij16}.
 
@@
 
-A useful way to look at the samples of the posterior returned by the MCMC is to make a corner plot using a Python module named \textit{corner}.\cite{corner} The corner plot shows all the one- and two-dimensional projections of the posterior probability distributions and demonstrates quickly the covariances between parameters.
+A useful way to look at the samples of the posterior returned by the MCMC is to make a corner plot using a Python module named \textit{corner} \citep{corner}.
+The corner plot shows all the one- and two-dimensional projections of the posterior probability distributions and demonstrates quickly the covariances between parameters.
 Along the diagonal, the marginalized distribution for each parameter independently is shown.
@@
 Hence, about the same relative uncertainty as for Planck's constant
-$h$ ($1.2 \cdot 10^{-8}$)\cite{CODATA17} could be achieved. This then
+$h$ \citep[$1.2 \cdot 10^{-8}$][]{CODATA17} could be achieved. This then
 would allow a future redefinition of the kilogram as an integer
@@
 \end{document}
-
-bbibitem{BIPM16} International Bureau of Weights and Measures, ``DRAFT 9th edition of the SI Brochure", BIPM, (2016)
-
-bbibitem{Chao15} L.
-S.
-Chao, S.
-Schlamminger, D.
-B.
-Newell, J.
-R.
-Pratt, F.
-Seifert, X.
-Zhang, G.
-Sineriz, M.
-Liu and D.
-Haddad, ``A LEGO Watt balance: An apparatus to determine a mass based on the new SI", \textit{American Journal of Physics}, 83:11:913--922 (2015).
-% 2015AmJPh..83..913C
-
-bbibitem{Tomilin1999} D. K. Tomilin, ``Natural Systems of Units. To the Centenary Anniversary of the Planck System,'' 
-Proceedings of the XXII Workshop on high Energy Physics and field theory, 290 (1999).
-
-bbibitem{Planck99} M. Planck, ``\"{U}ber irreversible {S}trahlungsvorg\"{a}nge,'' 
-Sitzungsberichte der K\"{o}niglich Preussischen Akademie der Wissenschaften zu Berlin, 479--480 (1899).
-
-bbibitem{BIPM} Bureau International des Poids et Mesures, Calibration and measurement services: Mass, \url{<https://www.bipm.org/utils/common/pdf/cms_m.pdf>}, (2015).
-
-bbibitem{CODATA16} P. J. Mohr, D. B. Newell and B. N. Taylor, ``CODATA recommended values of the fundamental physical constants: 2014*, \textit{Reviews of Modern Physics}, 88(3):035009 (2016).
-
-bbibitem{Quinn14} T.
-Quinn, C.
-Speake, H.
-Parks and R.
-Davis, ``The BIPM measurements of the Newtonian constant of gravitation $G$'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (2014).
-
-bbibitem{Newman14} R.
-Newman, M.
-Bantel, E.
-Berg and W.
-Cross, ``A measurement of $G$ with a cryogenic torsion pendulum'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (2014).
-
-bbibitem{Luo09} J.
-Luo, W.
-Liu, L.
-Tu, C.
-Shao, L.
-Liu, S.
-Yang, Q.
-Li and Y.
-Zhang, ``Determination of the Newtonian gravitational constant $G$ with time-of-swing method'', \textit{Phys.
-Rev.
-Lett.}, 102:240801 (2009).
-
-bbibitem{Schlamminger06} S.
-Schlamminger, E.
-Holzschuh, W.
-Kündig, F.
-Nolting, R.
-E.
-Pixley, J.
-Schnurr and U.
-Straumann, ``Measurement of Newton's gravitational constant", \textit{Phys.
-Rev.
-D}, 74:082001 (2009).
-
-bbibitem{Parks10} H. V. Parks and J. E. Faller, ``Simple pendulum determination of the gravitational constant", \textit{Phys. Rev. Lett.}, 105:110801 (2010).
-
-bbibitem{Rosi14} G.
-Rosi, F.
-Sorrentino, L.
-Cacciapuoti, M.
-Prevedelli and G.
-M.
-Tino, ``Precision measurement of the Newtonian gravitational constant using cold atoms", \textit{Nature}, 510:518--521 (2014).
-
-bbibitem{Ch-Dalsgaard05} J. Christensen-Dalsgaard, M.~P. Di Mauro,
-  H. Schlattl and A. Weiss, ``On helioseismic tests of basic
-  physics'', \textit{MNRAS}, 356:587--595 (2005).
-
-bbibitem{Loughridge13} R. Loughridge and D. Y. Abramovitch, ``A tutorial on laser interferometry for precision measurements,'' 
-American Control Conference, 3686--3703 (2013).
-
-bbibitem{esopycoffee} Fast and easy-to-implement Markov Chain Monte Carlo with the emcee package, ESO PyCoffee (2014),
-\url{<http://eso-python.github.io/ESOPythonTutorials/ESOPythonDemoDay8_MCMC_with_emcee.html>}.
-
-bbibitem{vanRavenzwaaij16} D. van Ravenzwaji, P. Cassey and S. D. Brown, ``A simple introduction to Markov Chain Monte-Carlo sampling,'' 
-Psychonomic Bulletin {\&} Review, 1--12 (2016).
-
-bbibitem{corner} D. Foreman-Mackey, ``corner.py: Scatterplot matrices in Python,'' 
-The Journal of Open Source Software (10), (2016).

### 2018-04-03 msrsos.tex
RSOS format

--- 2018-03-03 ms.tex
@@
-%\documentclass[referee]{aa} % for a referee version
-\documentclass[onecolumn]{aa} % for a paper on 1 column  
-%\documentclass[longauth]{aa} % for the long lists of affiliations 
-%\documentclass[letter]{aa} % for the letters 
-%\documentclass[bibyear]{aa} % if the references are not structured 
-%                              according to the author-year natbib style
-%\documentclass{aa}
+\documentclass[]{rsos}
 
@@
 
-\title{Towards a Planckian standard kilogram}
-\subtitle{}
+%%%% Article title to be placed here
+\title{Towards a Planckian standard kilogram:
+a scenario for measuring $G$ using an artificial two-body orbit}
 
-\author{Michael Ebersold\thanks{michael.ebersold@uzh.ch}%\inst{1}
-        \and
-        Prasenjit Saha%\inst{2}\fnmsep
-       }
+\author{Michael Ebersold and Prasenjit Saha}
 
-\institute{Physik-Institut, University of Zurich, Winterthurerstrasse
+\address{Physik-Institut, University of Zurich, Winterthurerstrasse
   190, 8057 Zurich, Switzerland}
 
-\date{}
+\subject{xxxxx, xxxxx, xxxx}
 
-\abstract
-% context heading (optional)
-% {} leave it empty if necessary  
+\keywords{xxxx, xxxx, xxxx}
+
+\corres{Michael Ebersold\\
+\email{michael.ebersold@uzh.ch}}
+
+\begin{abstract}
 {As the kilogram assumes its new definition in terms of $h,c,$ and the
   standard second, it is interesting to think about a possible future
-  definition entirely in terms of fundamental constants.  A kilogram
-  defined as an integer multiple of the Planck mass (or
-  4594xxxx$\times\sqrt{\hbar c/G}$) would cause no significant change
-  from its current value.}
-% aims heading (mandatory)
-{The practical hurdle to this Planckian kilogram is measuring $G$
-  three or four orders of magnitude better than currently known, so as
-  to find the unknown digits xxxx.  We study a possible scenario for
-  doing so with an artificial two-body orbit.}
-% methods heading (mandatory)
+  definition entirely in terms of fundamental constants.
+  A kilogram could, in principle, be defined as an integer multiple of
+  the Planck mass (or 4594????$\times\sqrt{\hbar c/G}$) without
+  significantly altering its current value.  The practical hurdle is
+  measuring $G$ four orders of magnitude better than currently known,
+  in order to fix the four unknown digits.}
+{We assess the prospects for measuring $G$ to the desired accuracy
+  using an artificial two-body orbit.}
 {The cleanest (admittedly, not the cheapest) option is to place the
@@
   temperatures, to suppress radiation pressure.}
-% results heading (mandatory)
 {Data analysis would involve marginalizing over at least 15~nuisance
@@
   but that, we show, is feasible.}
-% conclusions heading (optional), leave it empty if necessary 
-{}
-
-\keywords{}
+{A more complicated system in Earth orbit should be taken seriously.}
+\end{abstract}
 
@@
 
-\bibliographystyle{aa}
+\def\nat{Nature}
+\def\prd{PRD}
+
+\bibliographystyle{RS}
 \bibliography{ms.bib}
@@
 \end{document}
+
+%%%%%%%%%% Insert the texts which can accomdate on firstpage in the tag "fmtext" %%%%%
+
+\begin{fmtext}
+
+\section{Insert A head here}
+%%%% Insert A head here
+
+This demo file is intended to serve as a ``starter file''
+for rsproca journal papers produced under \LaTeX\ using
+rsproca.cls v1.5e.
+
+\subsection{Insert B head here}
+%%%% Insert B head here
+Subsection text here.
+
+\subsubsection{Insert C head here}
+%%%% Insert C head here
+Subsubsection text here.
+
+\section{Equations}
+
+Sample equations. \cite{1}\cite{1,2} \cite{1,2,3}
+
+%%% Numbered equation
+\begin{align}\label{1.1}
+\begin{split}
+\frac{\partial u(t,x)}{\partial t} &= Au(t,x) \left(1-\frac{u(t,x)}{K}\right)-B\frac{u(t-\tau,x) w(t,x)}{1+Eu(t-\tau,x)},\\
+\frac{\partial w(t,x)}{\partial t} &=\delta \frac{\partial^2w(t,x)}{\partial x^2}-Cw(t,x)+D\frac{u(t-\tau,x)w(t,x)}{1+Eu(t-\tau,x)},
+\end{split}
+\end{align}
+
+\begin{align}\label{1.2}
+\begin{split}
+\frac{dU}{dt} &=\alpha U(t)(\gamma -U(t))-\frac{U(t-\tau)W(t)}{1+U(t-\tau)},\\
+\frac{dW}{dt} &=-W(t)+\beta\frac{U(t-\tau)W(t)}{1+U(t-\tau)}.
+\end{split}
+\end{align}
+
+%%%% Unnumbered equation
+\begin{eqnarray}
+\frac{\partial(F_1,F_2)}{\partial(c,\omega)}_{(c_0,\omega_0)} = \left|
+\begin{array}{ll}
+\frac{\partial F_1}{\partial c} &\frac{\partial F_1}{\partial \omega} \\\noalign{\vskip3pt}
+\frac{\partial F_2}{\partial c}&\frac{\partial F_2}{\partial \omega}
+\end{array}\right|_{(c_0,\omega_0)}\notag\\
+=-4c_0q\omega_0 -4c_0\omega_0p^2 =-4c_0\omega_0(q+p^2)>0.
+\end{eqnarray}
+\end{fmtext}
+
+%%%%%%%%%%%%%%% End of first page %%%%%%%%%%%%%%%%%%%%%
+
+\maketitle
+
+\section{Enunciations}
+
+\begin{theorem}\label{T0.1}
+Assume that $\alpha>0, \gamma>1, \beta>\frac{\gamma+1}{\gamma-1}$.
+Then there exists a small $\tau_1>0$, such that for $\tau\in
+[0,\tau_1)$, if $c$ crosses $c(\tau)$ from the direction of
+to  a small amplitude periodic traveling wave solution of
+(2.1), and the period of $(\check{u}^p(s),\check{w}^p(s))$ is
+\[
+\check{T}(c)=c\cdot \left[\frac{2\pi}{\omega(\tau)}+O(c-c(\tau))\right].
+\]
+\end{theorem}
+
+\begin{condition}\label{C2.2}
+From (0.8) and (2.10), it holds
+$\frac{d\omega}{d\tau}<0,\frac{dc}{d\tau}<0$ for $\tau\in
+[0,\tau_1)$. This fact yields that the system (2.1) with delay
+$\tau>0$ has the periodic traveling waves for smaller wave speed $c$
+than that the system (2.1) with $\tau=0$ does. That is, the
+delay perturbation stimulates an early occurrence of the traveling waves.
+\end{condition}
+
+\section{Figures \& Tables}
+
+The output for figure is:
+
+\begin{figure}[!h]
+%\centering\includegraphics[width=2.5in]{xxxxxx.eps}
+%%% where xxxxxx name represents "figurename.eps"
+\caption{Insert figure caption here}
+\label{fig_sim}
+\end{figure}
+
+\vspace*{-10pt}
+
+\noindent The output for table is:
+
+\begin{table}[!h]
+\caption{An Example of a Table}%%%Table caption goes here
+\label{table_example}
+\begin{tabular}{llll}%%%The number of columns has to be defined here
+\hline
+date &Dutch policy &date &European policy \\
+\hline
+1988 &Memorandum Prevention &1985 &European Directive (85/339) \\
+1991--1997 &{\bf Packaging Covenant I} & & \\
+1994 &Law Environmental Management &1994 &European Directive (94/62) \\
+1997 &Agreement Packaging and Packaging Waste & & \\
+1998--2002 &{\bf Packaging Covenant II} & & \\
+2003--2005 &{\bf Packaging Covenant III} & & \\
+2006--2007 &{\bf Decree on Packaging and paper} & & \\\hline
+\end{tabular}
+\end{table}%%%End of the table
+
+\section{Conclusion}
+The conclusion text goes here.
+
+\vskip1pc
+
+\ethics{Insert ethics text here.}
+
+\dataccess{Insert data accessibility text here. '(If no information, then please include the text ``This article has no additional data'').}
+
+\aucontribute{Insert author contributions text here (to be included if more than one author).}
+
+\competing{Insert competing interests text here.}
+
+\funding{Insert funding text here.}
+
+\ack{Insert acknowledgment text here.}
+
+\disclaimer{Insert disclaimer text here.}
+
+\pagebreak
+
+%%%%%%%%%% Insert bibliography here %%%%%%%%%%%%%%
+
+\noindent {\bf Please follow the coding for references as shown below.}
+
+\begin{thebibliography}{9}
+
+\bibitem{1} Allwood JM, Cullen JM. 2011 \textit{Sustainable materials:  with both eyes open}.
+Cambridge, UK: UIT Cambridge. See \href{http://www.withbotheyesopen.com}{http://www.withbotheyesopen.com}.
+
+\bibitem{2}  MacKay DJC. 2008  \textit{Sustainable energy:  without the hot air}.
+ Cambridge, UK: UIT Cambridge. See \href{http://www.withouthotair.com}{http://www.withouthotair.com}.
+
+\bibitem{3} Gallman PG. 2011  \textit{Green alternatives and national energy strategy: the facts
+ behind the headlines}.  Baltimore,\ MD: Johns Hopkins University Press.
+
+\bibitem{4} MacKay DJC. 2013.  Solar energy in the context of energy use, energy transportation, and
+ energy storage. \textit{Proc. R. Soc. A} \textbf{371}.
+
+\end{thebibliography}
+
+\vskip2pc
+
+\noindent If maintaining .bib file for references, then please use "RS.bst" to generate the references.
+
+\noindent Example:
+
+\verb+\bibliographystyle{RS}+ %%%% .BST file
+
+\verb+\bibliography{sample}+ %%%%% .Bib file
+
+\end{document}

### 2018-04-07 other-formats/aa/ms.tex
rsos format

--- 2018-03-03 ms.tex
@@
 \title{Towards a Planckian standard kilogram}
-\subtitle{}
+\subtitle{A scenario for measuring $G$ using an artificial two-body orbit}
 
@@
   standard second, it is interesting to think about a possible future
-  definition entirely in terms of fundamental constants.  A kilogram
-  defined as an integer multiple of the Planck mass (or
-  4594xxxx$\times\sqrt{\hbar c/G}$) would cause no significant change
-  from its current value.}
+  definition entirely in terms of fundamental constants.
+  A kilogram could, in principle, be defined as an integer multiple of
+  the Planck mass (or 4594????$\times\sqrt{\hbar c/G}$) without
+  significantly altering its current value.  The practical hurdle is
+  measuring $G$ four orders of magnitude better than currently known,
+  in order to fix the four unknown digits.}
 % aims heading (mandatory)
-{The practical hurdle to this Planckian kilogram is measuring $G$
-  three or four orders of magnitude better than currently known, so as
-  to find the unknown digits xxxx.  We study a possible scenario for
-  doing so with an artificial two-body orbit.}
+{We assess the prospects for measuring $G$ to the desired accuracy
+  using an artificial two-body orbit.}
 % methods heading (mandatory)
@@
 % conclusions heading (optional), leave it empty if necessary 
-{}
+{A more complicated system in Earth orbit should be taken seriously.}
 

### 2018-04-12 ms.tex
A&A format

@@
   standard second, it is interesting to think about a possible future
-  definition entirely in terms of fundamental constants.  A kilogram
-  defined as an integer multiple of the Planck mass (or
-  4594xxxx$\times\sqrt{\hbar c/G}$) would cause no significant change
-  from its current value.}
+  definition entirely in terms of fundamental constants.
+  A kilogram could, in principle, be defined as an integer multiple of
+  the Planck mass (or 4594????$\,\times\sqrt{\hbar c/G}$) without
+  significantly altering its current value.  The practical hurdle is
+  measuring $G$ four orders of magnitude better than currently known,
+  in order to fix the four unknown digits.}
 % aims heading (mandatory)
-{The practical hurdle to this Planckian kilogram is measuring $G$
-  three or four orders of magnitude better than currently known, so as
-  to find the unknown digits xxxx.  We study a possible scenario for
-  doing so with an artificial two-body orbit.}
+{We assess the prospects for measuring $G$ to the desired accuracy
+  using an artificial two-body orbit.}
 % methods heading (mandatory)
-{The cleanest (admittedly, not the cheapest) option is to place the
-  system on a Trojan orbit to minimize external gravitational
-  perturbations, and enclose it in a cavity chilled to liquid-helium
+{We consider the simplest configuration, which would be a system
+  placed on a Trojan orbit to minimize external gravitational
+  perturbations, and enclosed in a cavity chilled to liquid-helium
   temperatures, to suppress radiation pressure.}
@@
 % conclusions heading (optional), leave it empty if necessary 
-{}
+{We have not considered costs in this preliminary study, but more
+  complicated but more affordable scenarios in Earth orbit merit
+  investigation.}
 
@@
 
+\bigskip
+
+We thank Scott Tremaine for comments.
+
 \bibliographystyle{aa}

### 2018-04-12 other-formats/rsos/ms.tex
A&A format

--- 2018-03-03 ms.tex
@@
 
-\title{Towards a Planckian standard kilogram}
-\subtitle{}
+\title{Towards a Planckian standard kilogram:
+a scenario for measuring $G$ using an artificial two-body orbit}
 
-\author{Michael Ebersold\thanks{michael.ebersold@uzh.ch}%\inst{1}
-        \and
-        Prasenjit Saha%\inst{2}\fnmsep
-       }
+\author{Michael Ebersold and Prasenjit Saha}
 
-\institute{Physik-Institut, University of Zurich, Winterthurerstrasse
+\address{Physik-Institut, University of Zurich, Winterthurerstrasse
   190, 8057 Zurich, Switzerland}
 
-\date{}
+\subject{xxxxx, xxxxx, xxxx}
 
-\abstract
-% context heading (optional)
-% {} leave it empty if necessary  
-{As the kilogram assumes its new definition in terms of $h,c,$ and the
+\keywords{xxxx, xxxx, xxxx}
+
+\corres{Michael Ebersold\\
+\email{michael.ebersold@uzh.ch}}
+
+\begin{abstract}
+As the kilogram assumes its new definition in terms of $h,c,$ and the
 standard second, it is interesting to think about a possible future
 definition entirely in terms of fundamental constants.  A kilogram
-  defined as an integer multiple of the Planck mass (or
-  4594xxxx$\times\sqrt{\hbar c/G}$) would cause no significant change
-  from its current value.}
-% aims heading (mandatory)
-{The practical hurdle to this Planckian kilogram is measuring $G$
-  three or four orders of magnitude better than currently known, so as
-  to find the unknown digits xxxx.  We study a possible scenario for
-  doing so with an artificial two-body orbit.}
-% methods heading (mandatory)
-{The cleanest (admittedly, not the cheapest) option is to place the
-  system on a Trojan orbit to minimize external gravitational
-  perturbations, and enclose it in a cavity chilled to liquid-helium
-  temperatures, to suppress radiation pressure.}
-% results heading (mandatory)
-{Data analysis would involve marginalizing over at least 15~nuisance
-  parameters (6~for orbital parameters and 9~for fictitious forces)
-  but that, we show, is feasible.}
-% conclusions heading (optional), leave it empty if necessary 
-{}
-
-\keywords{}
+could, in principle, be defined as an integer multiple of the Planck
+mass (or 4594????$\,\times\sqrt{\hbar c/G}$) without significantly
+altering its current value.  The practical hurdle is measuring $G$
+four orders of magnitude better than currently known, in order to fix
+the four unknown digits.  We assess the prospects for measuring $G$ to
+the desired accuracy using an artificial two-body orbit.  The simplest
+configuration would be a system placed on a Trojan orbit to minimize
+external gravitational perturbations, and enclosed in a cavity chilled
+to liquid-helium temperatures to suppress radiation pressure.  Data
+analysis would involve marginalizing over at least 15~nuisance
+parameters (6~for orbital parameters and 9~for fictitious forces) but
+that, we show, is feasible.  We have not considered the likely cost of
+a Trojan space mission in this simple study, but a more complicated
+scenario in Earth orbit should be taken seriously.
+\end{abstract}
 
@@
 
-\bibliographystyle{aa}
+\ack{We thank Scott Tremaine for comments.}
+
+\def\nat{Nature}
+\def\prd{PRD}
+
+\bibliographystyle{RS}
 \bibliography{ms.bib}

### 2018-07-18 ms.tex
small edits

@@
   standard second, it is interesting to think about a possible future
-  definition entirely in terms of fundamental constants.
-  A kilogram could, in principle, be defined as an integer multiple of
-  the Planck mass (or 4594????$\,\times\sqrt{\hbar c/G}$) without
-  significantly altering its current value.  The practical hurdle is
-  measuring $G$ four orders of magnitude better than currently known,
-  in order to fix the four unknown digits.}
+  definition entirely in terms of fundamental constants.  A kilogram
+  could, in principle, be defined as an integer multiple of the Planck
+  mass (or 4594????$\,\times\sqrt{\hbar c/G}$) without changing it
+  currently realizable value.  The practical hurdle is measuring $G$
+  four orders of magnitude better than now known, in order to fix the
+  four unknown digits.}
 % aims heading (mandatory)
@@
 % conclusions heading (optional), leave it empty if necessary 
-{We have not considered costs in this preliminary study, but more
-  complicated but more affordable scenarios in Earth orbit merit
-  investigation.}
+{Artificial two-body orbits merit serious consideration as a method
+  for measuring $G$.  The configuration considered in this preliminary
+  study may be unrealistically expensive, but more complicated but
+  more affordable scenarios in Earth orbit may be practical.}
 
@@
 enable electrical units to be defined in terms of $h$ and $e$.  A
-further ingenious instrument, known as a watt balance, precisely
-compares electrical and mechanical power, thus enabled mass to be
-standardized in terms of $h$.  For a simple introduction to the new
-SI, we refer the reader to the article on the ``LEGO watt
-balance'' \citep{Chao15}. The proposed redefinition of the kilogram is
-an explicit value for $h$ and $c$, but we can think of it as
+further ingenious instrument, known as a Kibble balance or watt
+balance, precisely compares electrical and mechanical power, thus
+enabled mass to be standardized in terms of $h$.  For a simple
+introduction to the new SI, we refer the reader to the article on the
+``LEGO watt balance'' \citep{Chao15}. The proposed redefinition of the
+kilogram is as an explicit value for $h$ and $c$, but we can think of
+it as
 \begin{equation}
-\mathrm{kg} \equiv 1.3563925\ldots \times 10^{50} \, \mathrm{s}^{-1}
-                   \times \frac{h}{c^2}
+\mathrm{kg} \equiv 8.52246550 \times 10^{50} \, \mathrm{s}^{-1}
+                   \times c^{-2} \hbar .
 \end{equation}
-with the exact value to be decided.  As we can see, the kilogram is
-coupled to the definition of a second.  That is not a problem in
-practice, as the second is standardized orders of magnitude better
-than any other unit.  Nonetheless, it is interesting to consider a
-logical further step of decoupling the kilogram from other
-definitions.  This could be done by introducing the gravitational
-constant, since $\sqrt{hc/G}$ has dimensions of mass.  Historically,
-there have been several proposed unit systems that included $G$ in
-some way \citep[for a review, see][]{Tomilin1999}, but the idea of
-including both gravity and quantum mechanics in a unit system comes
-from \cite{Planck99}. In the process of working towards the
-radiation law, Planck realized that $c,G,h$ and the Boltzmann constant
-$k_B$ (in his notation $G\rightarrow f$, $h\rightarrow b$,
-$h/k_B\rightarrow a$) naturally define units for mass, length, time,
-and temperature.  Indeed, Planck remarked that such units would be
-meaningful even in non-human and extraterrestrial cultures.
+As we can see, the kilogram is coupled to the definition of a second.
+That is not a problem in practice, as the second is standardized
+orders of magnitude better than any other unit.  Nonetheless, it is
+interesting to consider a logical further step of decoupling the
+kilogram from other definitions.  This could be done by introducing
+the gravitational constant, since $\sqrt{hc/G}$ has dimensions of
+mass.  Historically, there have been several proposed unit systems
+that included $G$ in some way \citep[for a review,
+  see][]{Tomilin1999}, but the idea of including both gravity and
+quantum mechanics in a unit system comes from \cite{Planck99}. In the
+process of working towards the radiation law, Planck realized that
+$c,G,h$ and the Boltzmann constant $k_B$ (in his notation
+$G\rightarrow f$, $h\rightarrow b$, $h/k_B\rightarrow a$) naturally
+define units for mass, length, time, and temperature.  Indeed, Planck
+remarked that such units would be meaningful even in non-human and
+extraterrestrial cultures.
 
@@
 only part of some expression, as they are here.  The Planck mass is
-small but microscopically measurable: $\sim20\mu\mathrm{g}$.  This is
-of the same order as the uncertainty in the prototype kilogram
-itself.\footnote{\url{<https://www.bipm.org/utils/common/pdf/cms_m.pdf>}}
-Hence the kilogram could be redefined as an integer multiple of the
-Planck mass, without significantly perturbing its value.
+small but microscopically measurable: $\sim20\,\mu\mathrm{g}$.  This
+is of the same order as the uncertainty in the old prototype
+kilogram\footnote{\url{<https://www.bipm.org/utils/common/pdf/cms_m.pdf>}}
+and the uncertainty in watt-balance experiments.  Hence the kilogram
+could be redefined as an integer multiple of the Planck mass, without
+significantly perturbing its value.
 
@@
 \subsection{An artificial two-body gravitating system}
-Newton's law of gravitation does not only explain why an apple falls
-down from a tree, it also explains orbits. If one has two bodies of
-masses $m_1$ and $m_2$, on which the only force acting is their
-respective gravitational attraction, they will orbit around the common
-center of mass, with the relative vector tracing an ellipse
-described by Kepler's laws. The third law, relates the
-orbital period $P$ to semimajor axis $a$ of the ellipse, as
+Newton's law of gravitation explains not only why an apple falls down
+from a tree, but also orbits. If one has two bodies of masses $m_1$
+and $m_2$, on which the only force acting is their respective
+gravitational attraction, they will orbit around the common center of
+mass, with the relative vector tracing an ellipse described by
+Kepler's laws. The third law, relates the orbital period $P$ to
+semimajor axis $a$ of the ellipse, as
 \begin{equation}\label{eq:kepler3}
@@
 Such a low temperature results in a force on the balls in the order of $10^{-16}$~N.
-Compared to the gravitational force, this is orders of magnitude less and thus we don't have to worry about effects of radiation pressure.
+This is $\sim10^{-9}$ of the gravitational force, and thus we don't have to further model the effects of radiation pressure.
 
@@
 \label{sec:tidal}
-The free fall condition is not possible to achieve for both masses simultaneously since we are in a non-inertial, rotating frame and therefore have to account for centrifugal forces.
+The free-fall condition is not possible to achieve for both masses simultaneously since we are in a non-inertial, rotating frame and therefore have to account for centrifugal forces.
 The centrifugal acceleration $\ddot{\vec{r}}_{\mathrm{Z}}$ is proportional to the distance vector $\vec{r}$ and scales with $\omega^2$, where $\omega$ is the angular velocity of the Sun-Earth reference frame:
@@
 It should also be possible to calculate the gravitational field caused by the components of the spacecraft at the positions of the balls.
-Then one can correct the equation of motion by adding an extra term that is accounting for the gravitational field.
-\\
-A source of an additional gravitational field is Earth's moon and the other planets in the solar system.
+Then one can correct the equation of motion by adding an extra term accounting for the gravitational field.
+
+A source of an additional gravitational field is the Earth's moon and the other planets in the solar system.
 Fortunately, for this we don't need to correct if the whole system, consisting of the spacecraft and the two-body system, is moving through space together.
-Although, the spacecraft should be able to correct its position around the two balls to avoid a collision.
+However, the spacecraft should be able to correct its position around the two balls to avoid a collision.
 
@@
 
-These are actually three coupled equations of motion, one for each spatial coordinate.
-Since all are second order differential equations, we need to give six initial conditions to determine the orbit.\\
-We choose our coordinate system such that the orbital plane of the two-body system is in the $x-y$ plane.
-$\vec{\omega}$ is a constant vector that points in the direction of the rotation axis of the Earth-Sun reference frame.
-We will fit for $\vec{\omega}$, so we don't have to know it exactly before, but it can be estimated well and thus provides good starting points for the fit.
-The same is valid for the six components of the matrix $C$.
+These are actually three coupled equations of motion, one for each spatial coordinate. Since all are second order differential equations, we need to give six initial conditions to determine the orbit.
+
 We choose our coordinate system such that the orbital plane of the two-body system is in the $x-y$ plane.
@@
 In the next step, we set the parameters to a fixed ``true" value
-within the range estimated. We have to keep in mind that $k$, $x_0$
-and $v_{y_0}$ are linked together and there must not be contradictions
-in the true values. The chosen values are displayed in the right
+within the range estimated. We have to keep in mind that for given $k$
+and $x_0$, $v_{y_0}$ must be chosen to as to produce a nearly-circular
+orbit, as desired.  The chosen values are displayed in the right-hand
 column of Table~\ref{tab:parameters}.  To simulate data we would
@@
 using Kepler's third law (\ref{eq:kepler3}). For the value of $k$
-assumed above and a semi-major axis of $0.15$~m, this
-results in an orbital period of roughly 12900 seconds or
-3.5 hours. Here we integrate two orbits in 100000
-steps, that would correspond to about 4 measurements per second,
-which should be feasible. To the generated data, we add Gaussian noise
-with a standard deviation of 10~nm. The value we use is just an estimate,
-it would depend strongly on the measurement system that has been used.
+assumed above and a semi-major axis of $0.15$~m, this results in an
+orbital period of roughly 12900 seconds or 3.5 hours. Here we
+integrate two orbits in 100000 steps, that would correspond to about 4
+measurements per second, which should be feasible. To the generated
+data, we add Gaussian noise with a standard deviation of 10~nm. The
+value we use is just an estimate, it would depend strongly on the
+measurement system that has been used.
 
@@
 estimated to about $10^{-7}$ relative uncertainty.  This is about a
-factor of 300 better than today's recommended CODATA value.
-A further increase in precision could be obtained by running the experiment longer.
-Measuring for 200 instead of two orbits could increase the precision by a factor of 10.
-Hence, about the same relative uncertainty as for Planck's constant
-$h$ \citep[$1.2 \cdot 10^{-8}$][]{CODATA17} could be achieved. This then
-would allow a future redefinition of the kilogram as an integer
-multiple of the Planck mass.
+factor of 300 better than today's recommended CODATA value. A further
+increase in precision could be obtained by running the experiment
+longer. Measuring for 200 instead of two orbits could increase the
+precision by a factor of 10.  Hence, about the same relative
+uncertainty as for Planck's constant $h$ \citep[$1.2 \cdot 10^{-8}$,
+  see][]{CODATA17} could be achieved. This then would allow a future
+redefinition of the kilogram as an integer multiple of the Planck
+mass.
 

### 2020-04-07 spg/main.tex
SPG article

\documentclass[aps,prb,12pt]{revtex4-1}

\def\unit#1{\;{\rm#1}}

\begin{document}

\title{Planck and the Extra-terrestrials\\
       or what the new SI means for astronomy}

\author{Prasenjit Saha} \email{psaha@physik.uzh.ch}
\affiliation{Physik-Institut, University of Zurich\\
  Winterthurerstr.~190, 8057~Zurich, Switzerland}

\begin{abstract}
New freedom.
\end{abstract}

\maketitle

In 1899 Planck \cite{Planck1899}.
Let $m=\sqrt{hc/G}$.
$f \rightarrow G$, $b\rightarrow h$, $a\rightarrow h/k$
Comes to $55\rm\,\mu g$.

Not the first \cite{Tomilin1999} but most prescient.  SI
\cite{Jeckelmann_2018}.  Leaves out $G$.  Also candela, sievert.

Astros use Planckian units occasionally (with $\hbar$) but generally
not.  Stories of cross-sections in gallons/Mpc.\footnote{A gallon/Mpc
  is about a kilogram, but the exact value depends on which gallon.}
Why?

Solar mass in kg would be bad.  SI in astro has been a non-starter.
But spacecraft dynamics uses $GM$ in SI.

New SI new freedoms.  eV not a new unit.  Density as
$\!\unit{eV}\unit{m}^{-3}$ is fine.  Anarchy?  No, because conversions
only through physical constants.

For astros, don't need to express solar mass in kg.  But we'll get to
that.

First Light-second: au and pc.  Again, not a new unit.  Round like Pfund.

Optical magnitude.  Photon flux on logarithmic wavelength scale.
Rounds nicely.  eNot to be confused with seismological magnitudes.

Gravity-second $GM/c^3$
(pulsars).
Strange formulations.
Dimensionless velocity ok.  But density $\rho$ as $s^{-2}$ seems
strange.  But $(G\rho)^{-1/2}$ is a time scale.  And gravity-second
per second is a power.  Basically, avoid explicit $G$ in pure
gravitational phenomena.  Explicit $G$ only when gravity and non-grav
processes both appear.

In the 120 years since Planck speculated about it, we have yet to make
contact with non-human or extra-terrestrial cultures, and ask them if
they indeed share Planck's views on units.  What {\em has} happened,
however, is that physical constants have turned out to have meanings
not even Planck in 1899 had imagined.  As we all know, the following
year Planck himself discovered that $h$ (formerly known as $b$) was
about quantization.  A few years later the formal relation between
mass and energy through $c^2$ turned out to be real.  Starting in the
1920s $(\hbox{Planck mass})^{-2}\times(\hbox{proton mass})^3$ was
discovered to be the mass scale of stars.  Later in the 20th century,
$2e/h$ and $h/e^2$ turned out to be macroscopically observable as
Josephson's constant and von~Klitzing's constant.  And just in the
last few years, $c^5/G$ has been observed to be the power-output scale
for merging black holes.  We can only wonder what more surprises await
us.

\def\aj{AJ}
\def\apjl{ApJL}
\def\aap{A\&A}
\def\mnras{MNRAS}
\def\pasj{PASJ}
\def\jgr{JGR}

\bibliographystyle{apsrev4-1}
\bibliography{refs.bib}

\end{document}

### 2020-04-07 spg/constants.py

@@ -1,0 +1,18 @@
+import numpy as np
+
+pi = np.pi
+
+c = 299792458
+h = 6.626070040e-34
+k = 1.38064852e-23
+e = 1.6021766208e-19
+
+me = 1.2355899e20
+mp = 2.2687318e23
+alpha = 0.00729735256
+
+au = 149597870700
+parsec = 180/pi*3600*au
+yr = 365.25*86400
+G = 6.674e-11
+

### 2020-04-08 spg/main.tex
editing

@@
 
-Optical magnitude.  Photon flux on logarithmic wavelength scale.
-Rounds nicely.  eNot to be confused with seismological magnitudes.
+In the astronomy literature one finds many named units (\AA ngström,
+gauss, jansky) that are simply powers of 10 times SI units, which need
+not detain us here.  There are also parody units such as
+$\!\unit{gallon}\unit{Mpc}^{-1}$ for cross-sections (it depends on the
+type of gallon, but is about a kilobarn), which would need an article
+to themselves.  The only remaining unit that needs discussing is the
+optical magnitude scale.  Optical magnitudes are a measure of
+brightness going back to classical times, but like other units they
+have been progressively redefined, and are now considered
+SI-traceable.  A zero-magnitude source (such as the star Vega)
+corresponds to a flux of roughly $10^{10}$ photons
+$\!\unit{m}^{-2}\unit{s}$ in a typical spectral band.  More precisely,
+zero magnitude is $5.480 \times10^{10}$ photons
+$\!\unit{m}^{-2}\unit{s}$ per logarithmic spectral interval, with each
+5~mag being 100 times fainter.  Since modern optical cameras are
+invariably counters of photons, it makes sense to simply use photon
+fluxes rather than optical magnitudes, with ``rounded'' magnitudes
+used for historical comprehension.
 
-Gravity-second $GM/c^3$
-(pulsars).
-Strange formulations.
+Gravity-second $GM/c^3$ (pulsars).  Strange formulations.
 Dimensionless velocity ok.  But density $\rho$ as $s^{-2}$ seems

### 2020-04-08 spg/main.tex
editing

@@
 \author{Prasenjit Saha} \email{psaha@physik.uzh.ch}
-\affiliation{Physik-Institut, University of Zurich\\
+\affiliation{Physik-Institut, University of Zurich,
   Winterthurerstr.~190, 8057~Zurich, Switzerland}
@@
 
-In 1899 Planck \cite{Planck1899}.
-Let $m=\sqrt{hc/G}$.
-$f \rightarrow G$, $b\rightarrow h$, $a\rightarrow h/k$
-Comes to $55\rm\,\mu g$.
+In 1899, during his struggle to understand blackbody radiation but
+about a year before he found the key, Planck proposed a curious set of
+units.\cite{Planck1899} In these natural units, as he called them, the
+unit of mass $m=\sqrt{hc/G}$ which comes to about $55\rm\,\mu g$.  The
+length unit is $h/(mc)$, the time unit is $h/(mc^2)$, while the
+temperature unit is $mc^2/k$.  (Reading the original today, one needs
+to substitute $f \rightarrow G$, $b\rightarrow h$, $a\rightarrow
+h/k$.)  Planck then declared that these units would be recognized by
+all cultures as fundamental, even extraterrestrial or non-human ones
+(ausserirdische und aussermenschliche Culturen).
 
-Not the first \cite{Tomilin1999} but most prescient.  SI
+Planck was by no means the only person to try
+
+Not the first \cite{Tomilin1998} but most prescient.  SI
 \cite{Jeckelmann_2018}.  Leaves out $G$.  Also candela, sievert.
 
-Astros use Planckian units occasionally (with $\hbar$) but generally
-not.  Stories of cross-sections in gallons/Mpc.\footnote{A gallon/Mpc
-  is about a kilogram, but the exact value depends on which gallon.}
-Why?
+Astros use Planckian units occasionally\cite{magicenv} (with $\hbar$)
+but generally not.\cite{dodd2011}  Why?
 
@@
 
-For astros, don't need to express solar mass in kg.  But we'll get to
-that.
-
-First Light-second: au and pc.  Again, not a new unit.  Round like Pfund.
+For astronomy, the good news is that the SI no longer requires you to
+express the solar mass in kg --- but we'll get to that.  We remark
+first that distances in light-seconds are compliant with the new SI.
+Like the electronvolt, a light-second is not itself a unit, it is an
+abbreviated way of referring to the equivalent light travel time.  On
+the other hand, which astronomer would wish to lose the cultural
+legacies of the astronomical unit of length (au), and the parsec?
+Fortunately, metrology and cultural legacies can be reconciled.  To
+see how, we only to see how modern German has kept the old unit of a
+Pfund, but has rounded its meaning to exactly $500\unit{g}$.  The au
+and parsec have serendipitously round values: $1\unit{au}\simeq
+c\times500\unit{s}$ to better than 1\%, while a parsec is just 3\%
+over $c\times10^8\unit{s}$.
 
@@
 
-Gravity-second $GM/c^3$ (pulsars).  Strange formulations.
-Dimensionless velocity ok.  But density $\rho$ as $s^{-2}$ seems
-strange.  But $(G\rho)^{-1/2}$ is a time scale.  And gravity-second
-per second is a power.  Basically, avoid explicit $G$ in pure
-gravitational phenomena.  Explicit $G$ only when gravity and non-grav
-processes both appear.
+Now we come to the kilogram, or avoiding the kilogram when necessary.
+Spacecraft dynamics has long used the so-called solar mass parameter
+$GM_\odot$ in $\!\unit{m}^3\unit{s}^{-2}$, which is known to eight
+significant digits in Newtonian gravity, two more with general
+relativity.  In pulsar timing, $GM_\odot/c^3$ in seconds is usual.  In
+the new SI, by analogy with electronvolts, we can meaningfully measure
+mass as $GM/c^3$ in ``gravity-seconds''.  The solar mass is about
+5~micro-(gravity)-seconds.  This does not mean that kilograms are to
+be avoided in astrophysics.  Rather, gravity-seconds can be useful
+where kilograms would needlessly propagate the uncertainty in $G$,
+which is typically the case for orbital processes.  Together with
+distances in light-seconds and dimensionless velocities,
+gravity-seconds allow for some elegant simplifications in the
+description of all kinds of orbital processes, classical and
+relativistic.\cite{2020PASP..132b1001S} Some constructions arise, that
+seem {\em very} strange at first: in particular density in
+gravity-seconds per cubic light-seconds, or power in gravity-seconds
+per second.  But these are not really unphysical at all.  In
+gravitational phenomena, a density $\rho$ is always associated with a
+time scale $(G\rho)^{-1/2}$, so density as frequency squared does make
+sense.  As for dimensionless power in gravity-seconds per second, this
+is just power in units of the well-known Planck power $c^5/G$, which
+is the luminosity scale in gravitational waves for merging black
+holes, irrespective of their mass.
 
@@
 \def\mnras{MNRAS}
-\def\pasj{PASJ}
-\def\jgr{JGR}
+\def\pasp{PASP}
 

### 2020-04-08 spg/main.tex
first draft for SPG

@@
 
-\begin{abstract}
-New freedom.
-\end{abstract}
+%\begin{abstract}
+%\end{abstract}
 
@@
 
-Planck was by no means the only person to try
+Planck was not the only one to propose a system of units based on
+fundamental constants,\cite{Tomilin1998} but he was the most
+prescient.  In Planck's system there is no prototype mass, length,
+time, or temperature.  Instead there are dimensional coefficients that
+appear in multiple equations of physics, and units are defined
+implicitly.  In the 21st century the International System of units
+concluded implicit definition of units is not a bug, it's a feature.
+In 2018 the SI decided that only the second shall be defined by a
+particular physical process (a spectral line in Cs).  All other units
+are defined implicitly, through defined values of physical constants,
+including (but of course) Planck's constant.  Any applicable equation
+of physics can be used for the realization of
+units.\cite{Jeckelmann_2018}
 
-Not the first \cite{Tomilin1998} but most prescient.  SI
-\cite{Jeckelmann_2018}.  Leaves out $G$.  Also candela, sievert.
+The reforms in the SI were not especially designed to communicate with
+extraterrestrials.  The decision to adopt implicit definitions was
+pragmatic, in that explicit definitions were sometimes overtaken by
+technology.  In particular, the kilogram is best realized as a derived
+electrical unit, with mass measured by way of the quantum Hall effect
+and the Josephson effect.  That would be sternly frowned upon by the
+old SI, but the new SI is cheerfully agnostic.  The new SI also
+removes conflicts with some common scientific usages.  For example,
+the electronvolt is not an SI unit.  However, if we understand mass in
+electronvolts as a shorthand for the value of mass times $c^2/e$ in
+volts, there is no conflict with the new SI.
 
-Astros use Planckian units occasionally\cite{magicenv} (with $\hbar$)
-but generally not.\cite{dodd2011}  Why?
+Planckian units can be useful useful for theoretical work, provided
+one changes to standard units for comparing with observable
+quantities.\cite{magicenv} Meanwhile, the community of scientists
+engaged with extraterrestrial things have steadfastly resisted
+adopting SI units.  Even the proponents of SI units among astronomers
+\cite{dodd2011} have not advocated a complete change to the SI.  Why
+is that?  The answer may lie to some extent in sociological factors,
+but there has been a scientific reason.  The key is the constant that
+Planck included but the new SI does not: $G$.  The gravitational
+constant is uniquely weak and uniquely hard to measure, and even now
+is known to only four significant digits.\cite{2018Natur.560..562S}
+The so-called solar mass parameter $GM_\odot$ is known to eight
+significant digits in Newtonian gravity, two more with general
+relativity.  But if you split that product into $G$ and $M_\odot$, in
+order to write the mass of the Sun in kilograms, your value of the
+gravitational field will be only good to four significant digits.  You
+cannot navigate a spacecraft on four significant digits.  End of story
+for SI in astronomy.  Or so it used to be.
 
-Solar mass in kg would be bad.  SI in astro has been a non-starter.
-But spacecraft dynamics uses $GM$ in SI.
-
-New SI new freedoms.  eV not a new unit.  Density as
-$\!\unit{eV}\unit{m}^{-3}$ is fine.  Anarchy?  No, because conversions
-only through physical constants.
-
-For astronomy, the good news is that the SI no longer requires you to
-express the solar mass in kg --- but we'll get to that.  We remark
-first that distances in light-seconds are compliant with the new SI.
-Like the electronvolt, a light-second is not itself a unit, it is an
-abbreviated way of referring to the equivalent light travel time.  On
-the other hand, which astronomer would wish to lose the cultural
-legacies of the astronomical unit of length (au), and the parsec?
-Fortunately, metrology and cultural legacies can be reconciled.  To
-see how, we only to see how modern German has kept the old unit of a
-Pfund, but has rounded its meaning to exactly $500\unit{g}$.  The au
-and parsec have serendipitously round values: $1\unit{au}\simeq
+But post 2018 the SI no longer requires you to express the solar mass
+in kg --- but we'll get to that.  We remark first that distances in
+light-seconds are compliant with the new SI.  Like the electronvolt, a
+light-second is not itself a unit, it is an abbreviated way of
+referring to the equivalent light travel time.  On the other hand,
+which astronomer would wish to lose the cultural legacies of the
+astronomical unit of length (au), and the parsec?  Fortunately,
+metrology and cultural legacies can be reconciled.  To see how, we
+only to see how modern German has kept the old unit of a Pfund, but
+has rounded its meaning to exactly $500\unit{g}$.  The au and parsec
+have serendipitously round values: $1\unit{au}\simeq
 c\times500\unit{s}$ to better than 1\%, while a parsec is just 3\%
@@
 Now we come to the kilogram, or avoiding the kilogram when necessary.
-Spacecraft dynamics has long used the so-called solar mass parameter
-$GM_\odot$ in $\!\unit{m}^3\unit{s}^{-2}$, which is known to eight
-significant digits in Newtonian gravity, two more with general
-relativity.  In pulsar timing, $GM_\odot/c^3$ in seconds is usual.  In
-the new SI, by analogy with electronvolts, we can meaningfully measure
-mass as $GM/c^3$ in ``gravity-seconds''.  The solar mass is about
-5~micro-(gravity)-seconds.  This does not mean that kilograms are to
-be avoided in astrophysics.  Rather, gravity-seconds can be useful
-where kilograms would needlessly propagate the uncertainty in $G$,
-which is typically the case for orbital processes.  Together with
-distances in light-seconds and dimensionless velocities,
-gravity-seconds allow for some elegant simplifications in the
-description of all kinds of orbital processes, classical and
-relativistic.\cite{2020PASP..132b1001S} Some constructions arise, that
-seem {\em very} strange at first: in particular density in
-gravity-seconds per cubic light-seconds, or power in gravity-seconds
-per second.  But these are not really unphysical at all.  In
-gravitational phenomena, a density $\rho$ is always associated with a
-time scale $(G\rho)^{-1/2}$, so density as frequency squared does make
-sense.  As for dimensionless power in gravity-seconds per second, this
-is just power in units of the well-known Planck power $c^5/G$, which
-is the luminosity scale in gravitational waves for merging black
-holes, irrespective of their mass.
+Spacecraft dynamics has long used $GM_\odot$ in
+$\!\unit{m}^3\unit{s}^{-2}$.  In pulsar timing, $GM_\odot/c^3$ in
+seconds is usual.  In the new SI, by analogy with electronvolts, we
+can meaningfully measure mass as $GM/c^3$ in ``gravity-seconds''.  The
+solar mass is about 5~micro-(gravity)-seconds.  This does not mean
+that kilograms are to be avoided in astrophysics.  Rather,
+gravity-seconds can be useful where kilograms would needlessly
+propagate the uncertainty in $G$, which is typically the case for
+orbital processes.  Together with distances in light-seconds and
+dimensionless velocities, gravity-seconds allow for some elegant
+simplifications in the description of all kinds of orbital processes,
+classical and relativistic.\cite{2020PASP..132b1001S} Some
+constructions arise, that seem {\em very} strange at first: in
+particular density in gravity-seconds per cubic light-seconds, or
+power in gravity-seconds per second.  But these are not really
+unphysical at all.  In gravitational phenomena, a density $\rho$ is
+always associated with a time scale $(G\rho)^{-1/2}$, so density as
+frequency squared does make sense.  As for dimensionless power in
+gravity-seconds per second, this is just power in units of the
+well-known Planck power $c^5/G$, which is the luminosity scale in
+gravitational waves for merging black holes, irrespective of their
+mass.
 

### 2020-04-08 spg/main.tex
edits

@@
 units.\cite{Planck1899} In these natural units, as he called them, the
-unit of mass $m=\sqrt{hc/G}$ which comes to about $55\rm\,\mu g$.  The
-length unit is $h/(mc)$, the time unit is $h/(mc^2)$, while the
+unit of mass $m$ is $\sqrt{hc/G}$ which comes to about $55\rm\,\mu g$.
+The length unit is $h/(mc)$, the time unit is $h/(mc^2)$, while the
 temperature unit is $mc^2/k$.  (Reading the original today, one needs
@@
 time, or temperature.  Instead there are dimensional coefficients that
-appear in multiple equations of physics, and units are defined
+appear in multiple equations of physics, which define the units
 implicitly.  In the 21st century the International System of units
-concluded implicit definition of units is not a bug, it's a feature.
-In 2018 the SI decided that only the second shall be defined by a
-particular physical process (a spectral line in Cs).  All other units
-are defined implicitly, through defined values of physical constants,
-including (but of course) Planck's constant.  Any applicable equation
-of physics can be used for the realization of
+concluded that implicit definition of units is not a bug, it's a
+feature.  In 2018 the SI decided that only the second shall be defined
+by a particular physical process (a spectral line in Cs).  All other
+units are defined implicitly, through defined values of physical
+constants, including (but of course) Planck's constant.  Any
+applicable equation of physics can be used for the realization of
 units.\cite{Jeckelmann_2018}
@@
 and the Josephson effect.  That would be sternly frowned upon by the
-old SI, but the new SI is cheerfully agnostic.  The new SI also
-removes conflicts with some common scientific usages.  For example,
-the electronvolt is not an SI unit.  However, if we understand mass in
-electronvolts as a shorthand for the value of mass times $c^2/e$ in
-volts, there is no conflict with the new SI.
+old SI, but the new SI is cheerfully agnostic about it.  The new SI
+also removes conflicts with some common scientific usages.  For
+example, the electronvolt is not an SI unit.  However, if we
+understand mass in electronvolts as a shorthand for the value of mass
+times $c^2/e$ in volts, there is no conflict with the new SI.
 
@@
 
-But post 2018 the SI no longer requires you to express the solar mass
-in kg --- but we'll get to that.  We remark first that distances in
-light-seconds are compliant with the new SI.  Like the electronvolt, a
-light-second is not itself a unit, it is an abbreviated way of
-referring to the equivalent light travel time.  On the other hand,
-which astronomer would wish to lose the cultural legacies of the
-astronomical unit of length (au), and the parsec?  Fortunately,
-metrology and cultural legacies can be reconciled.  To see how, we
-only to see how modern German has kept the old unit of a Pfund, but
-has rounded its meaning to exactly $500\unit{g}$.  The au and parsec
-have serendipitously round values: $1\unit{au}\simeq
-c\times500\unit{s}$ to better than 1\%, while a parsec is just 3\%
-over $c\times10^8\unit{s}$.
+After the reforms, however, the SI no longer requires you to express
+the solar mass in kg --- but we'll get to that.  We remark first that
+distances in light-seconds are compliant with the new SI.  Like the
+electronvolt, a light-second can be understood as not itself a unit,
+but an abbreviated way of referring to the equivalent light travel
+time.  On the other hand, which astronomer would wish to lose the
+cultural legacies of the astronomical unit of length (au), and the
+parsec?  Fortunately, metrology and cultural legacies can be
+reconciled.  To see how, we need only to see how modern German has
+kept the old unit of a Pfund, but has rounded its meaning to exactly
+$500\unit{g}$.  The au and parsec have serendipitously round values:
+$1\unit{au}\simeq c\times500\unit{s}$ to better than 1\%, while a
+parsec is just 3\% over $c\times10^8\unit{s}$.  Many astronomical
+applications do not require 1\% precision, and there ``rounded'' au
+and parsecs would work just fine.
 
-In the astronomy literature one finds many named units (\AA ngström,
-gauss, jansky) that are simply powers of 10 times SI units, which need
+In the astronomy literature one finds many further units (\AA ngström,
+gauss, jansky) that are simply powers of 10 times SI units, and need
 not detain us here.  There are also parody units such as
-$\!\unit{gallon}\unit{Mpc}^{-1}$ for cross-sections (it depends on the
-type of gallon, but is about a kilobarn), which would need an article
-to themselves.  The only remaining unit that needs discussing is the
-optical magnitude scale.  Optical magnitudes are a measure of
+$\!\!\unit{gallons}\unit{Mpc}^{-1}$ for cross-sections (it depends on
+the type of gallon, but is about a kilobarn), which would need an
+article to themselves.  The only remaining unit that needs discussing
+is the optical magnitude scale.  Optical magnitudes are a measure of
 brightness going back to classical times, but like other units they
@@
 classical and relativistic.\cite{2020PASP..132b1001S} Some
-constructions arise, that seem {\em very} strange at first: in
+constructions arise that seem {\em very} strange at first: in
 particular density in gravity-seconds per cubic light-seconds, or

### 2020-04-10 spg/main.tex
bbl
adding more

@@
 
+Solar grav lens.\cite{2020arXiv200211871T}
+
+$\alpha_\odot=4GM_\odot/(c^2 R_\odot)$.  $R_\odot\approx
+c\times2\unit{s}$.  Comes to $\approx10^{-5}\unit{radians}$.
+
+Caustic at $R_\odot/\alpha_\odot$.  This is $\approx
+c\times2\times10^5\unit{s}$ or $400\unit{au}$.  (Actually
+$550\unit{au}$.)
+
+$$ g_{\odot/\oplus} \approx 6\times10^{-3}\unit{m}\unit{s}^{-2} $$
+$$ P_{\odot/\oplus} \approx 5\times10^{-6}\unit{Pa} $$
+
+Would need $\approx 10^3\unit{m}^2\unit{kg}^{-1}$ to make the sun a
+net repeller.
+
+Cunning hybrid.
+
 In the 120 years since Planck speculated about it, we have yet to make
@@
 mass and energy through $c^2$ turned out to be real.  Starting in the
-1920s $(\hbox{Planck mass})^{-2}\times(\hbox{proton mass})^3$ was
+1920s $(hc/G)^{-2}\times(\hbox{proton mass})^3$ was
 discovered to be the mass scale of stars.  Later in the 20th century,
@@
 \bibliographystyle{apsrev4-1}
-\bibliography{refs.bib}
+\bibliography{main.bbl}
 

### 2020-04-10 spg/main.tex
adding an example

--- 2020-04-08 spg/main.tex
@@
 
+To illustrate working with the new SI in astronomy, let us consider an
+example that sounds like science fiction, but is in fact a serious
+design study: the solar gravity lens
+mission.\cite{2020arXiv200211871T} It envisions a telescope larger
+than the solar system with the sun's gravitational field as its main
+lens, for mapping the surfaces of extra-solar planets.  The essential
+physical effect is that light rays going past the sun with impact
+parameter $R$ are gravitationally deflected by an angle
+$4GM_\odot/(c^2 R)$.  In particular, the deflection of light from a
+star that is barely covered by the sun will make that star appear to
+be just outside the rim of the sun.  The deflection at the rim of the
+sun is well known to be $1.75\unit{arcsec}$ and its first measurement
+a century ago is the stuff of legend.\cite{Kennefick2012} Knowing the
+solar mass in gravity-seconds and approximating the solar radius as
+$R_\odot\approx c\times2\unit{s}$, we can trivially work out the
+gravitational deflection angle $\alpha=4GM_\odot/(c^2 R_\odot)$ as
+$\approx10^{-5}\unit{radians}$, which is indeed a little under
+$2\unit{arcsec}$.  If we go far-enough from the sun that its apparent
+radius on the sky becomes smaller than the deflection angle, a
+remarkable phenomenon will be seen: light sources precisely behind the
+sun will appear as luminous rings (known as Einstein rings) around the
+sun.  The threshold distance to see an Einstein ring is
+$R_\odot/\alpha\approx c\times2\times10^5\unit{s}$ or $\approx
+400\unit{au}$.  (Actually about $550\unit{au}$ with less drastic
+approximations.)
+
+$g_{\odot/\oplus} \approx 6\times10^{-3}\unit{m}\unit{s}^{-2}$
+
+$P_{\odot/\oplus} \approx 10^{-5}\unit{Pa}$
+
+Would need $\approx 600\unit{m}^2\unit{kg}^{-1}$ to make the sun a
+net repeller.
+
+Cunning hybrid.
+
 In the 120 years since Planck speculated about it, we have yet to make
@@
 \bibliographystyle{apsrev4-1}
+%\bibliography{main.bbl}
 \bibliography{refs.bib}

### 2020-04-10 spg/main.tex
version 2

--- 2020-04-08 spg/main.tex
@@
 
-In the 120 years since Planck speculated about it, we have yet to make
-contact with non-human or extra-terrestrial cultures, and ask them if
-they indeed share Planck's views on units.  What {\em has} happened,
-however, is that physical constants have turned out to have meanings
-not even Planck in 1899 had imagined.  As we all know, the following
-year Planck himself discovered that $h$ (formerly known as $b$) was
-about quantization.  A few years later the formal relation between
-mass and energy through $c^2$ turned out to be real.  Starting in the
-1920s $(\hbox{Planck mass})^{-2}\times(\hbox{proton mass})^3$ was
-discovered to be the mass scale of stars.  Later in the 20th century,
-$2e/h$ and $h/e^2$ turned out to be macroscopically observable as
-Josephson's constant and von~Klitzing's constant.  And just in the
-last few years, $c^5/G$ has been observed to be the power-output scale
-for merging black holes.  We can only wonder what more surprises await
-us.
+To illustrate working with the new SI in astronomy, let us consider an
+example that sounds like science fiction, but is in fact a serious
+design study: the solar gravity lens
+mission.\cite{2020arXiv200211871T} It envisions a telescope larger
+than the solar system with the sun's gravitational field as its main
+lens, for mapping the surfaces of extra-solar planets.  The essential
+physical effect is that light rays going past the sun with impact
+parameter $R$ are gravitationally deflected by an angle
+$4GM_\odot/(c^2 R)$.  In particular, the deflection of light from a
+star that is barely covered by the sun will make that star appear to
+be just outside the rim of the sun.  The deflection at the rim of the
+sun is well known to be $1.75\unit{arcsec}$ and its first measurement
+a century ago is the stuff of legend.\cite{Kennefick2012} Knowing the
+solar mass in gravity-seconds and approximating the solar radius as
+$R_\odot\approx c\times2\unit{s}$, we can trivially work out the
+gravitational deflection angle $\alpha=4GM_\odot/(c^2 R_\odot)
+\approx10^{-5}\unit{radians}$, which is indeed a little under
+$2\unit{arcsec}$.  If we go far enough from the sun that its apparent
+radius on the sky becomes smaller than the deflection angle, a
+remarkable phenomenon will present itself: light sources precisely
+behind the sun will appear as luminous rings (known as Einstein rings)
+around the sun.  The threshold distance to see an Einstein ring is
+$R_\odot/\alpha\approx c\times2\times10^5\unit{s}$ or $\approx
+400\unit{au}$.  (Actually about $550\unit{au}$ with less drastic
+approximations.)  The advantage of an Einstein ring is that it
+enormously magnifies the source, so much so that a $1\unit{m}$
+telescope located at the right place in deep space could resolve
+features down to $10\unit{km}$ on an exoplanet at 30~parsecs.  That
+level of detail is comparable to what the Hubble Space Telescope can
+see on Mars.  The image-reconstruction problem involved would be a
+major challenge in its own right, because the magnification produced
+by Einstein rings is highly anisotropic, but simulations indicate that
+it is solvable and that images could indeed be obtained.  The task
+that remains, then, is to fly a fleet of space telescopes to
+appropriate locations beyond $500\unit{au}$.  And within one lifetime,
+if possible, please.  The currently most promising strategy for doing
+this turns out to be (who would have guessed?) solar sails.  Solar
+sails also provide a nice example of how kilograms and gravity-seconds
+can co-exist.  Radiation pressure from the sun is, like gravity,
+inverse squared in the distance.  Hence the acceleration on a
+spacecraft with a solar sail will take the form
+$$ \frac{S\,F_\odot}{r^2} - \frac{GM_\odot}{r^2} $$ where $r$ is the
+distance from the sun, $F_\odot/r^2$ is the radiation pressure from
+the sun, and $S$ is the effective sail area per unit mass.  For
+simplicity we are neglecting the gravity of the planets and further
+non-gravitational perturbations.  The solar-sail term in effect
+reduces the gravitating mass of the sun, and could even reverse its
+sign if $S$ is large enough.  Let us consider both terms at
+$r=r_\oplus=1\unit{au}$.  Knowing the solar mass in gravity-seconds we
+easily get $GM_\odot/r_\oplus^2\approx6\unit{mm}\unit{s}^{-2}$.  To
+estimate $F_\odot/r_\oplus^2$ a convenient way is to recall the solar
+constant, which is the energy flux from the Sun at the top of the
+Earth's atmosphere.  This energy flux is, of course, in photons, and
+the energy of a photon is $c$ times its momentum.  Holding up a mirror
+normal to sunlight reflects the photons and imparts twice their
+momentum to the mirror.  Hence, multiplying the solar constant by
+$2/c$ gives the pressure on an optimally-aligned solar sail
+$1\unit{au}$ from the sun.  The value of the solar constant
+$1361\unit{W}\unit{m}^{-2}$ with small variations which we will
+disregard here, and the corresponding pressure will be a little under
+$10^{-5}\unit{Pa}$.  Comparing the terms, we see that we would need
+$S\approx 600\unit{m}^2\unit{kg}^{-1}$ to make the sun a net repeller.
+This may or may not be technologically feasible, but it is actually
+not necessary, thanks to a further cunning plan.  This is to first
+plunge the spacecraft in a very eccentric orbit close to the sun, and
+then at perihelion deploy the solar sail.  Without the solar sail, the
+spacecraft would simply have returned to repeat the orbit, but now it
+can sail out of the solar system on its mission to the focal region of
+the solar gravity lens.
+
+Even with such a daring space mission, it will probably be some time
+before we make contact with non-human or extra-terrestrial cultures,
+so that we can ask them if they indeed share Planck's views on units.
+Yet in the 120 years since Planck drew special attention to physical
+constants, they have turned out to have meanings not even Planck in
+1899 had imagined.  As we all know, the following year Planck himself
+discovered that $h$ (formerly known as $b$) was about quantization.  A
+few years later the formal relation between mass and energy through
+$c^2$ turned out to be real.  Starting in the 1920s
+$(hc/G)^{3/2}\times(\hbox{proton mass})^{-2}$ was discovered to be the
+mass scale of stars.  Later in the 20th century, $2e/h$ and $h/e^2$
+turned out to be macroscopically observable as Josephson's constant
+and von~Klitzing's constant.  And just in the last few years, $c^5/G$
+has been observed to be the power-output scale for merging black
+holes.  We can only wonder what more surprises await us.
 
@@
 \bibliographystyle{apsrev4-1}
-\bibliography{refs.bib}
+\bibliography{main.bbl}
+%\bibliography{refs.bib}
 
